---
title: "GoM cod and haddock RDM"
author: "Lou Carr-Harris"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: cerulean
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, comment = NA)

# Package setup
pkgs_to_use <- c("tidyverse", "data.table", "readxl", "haven", "stringr", "knitr",
                 "furrr", "profvis", "future", "copula", "VineCopula", "fitdistrplus",
                 "psych", "logspline", "univariateML", "ggpubr", "gridExtra", "hrbrthemes",
                 "writexl", "sjPlot", "tictoc", "Hmisc")

install_if_missing <- setdiff(pkgs_to_use, rownames(installed.packages()))
if (length(install_if_missing) > 0) install.packages(install_if_missing)
lapply(pkgs_to_use, library, character.only = TRUE)

# Set preferred functions from conflicted packages
if ("conflicted" %in% rownames(installed.packages())) {
  library(conflicted)
  conflicts_prefer(dplyr::filter)
  conflicts_prefer(dplyr::select)
  conflicts_prefer(dplyr::mutate)
  conflicts_prefer(dplyr::rename)
  conflicts_prefer(dplyr::summarize)
  conflicts_prefer(dplyr::summarise)
  conflicts_prefer(dplyr::count)
}

output_data_cd <- "C:/Users/andrew.carr-harris/Desktop/Git/welfare-model-GoM/newest_version/output_data/"
input_data_cd <- "C:/Users/andrew.carr-harris/Desktop/Git/welfare-model-GoM/newest_version/input_data/"
```

### Bottom temperatures {.tabset}
```{r bottom-temp-data, echo = FALSE, fig.width=8, fig.height=6}
# Load and process projection data
bt_temp_project <- read_csv(file.path(input_data_cd, "decadal_bottom_temp_distributions_levels_3_12_2025.csv"), show_col_types = FALSE) %>%
  mutate(
    lower = average_temp - 1.96 * sd_temp,
    upper = average_temp + 1.96 * sd_temp
  ) %>%
  group_by(decade) %>%
  mutate(mean_decadal_tmp = mean(average_temp)) %>%
  rename(decade2 = decade) %>%
  mutate(decade = case_when(
    decade2 == 1 ~ "2021-2030",
    decade2 == 2 ~ "2031-2040",
    decade2 == 3 ~ "2041-2050",
    decade2 == 4 ~ "2051-2060",
    decade2 == 5 ~ "2061-2070",
    decade2 == 6 ~ "2071-2080",
    decade2 == 7 ~ "2081-2090",
    decade2 == 8 ~ "2091-3000"
  )) %>%
  ungroup() %>%
  select(-decade2) %>%
  rename(mean_temp = average_temp) %>%
  mutate(month = as.numeric(month))

# Load and process historical data
hist_daily_bt_tmps_raw_GoM <- read_excel(file.path(input_data_cd, "hist_daily_bt_tmps_agg_GoM.xlsx")) %>%
  mutate(
    date = as.Date(date),
    year = as.numeric(format(date, "%Y")),
    month = as.numeric(format(date, "%m"))
  ) %>%
  group_by(year, month) %>%
  summarise(mean_tmp_ym = mean(mean_tmp), .groups = "drop") %>%
  mutate(decade = case_when(
    year >= 1961 & year <= 1970 ~ "1961-1970",
    year >= 1971 & year <= 1980 ~ "1971-1980",
    year >= 1981 & year <= 1990 ~ "1981-1990",
    year >= 1991 & year <= 2000 ~ "1991-2000",
    year >= 2001 & year <= 2010 ~ "2001-2010",
    year >= 2011 & year <= 2020 ~ "2011-2020"
  )) %>%
  filter(!is.na(decade)) %>%
  group_by(decade, month) %>%
  mutate(
    mean_temp = mean(mean_tmp_ym),
    sd_temp = sd(mean_tmp_ym),
    lower = mean_temp - 1.96 * sd_temp,
    upper = mean_temp + 1.96 * sd_temp
  ) %>%
  ungroup() %>%
  group_by(decade) %>%
  mutate(mean_decadal_tmp = mean(mean_temp)) %>%
  ungroup()

historical_and_projections <- bind_rows(hist_daily_bt_tmps_raw_GoM, bt_temp_project)


#annual 
bt_temp_project_annual <- read_csv(file.path(input_data_cd, "decadal_bottom_temp_distributions_levels_3_12_2025.csv"), show_col_types = FALSE) %>%
  mutate(
    lower = average_temp - 1.96 * sd_temp,
    upper = average_temp + 1.96 * sd_temp
  ) %>%
  group_by(decade) %>%
  mutate(mean_decadal_tmp = mean(average_temp)) %>%
  rename(decade2 = decade) %>%
  mutate(decade = case_when(
    decade2 == 1 ~ "2021-2030",
    decade2 == 2 ~ "2031-2040",
    decade2 == 3 ~ "2041-2050",
    decade2 == 4 ~ "2051-2060",
    decade2 == 5 ~ "2061-2070",
    decade2 == 6 ~ "2071-2080",
    decade2 == 7 ~ "2081-2090",
    decade2 == 8 ~ "2091-3000"
  )) %>%
  ungroup() %>%
  select(-decade2) %>%
  rename(mean_temp = average_temp) %>%
  mutate(month = as.numeric(month))

# Load and process historical data
hist_daily_bt_tmps_raw_GoM_annual <- read_excel(file.path(input_data_cd, "hist_daily_bt_tmps_agg_GoM.xlsx")) %>%
  mutate(
    date = as.Date(date),
    year = as.numeric(format(date, "%Y")),
    month = as.numeric(format(date, "%m"))
  ) %>%
  group_by(year, month) %>%
  summarise(mean_tmp_ym = mean(mean_tmp), .groups = "drop") %>%
  mutate(decade = case_when(
    year == 2011  ~ "2011",
    year == 2012  ~ "2012",
    year == 2013  ~ "2013",
    year == 2014  ~ "2014",
    year == 2015  ~ "2015",
    year == 2016  ~ "2016", 
    year == 2017  ~ "2017", 
    year == 2018  ~ "2018", 
    year == 2019  ~ "2019", 
    year == 2020  ~ "2020", 
    year == 2021  ~ "2021")) %>%
  filter(!is.na(decade)) %>%
  group_by(decade, month) %>%
  mutate(
    mean_temp = mean(mean_tmp_ym),
    sd_temp = sd(mean_tmp_ym),
    lower = mean_temp - 1.96 * sd_temp,
    upper = mean_temp + 1.96 * sd_temp
  ) %>%
  ungroup() %>%
  group_by(decade) %>%
  mutate(mean_decadal_tmp = mean(mean_temp)) %>%
  ungroup()

historical_and_projections_annual <- bind_rows(hist_daily_bt_tmps_raw_GoM_annual, bt_temp_project_annual)


```

#### By decade
```{r bottom-temp-plot, echo = FALSE, fig.height=6, fig.width=10}
ggplot(historical_and_projections, aes(month, mean_temp)) +
  geom_point() +
  geom_errorbar(aes(ymin = lower, ymax = upper)) +
  facet_wrap(~decade, nrow = 1) +
  theme(
    axis.text.x = element_blank(),
    strip.text = element_text(size = 7, margin = margin()),
    axis.ticks.x = element_blank()
  ) +
  geom_hline(aes(yintercept = mean_decadal_tmp), color = "red") +
  labs(x = NULL, y = "Sea bottom temperature (C)") +
  ggtitle("Historical and projected average monthly sea bottom temperatures in the Gulf of Maine by decade")
```

*Mean monthly bottom temps by decade/year, red line indicates the decadal average. Bars represent mean monthly temp +/- 1.96 x standard dev.*

#### By year
```{r bottom-temp-plot2, echo = FALSE, fig.height=6, fig.width=10}
ggplot(historical_and_projections_annual, aes(month, mean_temp)) +
  geom_point() +
  geom_errorbar(aes(ymin = lower, ymax = upper)) +
  facet_wrap(~decade, nrow = 1) +
  theme(
    axis.text.x = element_blank(),
    strip.text = element_text(size = 7, margin = margin()),
    axis.ticks.x = element_blank()
  ) +
  geom_hline(aes(yintercept = mean_decadal_tmp), color = "red") +
  labs(x = NULL, y = "Sea bottom temperature (C)") +
  ggtitle("Historical and projected average monthly sea bottom temperatures in the Gulf of Maine by year/decade")
```

*Mean monthly bottom temps by decade/year, red line indicates the decadal average. Bars represent mean monthly temp +/- 1.96 x standard dev.*

### {-}
### Model input projected catch-trip-data
```{r echo = FALSE}
proj_data <- read_dta("C:/Users/andrew.carr-harris/Desktop/Git/welfare-model-GoM/newest_version/input_data/projection_catch_base_wide.dta")

# Rename columns
proj_data <- proj_data %>%
  rename(month = month1, mode = mode1)

# Recode 'state' values
proj_data <- proj_data %>%
  mutate(state = case_when(
    state == "MA" ~ 25,
    state == "ME" ~ 23,
    state == "NH" ~ 33,
    TRUE ~ NA_real_
  ))

# Collapse (mean) of had* and cod* by month/mode/area/state
proj_data <- proj_data %>%
  dplyr::group_by(month, mode, area, state) %>%
  dplyr::summarise(across(starts_with("had"), \(x) mean(x, na.rm = TRUE)),
            across(starts_with("cod"),\(x) mean(x, na.rm = TRUE)),
            .groups = "drop")

# Reshape wide to long format for multiple 'decade' groups
proj_data_long <- proj_data %>%
  pivot_longer(
    cols = c(
      starts_with("cod_corr_clayton"), starts_with("cod_ind_clayton"),
      starts_with("had_corr_clayton"), starts_with("had_ind_clayton"), 
      starts_with("cod_corr_plackett"), starts_with("cod_ind_plackett"),
      starts_with("had_corr_plackett"), starts_with("had_ind_plackett"), 
      starts_with("cod_corr_gaussian"), starts_with("cod_ind_gaussian"),
      starts_with("had_corr_gaussian"), starts_with("had_ind_gaussian"), 
      starts_with("cod_corr_frank"), starts_with("cod_ind_frank"),
      starts_with("had_corr_frank"), starts_with("had_ind_frank"), 
      starts_with("cod_corr_gumbel"), starts_with("cod_ind_gumbel"),
      starts_with("had_corr_gumbel"), starts_with("had_ind_gumbel")
    ),
    names_to = c(".value", "decade"),
    names_pattern = "(cod_corr_clayton|had_corr_clayton|cod_ind_clayton|had_ind_clayton|cod_corr_plackett|had_corr_plackett|cod_ind_plackett|had_ind_plackett|cod_corr_gaussian|had_corr_gaussian|cod_ind_gaussian|had_ind_gaussian|cod_corr_frank|had_corr_frank|cod_ind_frank|had_ind_frank|cod_corr_gumbel|had_corr_gumbel|cod_ind_gumbel|had_ind_gumbel)(.+)"
  )

# --- Step 2: Read the directed trips CSV ---
directed_trips <- fread("C:/Users/andrew.carr-harris/Desktop/Git/welfare-model-GoM/newest_version/input_data/directed trips and regulations 2010_2020_disaggregated.csv")

# Filter and rename
directed_trips <- directed_trips %>%
  filter(year == 2021) %>%
  rename(state = st)

# Collapse (sum) dtrip by month/mode/area/state
directed_trips_summarized <- directed_trips %>%
  group_by(month, mode, area, state) %>%
  summarise(dtrip = sum(dtrip, na.rm = TRUE), .groups = "drop")

# --- Step 3: Merge with reshaped projection data ---
merged_data <- directed_trips_summarized %>%
  left_join(proj_data_long, by = c("month", "mode", "area", "state")) %>%
  dplyr::filter(!is.na(decade)) %>%  # equivalent to dropping _merge==1
  select(-contains("ind"))  # drop *ind*

# --- Step 4: Collapse weighted means by decade ---
final_result <- merged_data %>%
  group_by(decade) %>%
  summarise(
    cod_corr_clayton = weighted.mean(cod_corr_clayton, dtrip, na.rm = TRUE),
    had_corr_clayton = weighted.mean(had_corr_clayton, dtrip, na.rm = TRUE),
    cod_corr_frank = weighted.mean(cod_corr_frank, dtrip, na.rm = TRUE),
    had_corr_frank = weighted.mean(had_corr_frank, dtrip, na.rm = TRUE),
    cod_corr_gumbel = weighted.mean(cod_corr_gumbel, dtrip, na.rm = TRUE),
    had_corr_gumbel = weighted.mean(had_corr_gumbel, dtrip, na.rm = TRUE),
    cod_corr_plackett = weighted.mean(cod_corr_plackett, dtrip, na.rm = TRUE),
    had_corr_plackett = weighted.mean(had_corr_plackett, dtrip, na.rm = TRUE),
    cod_corr_gaussian = weighted.mean(cod_corr_gaussian, dtrip, na.rm = TRUE),
    had_corr_gaussian = weighted.mean(had_corr_gaussian, dtrip, na.rm = TRUE),
    # If cod_ind and had_ind are still there
    #cod_ind = weighted.mean(cod_ind, dtrip, na.rm = TRUE),
    #had_ind = weighted.mean(had_ind, dtrip, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  select(-contains("ind"))  # drop *ind*
head(final_result)
```

### {-}
### Decadal projections (catch data from 2025-04-17) {.tabset}
Each tab contains different projected fishery outcomes across copula models for the case of dependence, independence, and the difference between dependence and independence. 
```{r echo = FALSE,  fig.width=10}
#historical catch 
historical_catch <- read_dta("C:/Users/andrew.carr-harris/Desktop/Git/welfare-model-GoM/newest_version/input_data/cod_hadd_catch_data_1_15.dta")

historical_catch<-historical_catch %>% 
  dplyr::filter(year>=2011 & year<=2020) %>% 
  dplyr::mutate(dtrip=1) %>% 
  dplyr::group_by(year) %>%
  summarise(across(c(tot_cat_cod, tot_cat_hadd, dtrip), \(x) sum(x, na.rm = TRUE)),.groups="drop") %>% 
  dplyr::mutate(codcattrip=tot_cat_cod/dtrip, 
                haddcattrip=tot_cat_hadd/dtrip, 
                copula="baseline", 
                correlation="baseline") 


#2021 output 
base_output<-read_excel(paste0(output_data_cd,"model_output_4-21-25.xlsx")) %>% 
  dplyr::select(month, mode, area, state, draw, matches("base")) %>%
  rename_with(~ gsub("_(cat)", "\\1", .x), matches("_cat")) %>%
  rename_with(~ gsub("_(keep)", "\\1", .x), matches("_keep")) %>%
  rename_with(~ gsub("_(rel)", "\\1", .x), matches("_rel")) %>%
  rename_with(~ gsub("_(alt)", "\\1", .x), matches("_alt")) %>% 
  rename_with(~ gsub("base_", "", .x), contains("base_"))

base_output_long <- base_output %>%
  pivot_longer(
    cols =  starts_with("codkeep") | starts_with("codrel") | starts_with("haddkeep") |
      starts_with("haddrel") | starts_with("haddcat") | starts_with("codcat") | starts_with("ntrips"),  # Select columns to reshape
    names_to = c(".value", "correlation", "copula", "decade"), 
    names_pattern = "([a-z]+)_([a-z]+)_([a-z]+)([12345678])"  
  )

base_output_summarized <- base_output_long %>%
  group_by(draw, copula, correlation, decade) %>%
  summarise(across(c(codcat, codkeep, codrel, haddcat, haddkeep, haddrel, ntrips), \(x) sum(x, na.rm = TRUE)), .groups="drop") %>% 
  dplyr::mutate(haddrel=haddcat-haddkeep) %>% 
  dplyr::filter(copula=="clayton", correlation=="corr", decade==1) %>% 
  dplyr::mutate(copula="baseline", correlation="baseline", decade=0) %>% 
  dplyr::mutate(codcattrip=codcat/ntrips, 
                codkeeptrip=codkeep/ntrips, 
                haddcattrip=haddcat/ntrips, 
                haddkeeptrip=haddkeep/ntrips, 
                year=2021) 

#mean(base_output_summarized$codcattrip)
#mean(base_output_summarized$haddcattrip)

#Projection output by decade
output<-read_excel(paste0(output_data_cd,"model_output_4-21-25.xlsx")) %>% 
  dplyr::select(-matches("base"))  %>%
  rename_with(~ gsub("_(cat)", "\\1", .x), matches("_cat")) %>%
  rename_with(~ gsub("_(keep)", "\\1", .x), matches("_keep")) %>%
  rename_with(~ gsub("_(rel)", "\\1", .x), matches("_rel")) %>%
  rename_with(~ gsub("_(alt)", "\\1", .x), matches("_alt")) 

# Reshaping to long format
output_long <- output %>%
  pivot_longer(
    cols = starts_with("cv") | starts_with("codkeep") | starts_with("codrel") | starts_with("haddkeep") |
      starts_with("haddrel") | starts_with("haddcat") | starts_with("codcat") | starts_with("ntripsalt"),  # Select columns to reshape
    names_to = c(".value", "correlation", "copula", "decade"), 
    names_pattern = "([a-z]+)_([a-z]+)_([a-z]+)([12345678])"  
  )


# Summing selected variables by grouping variables
output_summarized <- output_long %>%
  group_by(draw, copula, correlation, decade) %>%
  summarise(across(c(codcat, codkeep, codrel, cv, haddcat, haddkeep, haddrel, ntripsalt), \(x) sum(x, na.rm = TRUE)), .groups="drop")

output_summarized <- output_summarized %>%
  dplyr::mutate(decade=as.numeric(decade)) %>%  
  dplyr::mutate(codcattrip=codcat/ntripsalt, 
                codkeeptrip=codkeep/ntripsalt, 
                haddcattrip=haddcat/ntripsalt, 
                haddkeeptrip=haddkeep/ntripsalt, 
                cvtrip=cv/ntripsalt, 
                year=decade+2029) %>% 
  dplyr::rename(ntrips=ntripsalt)

#Append the baseline output
output_summarized1 <- output_summarized %>%
  plyr::rbind.fill(base_output_summarized, historical_catch) 

#By decade and copula
output_summarized_corr<-output_summarized1 %>% 
  dplyr::filter(correlation=="corr" | correlation=="baseline") %>% 
  dplyr::select(-correlation)

# output_summarized_corr <- output_summarized_corr %>%
#   rename_with(~ paste0(.x, "_corr"), c(codcat, codkeep, codrel, cv, haddcat, haddkeep, haddrel, ntrips, 
#                                        codcattrip, codkeeptrip, haddcattrip, haddkeeptrip, cvtrip))

output_summarized_ind<-output_summarized1 %>% 
  dplyr::filter(correlation=="ind" | correlation=="baseline") %>% 
  dplyr::select(-correlation)

# output_summarized_ind <- output_summarized_ind %>%
#   rename_with(~ paste0(.x, "_ind"), c(codcat, codkeep, codrel, cv, haddcat, haddkeep, haddrel, ntrips, 
#                                       codcattrip, codkeeptrip, haddcattrip, haddkeeptrip, cvtrip))

# output_summarized <- output_summarized_corr %>% 
#   dplyr::left_join(output_summarized_ind, by=c("draw", "copula","decade" )) %>% 
#   dplyr::mutate(diff_codcat= codcat_corr-codcat_ind,
#                 diff_codkeep=  codkeep_corr- codkeep_ind,
#                 diff_codrel=  codrel_corr- codrel_ind,
#                 diff_cv=  cv_corr- cv_ind,
#                 diff_haddcat=  haddcat_corr- haddcat_ind,
#                 diff_haddkeep= haddkeep_corr- haddkeep_ind,
#                 diff_haddrel= haddrel_corr- haddrel_ind,
#                 diff_ntrips= ntrips_corr- ntrips_ind,
#                 diff_codcattrip=  codcattrip_corr- codcattrip_ind,
#                 diff_codkeeptrip= codkeeptrip_corr- codkeeptrip_ind,
#                 diff_haddcattrip= haddcattrip_corr- haddcattrip_ind,
#                 diff_haddkeeptrip= haddkeeptrip_corr- haddkeeptrip_ind,
#                 diff_cvtrip=cvtrip_corr- cvtrip_ind)
# 
# output_summarized<-rbind.fill(output_summarized, base_output_summarized)
```
<div style="margin-bottom:50px;">
</div>

#### CV per trip (correlated)
```{r echo = FALSE, fig.width=10}
  
ggplot(output_summarized_corr, aes(x=factor(year), y=cvtrip, color = factor(copula)))+
  geom_boxplot() 

```
<div style="margin-bottom:50px;">
</div>

#### cod catch per trip (correlated)
```{r echo = FALSE, fig.width=10}
  
ggplot(output_summarized_corr, aes(x=factor(year), y=codcattrip, color = factor(copula)))+
  geom_boxplot() 

```
<div style="margin-bottom:50px;">
</div>

#### cod keep per trip (correlated)
```{r echo = FALSE, fig.width=10}
  
ggplot(output_summarized_corr, aes(x=factor(year), y=codkeeptrip, color = factor(copula)))+
  geom_boxplot() 

```
<div style="margin-bottom:50px;">
</div>

#### haddock catch per trip (correlated)
```{r echo = FALSE, fig.width=10}
  
ggplot(output_summarized_corr, aes(x=factor(year), y=haddcattrip, color = factor(copula)))+
  geom_boxplot() 

```
<div style="margin-bottom:50px;">
</div>

#### haddock keep per trip (correlated)
```{r echo = FALSE, fig.width=10}
  
ggplot(output_summarized_corr, aes(x=factor(year), y=haddkeeptrip, color = factor(copula)))+
  geom_boxplot() 

```
<div style="margin-bottom:50px;">
</div>

#### CV per trip (independent)
```{r echo = FALSE, fig.width=10}
  
ggplot(output_summarized_ind, aes(x=factor(year), y=cvtrip, color = factor(copula)))+
  geom_boxplot() 
```
<div style="margin-bottom:50px;">
</div>

#### cod catch per trip (independent)
```{r echo = FALSE, fig.width=10}
  
ggplot(output_summarized_ind, aes(x=factor(year), y=codcattrip, color = factor(copula)))+
  geom_boxplot() 

```
<div style="margin-bottom:50px;">
</div>

#### cod keep per trip (independent)
```{r echo = FALSE, fig.width=10}
  
ggplot(output_summarized_ind, aes(x=factor(year), y=codkeeptrip, color = factor(copula)))+
  geom_boxplot() 

```
<div style="margin-bottom:50px;">
</div>

#### haddock catch per trip (independent)
```{r echo = FALSE, fig.width=10}
  
ggplot(output_summarized_ind, aes(x=factor(year), y=haddcattrip, color = factor(copula)))+
  geom_boxplot() 

```
<div style="margin-bottom:50px;">
</div>

#### haddock keep per trip (independent)
```{r echo = FALSE, fig.width=10}
  
ggplot(output_summarized_ind, aes(x=factor(year), y=haddkeeptrip, color = factor(copula)))+
  geom_boxplot() 

```

### {-}
### Decadal projections for Geret (catch data from 2025-04-17) {.tabset}
Each tab contains different projected fishery outcomes across copula models for the case of dependence, independence, and the difference between dependence and independence. 
```{r echo = FALSE,  fig.width=10}
# Filter out decade == 0
output_summarized_corr_filtered <- output_summarized_corr %>% filter(decade != 0)
output_summarized_ind_filtered <- output_summarized_ind %>% filter(decade != 0)

# Find global y-axis limits for both datasets
y_min_cv <- min(c(output_summarized_corr_filtered$cvtrip, output_summarized_ind_filtered$cvtrip), na.rm = TRUE)
y_max_cv <- max(c(output_summarized_corr_filtered$cvtrip, output_summarized_ind_filtered$cvtrip), na.rm = TRUE)



#Baseline period average catch-per-trips 
output_summarized_baseline_filtered<- output_summarized_corr %>% filter(copula == "baseline" & decade==0)

output_summarized_baseline_filtered<- output_summarized_baseline_filtered %>%
  group_by(year) %>%
  summarise(across(c(codcat, codkeep, codrel, haddcat, haddkeep, haddrel, ntrips), \(x) mean(x, na.rm = TRUE)), .groups="drop")

output_summarized_baseline_filtered2<- output_summarized_corr %>% filter(copula == "baseline" & is.na(decade))

output_summarized_baseline_filtered2 <- output_summarized_baseline_filtered2 %>%
  group_by(year) %>%
  summarise(across(c(tot_cat_cod, tot_cat_hadd, dtrip), \(x) mean(x, na.rm = TRUE)), .groups="drop") %>% 
  rename(codcat=tot_cat_cod, haddcat=tot_cat_hadd, ntrips=dtrip)

output_summarized_baseline_filtered2<-bind_rows(output_summarized_baseline_filtered2, output_summarized_baseline_filtered)

historical_average_cod_catch<-sum(output_summarized_baseline_filtered2$codcat)/sum(output_summarized_baseline_filtered2$ntrips)
historical_average_hadd_catch<-sum(output_summarized_baseline_filtered2$haddcat)/sum(output_summarized_baseline_filtered2$ntrips)

output_summarized_corr_filtered2<-output_summarized_corr %>% filter(!is.na(decade) & decade!=0)
output_summarized_ind_filtered2<-output_summarized_ind %>% filter(!is.na(decade) & decade!=0)

# Relabel decades
output_summarized_corr_filtered2 <- output_summarized_corr_filtered2 %>%
  mutate(decade_label = paste0("Decade ", decade))

output_summarized_ind_filtered2 <- output_summarized_ind_filtered2 %>%
  mutate(decade_label = paste0("Decade ", decade))


# Create a new row for the historical average point
historical_point_cod <- data.frame(
  decade_label = "Average 2011-2021",
  codcattrip = historical_average_cod_catch
)
historical_point_hadd <- data.frame(
  decade_label = "Average 2011-2021",
  haddcattrip = historical_average_hadd_catch
)

y_min_cod_cat <- min(c(output_summarized_corr_filtered$codcattrip, output_summarized_ind_filtered$codcattrip, historical_point_cod$codcattrip), na.rm = TRUE)
y_max_cod_cat <- max(c(output_summarized_corr_filtered$codcattrip, output_summarized_ind_filtered$codcattrip, historical_point_cod$codcattrip), na.rm = TRUE)


y_min_hadd_cat <- min(c(output_summarized_corr_filtered$haddcattrip, output_summarized_ind_filtered$haddcattrip,historical_point_hadd$haddcattrip ), na.rm = TRUE)
y_max_hadd_cat <- max(c(output_summarized_corr_filtered$haddcattrip, output_summarized_ind_filtered$haddcattrip ,historical_point_hadd$haddcattrip), na.rm = TRUE)

y_min_cod_keep <- min(c(output_summarized_corr_filtered2$codkeeptrip, output_summarized_ind_filtered2$codkeeptrip), na.rm = TRUE)
y_max_cod_keep <- max(c(output_summarized_corr_filtered2$codkeeptrip, output_summarized_ind_filtered2$codkeeptrip), na.rm = TRUE)

y_min_hadd_keep <- min(c(output_summarized_corr_filtered2$haddkeeptrip, output_summarized_ind_filtered2$haddkeeptrip), na.rm = TRUE)
y_max_hadd_keep <- max(c(output_summarized_corr_filtered2$haddkeeptrip, output_summarized_ind_filtered2$haddkeeptrip), na.rm = TRUE)


```

#### CV per trip (correlated)
```{r echo = FALSE, fig.width=10}
  
ggplot(output_summarized_corr_filtered, aes(x = factor(decade), y = cvtrip, color = factor(copula))) +
  geom_boxplot() +
  coord_cartesian(ylim = c(y_min_cv, y_max_cv)) +
  labs(x = "Decade", y = "Compensating variation per trip ($)")

```
<div style="margin-bottom:50px;">
</div>

#### CV per trip (independent)
```{r echo = FALSE, fig.width=10}
  
ggplot(output_summarized_ind_filtered, aes(x = factor(decade), y = cvtrip, color = factor(copula))) +
  geom_boxplot() +
  coord_cartesian(ylim = c(y_min_cv, y_max_cv))+
  labs(x = "Decade", y = "Compensating variation per trip ($)")
```
<div style="margin-bottom:50px;">
</div>

#### cod catch per trip (correlated)
```{r echo = FALSE, fig.width=10}
  
#ggplot(output_summarized_corr_filtered2, aes(x=factor(decade), y=codcattrip, color = factor(copula)))+
#  geom_boxplot() 
ggplot(output_summarized_corr_filtered2, aes(x = factor(decade), y = codcattrip, color = factor(copula))) +
  geom_boxplot() +
   coord_cartesian(ylim = c(y_min_cod_cat, y_max_cod_cat)) +
  # geom_point(data = historical_point_cod, aes(x = decade_label, y = codcattrip), 
  #            color = "black", shape = 18, size = 3, inherit.aes = FALSE) +
  labs(x = "Decade", y = "Cod catch per trip")


```
<div style="margin-bottom:50px;">
</div>


#### cod catch per trip (independent)
```{r echo = FALSE, fig.width=10}
  
#ggplot(output_summarized_ind_filtered2, aes(x=factor(decade), y=codcattrip, color = factor(copula)))+
#  geom_boxplot() 

ggplot(output_summarized_ind_filtered2, aes(x = factor(decade), y = codcattrip, color = factor(copula))) +
  geom_boxplot() +
   coord_cartesian(ylim = c(y_min_cod_cat, y_max_cod_cat)) +
  # geom_point(data = historical_point_cod, aes(x = decade_label, y = codcattrip), 
  #            color = "black", shape = 18, size = 3, inherit.aes = FALSE) +
  labs(x = "Decade", y = "Cod catch per trip")

```
<div style="margin-bottom:50px;">
</div>

#### haddock catch per trip (correlated)
```{r echo = FALSE, fig.width=10}
  
#ggplot(output_summarized_corr_filtered2, aes(x=factor(decade), y=haddcattrip, color = factor(copula)))+
#  geom_boxplot() 
ggplot(output_summarized_corr_filtered2, aes(x=factor(decade), y = haddcattrip, color = factor(copula))) +
  geom_boxplot() +
   coord_cartesian(ylim = c(y_min_hadd_cat, y_max_hadd_cat)) +
  # geom_point(data = historical_point_hadd, aes(x = decade_label, y = haddcattrip), 
  #            color = "black", shape = 18, size = 3, inherit.aes = FALSE) +
  labs(x = "Decade", y = "Haddock catch per trip")

```
<div style="margin-bottom:50px;">
</div>

#### haddock catch per trip (independent)
```{r echo = FALSE, fig.width=10}
  
#ggplot(output_summarized_ind_filtered2, aes(x=factor(decade), y=haddcattrip, color = factor(copula)))+
#  geom_boxplot() 

ggplot(output_summarized_ind_filtered2, aes(x = factor(decade), y = haddcattrip, color = factor(copula))) +
  geom_boxplot() +
   coord_cartesian(ylim = c(y_min_hadd_cat, y_max_hadd_cat)) +
  # geom_point(data = historical_point_hadd, aes(x = decade_label, y = haddcattrip), 
  #            color = "black", shape = 18, size = 3, inherit.aes = FALSE) +
  labs(x = "Decade", y = "Haddock catch per trip")

```
<div style="margin-bottom:50px;">
</div>

#### cod keep per trip (correlated)
```{r echo = FALSE, fig.width=10}
  
ggplot(output_summarized_corr_filtered2, aes(x=factor(decade), y=codkeeptrip, color = factor(copula)))+
  geom_boxplot() +
  coord_cartesian(ylim = c(y_min_cod_keep, y_max_cod_keep)) +
  labs(x = "Decade", y = "Cod harvest per trip")

```
<div style="margin-bottom:50px;">
</div>

#### cod keep per trip (independent)
```{r echo = FALSE, fig.width=10}
  
ggplot(output_summarized_ind_filtered2, aes(x=factor(decade), y=codkeeptrip, color = factor(copula)))+
  geom_boxplot() +
  coord_cartesian(ylim = c(y_min_cod_keep, y_max_cod_keep)) +
  labs(x = "Decade", y = "Cod harvest per trip")

```
<div style="margin-bottom:50px;">
</div>

#### haddock keep per trip (correlated)
```{r echo = FALSE, fig.width=10}
  
ggplot(output_summarized_corr_filtered2, aes(x=factor(decade), y=haddkeeptrip, color = factor(copula)))+
  geom_boxplot() +
  coord_cartesian(ylim = c(y_min_hadd_keep, y_max_hadd_keep)) +
  labs(x = "Decade", y = "Haddock harvest per trip")

```
<div style="margin-bottom:50px;">
</div>

#### haddock keep per trip (independent)
```{r echo = FALSE, fig.width=10}
  
ggplot(output_summarized_ind_filtered2, aes(x=factor(decade), y=haddkeeptrip, color = factor(copula)))+
  geom_boxplot() +
  coord_cartesian(ylim = c(y_min_hadd_keep, y_max_hadd_keep)) +
  labs(x = "Decade", y = "Haddock harvest per trip")

```

### {-}
