---
title: "GoM cod and haddock RDM"
author: "Lou Carr-Harris"
date: "`r Sys.Date()`"
output:
  html_document:
  theme: cerulean
toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, comment = NA)

# Package setup
pkgs_to_use <- c("tidyverse", "data.table", "readxl", "haven", "stringr", "knitr",
                 "furrr", "profvis", "future", "copula", "VineCopula", "fitdistrplus",
                 "psych", "logspline", "univariateML", "ggpubr", "gridExtra", "hrbrthemes",
                 "writexl", "sjPlot", "tictoc", "Hmisc", "plyr", "dplyr", "conflicted")

install_if_missing <- setdiff(pkgs_to_use, rownames(installed.packages()))
if (length(install_if_missing) > 0) install.packages(install_if_missing)
lapply(pkgs_to_use, library, character.only = TRUE)
# Set preferred functions from conflicted packages
if ("conflicted" %in% rownames(installed.packages())) {
  library(conflicted)
  conflicts_prefer(dplyr::filter)
  conflicts_prefer(dplyr::select)
  conflicts_prefer(dplyr::mutate)
  conflicts_prefer(dplyr::rename)
  conflicts_prefer(dplyr::summarize)
  conflicts_prefer(dplyr::summarise)
  conflicts_prefer(dplyr::count)
}

output_data_cd <- "C:/Users/andrew.carr-harris/Desktop/Git/welfare-model-GoM/newest_version/output_data/"
input_data_cd <- "C:/Users/andrew.carr-harris/Desktop/Git/welfare-model-GoM/newest_version/input_data/"

options(scipen=999)
```

## Bottom temperatures {.tabset}
```{r bottom-temp-data, echo = FALSE, fig.width=8, fig.height=6}
historical_and_projections<- read_excel(paste0(output_data_cd,"bottom_temp_reformat1.xlsx"))  #save the data
historical_and_projections_annual<- read_excel(paste0(output_data_cd,"bottom_temp_reformat2.xlsx"))  #save the data
```

### Historical by decade and projected 
```{r bottom-temp-plot1, echo = FALSE, fig.height=6, fig.width=10}
ggplot(historical_and_projections, aes(month, mean_temp)) +
  geom_point() +
  geom_errorbar(aes(ymin = lower, ymax = upper)) +
  facet_wrap(~decade, nrow = 1) +
  theme(
    axis.text.x = element_blank(),
    strip.text = element_text(size = 7, margin = margin()),
    axis.ticks.x = element_blank()
  ) +
  geom_hline(aes(yintercept = mean_decadal_tmp), color = "red") +
  labs(x = NULL, y = "Sea bottom temperature (C)") +
  ggtitle("Historical and projected average monthly sea bottom temperatures in the Gulf of Maine by decade")
```

*Mean monthly bottom temps by decade/year, red line indicates the decadal average. Bars represent mean monthly temp +/- 1.96 x standard dev.*

### Projected
```{r bottom-temp-plot2, echo = FALSE, fig.height=6, fig.width=10}
projection_temps<-historical_and_projections %>% 
  dplyr::filter(is.na(year))

ggplot(projection_temps, aes(month, mean_temp)) +
  geom_point() +
  geom_errorbar(aes(ymin = lower, ymax = upper)) +
  facet_wrap(~decade, nrow = 1) +
  theme(
    axis.text.x = element_blank(),
    strip.text = element_text(size = 10, margin = margin()),
    axis.ticks.x = element_blank()
  ) +
  geom_hline(aes(yintercept = mean_decadal_tmp), color = "red") +
  labs(x = NULL, y = "Sea bottom temperature (C)") 
#ggsave("Z:/cod and haddock/species shift/projection_temps.pdf", width = 8, height = 4)
```

*Mean monthly bottom temps by decade/year, red line indicates the decadal average. Bars represent mean monthly temp +/- 1.96 x standard dev.*

### Historical by year and projected

```{r bottom-temp-plot3, echo = FALSE, fig.height=6, fig.width=10}
ggplot(historical_and_projections_annual, aes(month, mean_temp)) +
  geom_point() +
  geom_errorbar(aes(ymin = lower, ymax = upper)) +
  facet_wrap(~decade, nrow = 1) +
  theme(
    axis.text.x = element_blank(),
    strip.text = element_text(size = 7, margin = margin()),
    axis.ticks.x = element_blank()
  ) +
  geom_hline(aes(yintercept = mean_decadal_tmp), color = "red") +
  labs(x = NULL, y = "Sea bottom temperature (C)") +
  ggtitle("Historical and projected average monthly sea bottom temperatures in the Gulf of Maine by year/decade")
```

*Mean monthly bottom temps by decade/year, red line indicates the decadal average. Bars represent mean monthly temp +/- 1.96 x standard dev.*

<!--
## Model input projected catch-trip-data
```{r echo = FALSE}
final_result<- read_excel(paste0(output_data_cd,"model_input_proj_data.xlsx"))  #save the data

head(final_result)
```
-->

## Regulations, effort by state and year {.tabset}
```{r echo = FALSE,  fig.width=10}
# Load data
df<-data.frame(read_csv("E:/Lou's projects/welfare-model-GoM/input_data/directed trips and regulations 2010_2020_disaggregated.csv"), show_col_types = FALSE)

# Filter for 2019-2021
df_filtered <- df %>%
  dplyr::filter(year>2018)

df_filtered <- df_filtered %>%
  dplyr::mutate(
    cod_open = cod_bag > 0,
    haddock_open = hadd_bag > 0) 
``` 

### Directed trips
```{r echo = FALSE,  fig.width=10}
ggplot(df_filtered, aes(x = factor(period), y = dtrip, fill = factor(year), group = year)) +
  geom_bar(stat = "identity", position = "dodge") +
  facet_wrap(~ mode) +
  labs(
    title = "Directed Trips by Period and Year",
    x = "Period (half-month)",
    y = "Directed Trips",
    color = "Year"
  ) +
  theme_minimal()
``` 

### Haddock bag limits
```{r echo = FALSE,  fig.width=10}
ggplot(df_filtered, aes(x = factor(period), y = hadd_bag, fill = factor(year), group = year)) +
  geom_bar(stat = "identity", position = "dodge") +
  facet_wrap(~ mode) +
  labs(
    title = "Haddock Bag Limits by Period and Year",
    x = "Period (half-month)",
    y = "Haddock Bag Limit",
    color = "Year"
  ) +
  theme_minimal()

``` 

### Cod bag limits
```{r echo = FALSE,  fig.width=10}
ggplot(df_filtered, aes(x = factor(period), y = cod_bag, fill = factor(year), group = year)) +
  geom_bar(stat = "identity", position = "dodge") +
  facet_wrap(~ mode) +
  labs(
    title = "Cod Bag Limits by Period and Year",
    x = "Period (half-month)",
    y = "Cod Bag Limit",
    color = "Year"
  ) +
  theme_minimal()
``` 

### Directed trips by state
```{r echo = FALSE,  fig.width=10}
ggplot(df_filtered, aes(x = factor(st), y = dtrip, fill = factor(year))) +
  geom_bar(stat = "identity", position = "dodge") +
  facet_wrap(~ mode) +
  labs(
    title = "Directed Trips by State and Year",
    x = "State",
    y = "Directed Trips",
    fill = "Year"
  ) +
  theme_minimal()
``` 

### Directed trips by period and cod open status
```{r echo = FALSE,  fig.width=10}
ggplot(df_filtered, aes(x = factor(period), y = dtrip, fill = cod_open)) +
  geom_bar(stat = "identity", position = "dodge") +
  facet_grid(year ~ mode) +
  labs(
    title = "Directed Trips by Period and Cod Season Status",
    x = "Period (half-month)",
    y = "Directed Trips",
    fill = "Cod Open?"
  ) +
  theme_minimal()
```  


## Coastwide decadal projections - welfare  {.tabset}

Each tab contains different projected fishery outcomes across copula models for the case of dependence, independence, and the difference between dependence and independence. Catch data from 2025-04-17. 
```{r echo = FALSE,  fig.width=10}

# Pull in all the data and reformat for plotting 
k_tau_data_combined_coast_list<-list()
k_tau_data_combined_state_list<-list()
k_tau_data_combined_mode_list<-list()
output_summarized1_list<-list()
plot_data_list<-list()
cvtrip_diff_list<-list()
diff_list<-list()

years<-c(2019, 2020, 2021)
for(yr in years){
  
  ktau_data<-read_excel(paste0(output_data_cd,"ktau_output_y", yr, "_outliers_9-21-25.xlsx"))
  ktau_annual<-ktau_data %>% filter(month==0 & domain1=="all") %>% 
    dplyr::select(-k_tau_catch_p, -k_tau_keep_p, -domain1) %>% 
    dplyr::mutate(pct_both_above=(both_above/2000)*100, pct_both_below=(both_below/2000)*100)
  
  ktau_annual_long <- ktau_annual %>%
    mutate(parts = str_split(domain, "_", simplify = TRUE),
           correlation = parts[, 1],
           copula = str_extract(parts[, 2], "^[a-zA-Z]+"),
           decade = str_extract(parts[, 2], "[0-9]+")
    ) %>%
    select(draw, correlation, copula, decade, k_tau_keep_est, k_tau_catch_est, pct_both_above, pct_both_below)
  
  ktau_data_ind<-read_excel(paste0(output_data_cd,"ktau_output_y", yr,"_outliers_9-21-25_ind.xlsx"))
  ktau_annual_ind<-ktau_data_ind %>% filter(month==0 & domain1=="all") %>% 
    dplyr::select(-k_tau_catch_p, -k_tau_keep_p, -domain1)%>% 
    dplyr::mutate(pct_both_above=(both_above/2000)*100, pct_both_below=(both_below/2000)*100)
  
  ktau_annual_ind_long <- ktau_annual_ind %>%
    mutate(parts = str_split(domain, "_", simplify = TRUE),
           correlation = parts[, 1],
           copula = str_extract(parts[, 2], "^[a-zA-Z]+"),
           decade = str_extract(parts[, 2], "[0-9]+")
    ) %>%
    select(draw, correlation, copula, decade, k_tau_keep_est, k_tau_catch_est, pct_both_above, pct_both_below) %>% 
    dplyr::mutate(copula="independent")
  
  k_tau_data_combined_coast<-ktau_annual_ind_long %>%
    plyr::rbind.fill(ktau_annual_long) 
  
  k_tau_data_combined_coast<- k_tau_data_combined_coast %>% 
    dplyr::filter(decade!=0) %>% 
    dplyr::filter(!is.na(decade))
  
  k_tau_data_combined_coast$copula <- factor(k_tau_data_combined_coast$copula,
                                             levels = c("independent", setdiff(unique(k_tau_data_combined_coast$copula), "independent")))
  k_tau_data_combined_coast$base_year<-yr
  
  k_tau_data_combined_coast_list[[yr]]<-k_tau_data_combined_coast
  
  
  # coastwide by state ktau data 
  ktau_data<-read_excel(paste0(output_data_cd,"ktau_output_y", yr, "_outliers_9-21-25.xlsx"))
  ktau_annual<-ktau_data %>% filter(month==0 & domain1 %in% c("ME", "NH", "MA")) %>% 
    dplyr::select(-k_tau_catch_p, -k_tau_keep_p) %>% 
    dplyr::rename(state=domain1) %>% 
    dplyr::mutate(pct_both_above=(both_above/2000)*100, pct_both_below=(both_below/2000)*100)
  
  ktau_annual_long <- ktau_annual %>%
    mutate(parts = str_split(domain, "_", simplify = TRUE),
           correlation = parts[, 1],
           copula = str_extract(parts[, 2], "^[a-zA-Z]+"),
           decade = str_extract(parts[, 2], "[0-9]+")
    ) %>%
    select(draw, correlation, copula, decade, k_tau_keep_est, k_tau_catch_est, state, pct_both_above,pct_both_below)
  
  
  ktau_data_ind<-read_excel(paste0(output_data_cd,"ktau_output_y", yr,"_outliers_9-21-25_ind.xlsx"))
  ktau_annual_ind<-ktau_data_ind %>% filter(month==0 & domain1 %in% c("ME", "NH", "MA")) %>% 
    dplyr::select(-k_tau_catch_p, -k_tau_keep_p) %>% 
    dplyr::rename(state=domain1) %>% 
    dplyr::mutate(pct_both_above=(both_above/2000)*100, pct_both_below=(both_below/2000)*100)
  
  ktau_annual_ind_long <- ktau_annual_ind %>%
    mutate(parts = str_split(domain, "_", simplify = TRUE),
           correlation = parts[, 1],
           copula = str_extract(parts[, 2], "^[a-zA-Z]+"),
           decade = str_extract(parts[, 2], "[0-9]+")
    ) %>%
    select(draw, correlation, copula, decade, k_tau_keep_est, k_tau_catch_est, state, pct_both_above, pct_both_below) %>% 
    dplyr::mutate(copula="independent")
  
  k_tau_data_combined_state<-ktau_annual_ind_long %>% 
    plyr::rbind.fill(ktau_annual_long) 
  
  k_tau_data_combined_state<- k_tau_data_combined_state %>% 
    dplyr::filter(decade!=0) %>% 
    dplyr::filter(!is.na(decade))
  
  k_tau_data_combined_state$copula <- factor(k_tau_data_combined_state$copula,
                                             levels = c("independent", setdiff(unique(k_tau_data_combined_state$copula), "independent")))
  k_tau_data_combined_state$base_year<-yr
  
  k_tau_data_combined_state_list[[yr]]<-k_tau_data_combined_state
  
  # coastwide by mode ktau data 
  ktau_data<-read_excel(paste0(output_data_cd,"ktau_output_y", yr,"_outliers_9-21-25.xlsx"))
  ktau_annual<-ktau_data %>% filter(month==0 & domain1 %in% c("pr", "fh")) %>% 
    dplyr::select(-k_tau_catch_p, -k_tau_keep_p) %>% 
    dplyr::rename(mode=domain1) %>% 
    dplyr::mutate(pct_both_above=(both_above/2000)*100, pct_both_below=(both_below/2000)*100)
  
  ktau_annual_long <- ktau_annual %>%
    mutate(parts = str_split(domain, "_", simplify = TRUE),
           correlation = parts[, 1],
           copula = str_extract(parts[, 2], "^[a-zA-Z]+"),
           decade = str_extract(parts[, 2], "[0-9]+")
    ) %>%
    select(draw, correlation, copula, decade, k_tau_keep_est, k_tau_catch_est, mode, pct_both_above, pct_both_below)
  
  
  ktau_data_ind<-read_excel(paste0(output_data_cd,"ktau_output_y", yr, "_outliers_9-21-25_ind.xlsx"))
  ktau_annual_ind<-ktau_data_ind %>% filter(month==0 & domain1 %in% c("pr", "fh")) %>% 
    dplyr::select(-k_tau_catch_p, -k_tau_keep_p) %>% 
    dplyr::rename(mode=domain1) %>% 
    dplyr::mutate(pct_both_above=(both_above/2000)*100, pct_both_below=(both_below/2000)*100)
  
  ktau_annual_ind_long <- ktau_annual_ind %>%
    mutate(parts = str_split(domain, "_", simplify = TRUE),
           correlation = parts[, 1],
           copula = str_extract(parts[, 2], "^[a-zA-Z]+"),
           decade = str_extract(parts[, 2], "[0-9]+")
    ) %>%
    select(draw, correlation, copula, decade, k_tau_keep_est, k_tau_catch_est, mode, pct_both_above, pct_both_below) %>% 
    dplyr::mutate(copula="independent")
  
  k_tau_data_combined_mode<-ktau_annual_ind_long %>% 
    plyr::rbind.fill(ktau_annual_long) 
  
  k_tau_data_combined_mode<- k_tau_data_combined_mode %>% 
    dplyr::filter(decade!=0) %>% 
    dplyr::filter(!is.na(decade))
  
  k_tau_data_combined_mode$copula <- factor(k_tau_data_combined_mode$copula,
                                            levels = c("independent", setdiff(unique(k_tau_data_combined_mode$copula), "independent")))
  
  
  k_tau_data_combined_mode$base_year<-yr
  
  k_tau_data_combined_mode_list[[yr]]<-k_tau_data_combined_mode
  
  #plot data 
  output_summarized1<- read_rds(paste0(output_data_cd,"model_output_y", yr,"_outliers_9-21-25_reformat_coast.rds"))  %>%
    dplyr::mutate(codreltrip=codrel/ntrips,
                  haddreltrip=haddrel/ntrips, 
                  codrelchoice=codrel/n_choice_occasions,
                  haddrelchoice=haddrel/n_choice_occasions, 
                  cod_hadd_keep=codkeep+haddkeep, 
                  cod_hadd_cat=codcat+haddcat)
  
  output_summarized1$ntrips[is.na(output_summarized1$ntrips)] <- output_summarized1$dtrip[is.na(output_summarized1$ntrips)]
  output_summarized1$copula[output_summarized1$correlation=="independent"] <- "independent"
  output_summarized1$base_year<-yr
  output_summarized1_list[[yr]]<-output_summarized1
  
  plot_data<-output_summarized1 %>% 
    dplyr::filter(decade!=0)
  
  plot_data$base_year<-yr
  plot_data_list[[yr]]<-plot_data
  
  #differences data CV
  output_summarized1<- read_rds(paste0(output_data_cd,"model_output_y", yr,"_outliers_9-21-25_reformat_coast.rds"))  %>%
    dplyr::mutate(codreltrip=codrel/ntrips,
                  haddreltrip=haddrel/ntrips, 
                  codrelchoice=codrel/n_choice_occasions,
                  haddrelchoice=haddrel/n_choice_occasions, 
                  cod_hadd_keep=codkeep+haddkeep, 
                  cod_hadd_cat=codcat+haddcat)
  
  output_summarized1$ntrips[is.na(output_summarized1$ntrips)] <- output_summarized1$dtrip[is.na(output_summarized1$ntrips)]
  
  output_summarized_corr<-output_summarized1 %>% 
    dplyr::filter(correlation=="corr") %>% 
    dplyr::filter(decade!=0) 
  
  output_summarized_ind<-output_summarized1 %>% 
    dplyr::filter(correlation=="independent" ) %>% 
    dplyr::filter(decade!=0) 
  
  cvtrip_diff_corr <- output_summarized_corr %>%
    rename_with(~ paste0(.x, "_corr"), c(cvtrip, cv_choice, cv, ntrips)) %>%
    dplyr::select("draw", "copula","decade","cvtrip_corr", "cv_choice_corr", "cv_corr", "ntrips_corr") %>%     dplyr::filter(decade!=0 )
  
  cvtrip_diff_ind <- output_summarized_ind %>%
    rename_with(~ paste0(.x, "_ind"), c(cvtrip, cv_choice, cv, ntrips)) %>%
    dplyr::select("draw", "copula","decade","cvtrip_ind", "cv_choice_ind", "cv_ind", "ntrips_ind") %>%     dplyr::filter(decade!=0 )
  
  cvtrip_diff<-cvtrip_diff_corr %>% 
    left_join(cvtrip_diff_ind, by=c("draw", "copula","decade" )) %>%
    mutate(diff_ntrips=ntrips_corr- ntrips_ind, 
           diff_cvtrip=cvtrip_corr- cvtrip_ind, 
           diff_cv_choice=cv_choice_corr- cv_choice_ind, 
           diff_cv=cv_corr- cv_ind)
  
  cvtrip_diff$base_year<-yr
  
  cvtrip_diff_list[[yr]]<-cvtrip_diff
  
  #differences data catch
  diff_corr <- output_summarized_corr %>%
    rename_with(~ paste0(.x, "_corr"), c(codkeep, haddkeep, codcat, haddcat, cv,
                                         cod_hadd_keep, cod_hadd_cat, cod_tot_mort, hadd_tot_mort)) %>%
    dplyr::select("draw", "copula","decade","codkeep_corr", "haddkeep_corr", "cv_corr",
                  "codcat_corr", "haddcat_corr", "cod_hadd_keep_corr", "cod_hadd_cat_corr", 
                  "cod_tot_mort_corr", "hadd_tot_mort_corr") %>%   
    dplyr::filter(decade!=0 )
  
  diff_ind <- output_summarized_ind %>%
    rename_with(~ paste0(.x, "_ind"), c(codkeep, haddkeep, codcat, haddcat, cv,
                                        cod_hadd_keep, cod_hadd_cat, cod_tot_mort, hadd_tot_mort)) %>%
    dplyr::select("draw", "copula","decade","codkeep_ind", "haddkeep_ind", "cv_ind",
                  "codcat_ind", "haddcat_ind", "cod_hadd_keep_ind", "cod_hadd_cat_ind", 
                  "cod_tot_mort_ind", "hadd_tot_mort_ind") %>%   
    dplyr::filter(decade!=0 )
  
  diff<-diff_corr %>% 
    left_join(diff_ind, by=c("draw", "copula","decade" )) %>%
    mutate(diff_cv=cv_corr- cv_ind,
           diff_codkeep=codkeep_corr- codkeep_ind, 
           diff_haddkeep=haddkeep_corr- haddkeep_ind, 
           diff_codcat=codcat_corr- codcat_ind, 
           diff_haddcat=haddcat_corr- haddcat_ind, 
           diff_cod_hadd_keep=cod_hadd_keep_corr- cod_hadd_keep_ind, 
           diff_cod_hadd_cat=cod_hadd_cat_corr- cod_hadd_cat_ind, 
           diff_cod_mort=cod_tot_mort_corr- cod_tot_mort_ind, 
           diff_hadd_mort=hadd_tot_mort_corr- hadd_tot_mort_ind, 
           pct_diff_codkeep=((codkeep_corr- codkeep_ind)/codkeep_ind)*100, 
           pct_diff_haddkeep=((haddkeep_corr- haddkeep_ind)/haddkeep_ind)*100, 
           pct_diff_codcat=((codcat_corr- codcat_ind)/codcat_ind)*100, 
           pct_diff_haddcat=((haddcat_corr- haddcat_ind)/haddcat_ind)*100, 
           pct_diff_cod_hadd_keep=((cod_hadd_keep_corr- cod_hadd_keep_ind)/cod_hadd_keep_ind)*100, 
           pct_diff_cod_hadd_cat=((cod_hadd_cat_corr- cod_hadd_cat_ind)/cod_hadd_cat_ind)*100, 
           pct_diff_cod_mort=((cod_tot_mort_corr- cod_tot_mort_ind)/cod_tot_mort_ind)*100, 
           pct_diff_hadd_mort=((hadd_tot_mort_corr- hadd_tot_mort_ind)/hadd_tot_mort_ind)*100, 
           base_year=yr)
  
  diff_list[[yr]]<-diff
  
}

k_tau_data_combined_coast <- dplyr::bind_rows(k_tau_data_combined_coast_list)
k_tau_data_combined_state <- dplyr::bind_rows(k_tau_data_combined_state_list)
k_tau_data_combined_mode <- dplyr::bind_rows(k_tau_data_combined_mode_list)
diff_combined <- dplyr::bind_rows(diff_list)
plot_data_combined <- dplyr::bind_rows(plot_data_list)
cvtrip_diff_combined <- dplyr::bind_rows(cvtrip_diff_list)
output_summarized1_combined<-dplyr::bind_rows(output_summarized1_list)
```

### CV per trip 
```{r echo = FALSE, fig.width=10}
ggplot(plot_data_combined, aes(x = factor(decade), y = cvtrip, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Compensating variation per trip ($)") +
  facet_wrap(~ base_year, ncol = 1)
```

### Difference in CV per trip (corr. - ind.)
```{r echo = FALSE, fig.width=10}
ggplot(cvtrip_diff_combined, aes(x = factor(decade), y = diff_cvtrip, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Difference in CV ($) per trip (corr- ind)") +
  facet_wrap(~ base_year, ncol = 1)
```

### CV per choice occasion
```{r echo = FALSE, fig.width=10}
ggplot(plot_data_combined, aes(x = factor(decade), y = cv_choice, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Compensating variation per choice occasion ($)")+
  facet_wrap(~ base_year, ncol = 1)
```

### Difference in CV per choice occasion (corr. - ind.)
```{r echo = FALSE, fig.width=10}
ggplot(cvtrip_diff_combined, aes(x = factor(decade), y = diff_cv_choice, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Difference in CV ($) per choice occasion (corr- ind)")+
  facet_wrap(~ base_year, ncol = 1)
```

### Total CV
```{r echo = FALSE, fig.width=10}
# plot_data_2019<-plot_data_combined %>%  
# 
# group_medians <- plot_data_combined %>%
#   dplyr::group_by(base_year) %>%
#   dplyr::summarise(median = median(n_choice_occasions, na.rm = TRUE), .groups = "drop")
# 
# # View the medians per group
# print(group_medians)
# 
# # Get the min and max of these medians
# min_median <- min(group_medians$median_cv)
# max_median <- max(group_medians$median_cv)
# 
# min_median/21570873
# max_median/21570873
ggplot(plot_data_combined, aes(x = factor(decade), y = cv, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Compensating variation ($)")+
  facet_wrap(~ base_year, ncol = 1)
```

### Difference in total CV (corr. - ind.)
```{r echo = FALSE, fig.width=10}
# cvtrip_diff_combined1<-cvtrip_diff_combined %>% dplyr::filter(base_year==2019)
# 
# group_medians <- cvtrip_diff_combined1 %>%
#   dplyr::group_by(copula, correlation, decade) %>%
#   dplyr::summarise(median_cv = median(diff_cv, na.rm = TRUE), .groups = "drop")
# 
# # View the medians per group
# print(group_medians)
# 
# # Get the min and max of these medians
# min_median <- min(group_medians$median_cv)
# max_median <- max(group_medians$median_cv)
# 
# min_median/21570873
# max_median/21570873
ggplot(cvtrip_diff_combined, aes(x = factor(decade), y = diff_cv, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Difference total CV ($) (corr- ind)")+
  facet_wrap(~ base_year, ncol = 1)
```

### Total directed trips
```{r echo = FALSE, fig.width=10}
ggplot(plot_data_combined, aes(x = factor(period), y = ntrips, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Number of directed trips")+
  facet_wrap(~ base_year, ncol = 1)
```

### Difference in total directed trips (corr. - ind.)
```{r echo = FALSE, fig.width=10}
ggplot(cvtrip_diff_combined, aes(x = factor(decade), y = diff_ntrips, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Difference in directed trips (dtrips_corr- dtrips_ind)")+
  facet_wrap(~ base_year, ncol = 1)
```

## Coastwide decadal projections - catch outcomes at the trip level  {.tabset}

Catch data from 2025-04-17.

### cod catch per trip
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_combined, aes(x=period, y=codcattrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod catch per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ base_year, ncol = 1)
```

### cod keep per trip
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_combined, aes(x=period, y=codkeeptrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod harvest per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ base_year, ncol = 1)
```

### cod release per trip
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_combined, aes(x=period, y=codreltrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod release per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ base_year, ncol = 1)
```

### haddock catch per trip
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_combined, aes(x=period, y=haddcattrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock catch per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ base_year, ncol = 1)
```

### haddock keep per trip
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_combined, aes(x=period, y=haddkeeptrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock harvest per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ base_year, ncol = 1)
```

### haddock release per trip 
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_combined, aes(x=period, y=haddreltrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock release per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ base_year, ncol = 1)
```

### k-tau catch
```{r echo = FALSE, fig.width=10}
ggplot(k_tau_data_combined_coast, aes(x=decade, y=k_tau_catch_est, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Decade", y = "Kendall's tau")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ base_year, ncol = 1)
```

### k-tau keep
```{r echo = FALSE, fig.width=10}
ggplot(k_tau_data_combined_coast, aes(x=decade, y=k_tau_keep_est, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Decade", y = "Kendall's tau")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ base_year, ncol = 1)
```

### % trips catch equal or below median
```{r echo = FALSE, fig.width=10}
ggplot(k_tau_data_combined_coast, aes(x=decade, y=pct_both_below, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Decade", y = "%")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ base_year, ncol = 1)
```

## Coastwide decadal projections - catch outcomes at the choice occasion level  {.tabset}

Catch data from 2025-04-17.

### cod catch per choice occasion
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_combined, aes(x=period, y=codcatchoice, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod catch per choice occasion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ base_year, ncol = 1)
```

### cod keep per choice occasion
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_combined, aes(x=period, y=codkeepchoice, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod harvest per choice occasion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ base_year, ncol = 1)
```

### cod release per choice occasion
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_combined, aes(x=period, y=codrelchoice, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod release per choice occasion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ base_year, ncol = 1)
```

### haddock catch per choice occasion
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_combined, aes(x=period, y=haddcatchoice, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock catch per choice occasion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ base_year, ncol = 1)
```

### haddock keep per choice occasion
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_combined, aes(x=period, y=haddkeepchoice, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock harvest per choice occassion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ base_year, ncol = 1)
```

### haddock release per choice occasion
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_combined, aes(x=period, y=haddrelchoice, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock release per choice occasion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ base_year, ncol = 1)
```

### cod keep per choice occasion
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_combined, aes(x=period, y=codkeepchoice, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod harvest per choice occasion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ base_year, ncol = 1)
```

### cod release per choice occasion
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_combined, aes(x=period, y=codrelchoice, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod release per choice occasion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ base_year, ncol = 1)
```

### haddock catch per choice occasion
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_combined, aes(x=period, y=haddcatchoice, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock catch per choice occasion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ base_year, ncol = 1)
```

### haddock keep per choice occasion
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_combined, aes(x=period, y=haddkeepchoice, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock harvest per choice occassion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ base_year, ncol = 1)
```

## Coastwide decadal projections by month- catch outcomes at the choice occasion level  {.tabset}

Catch data from 2025-04-17.

```{r echo = FALSE, fig.width=10}
# Pull in all the data and reformat for plotting 
output_summarized1_list<-list()
plot_data_list<-list()
cvtrip_diff_list<-list()
diff_list<-list()

years<-c(2019, 2020, 2021)
for(yr in years){
  #plot data 
  output_summarized1<- read_rds(paste0(output_data_cd,"model_output_y", yr,"_outliers_9-21-25_reformat_coast_mnth.rds"))  %>%
    dplyr::mutate(codreltrip=codrel/ntrips,
                  haddreltrip=haddrel/ntrips, 
                  codrelchoice=codrel/n_choice_occasions,
                  haddrelchoice=haddrel/n_choice_occasions, 
                  cod_hadd_keep=codkeep+haddkeep, 
                  cod_hadd_cat=codcat+haddcat)
  
  output_summarized1$ntrips[is.na(output_summarized1$ntrips)] <- output_summarized1$dtrip[is.na(output_summarized1$ntrips)]
  output_summarized1$copula[output_summarized1$correlation=="independent"] <- "independent"
  output_summarized1$base_year<-yr
  output_summarized1_list[[yr]]<-output_summarized1
  
  plot_data<-output_summarized1 %>% 
    dplyr::filter(decade!=0)
  
  plot_data$base_year<-yr
  plot_data_list[[yr]]<-plot_data
  
  #differences data CV
  output_summarized1<- read_rds(paste0(output_data_cd,"model_output_y", yr,"_outliers_9-21-25_reformat_coast_mnth.rds"))  %>%
    dplyr::mutate(codreltrip=codrel/ntrips,
                  haddreltrip=haddrel/ntrips, 
                  codrelchoice=codrel/n_choice_occasions,
                  haddrelchoice=haddrel/n_choice_occasions, 
                  cod_hadd_keep=codkeep+haddkeep, 
                  cod_hadd_cat=codcat+haddcat)
  
  output_summarized1$ntrips[is.na(output_summarized1$ntrips)] <- output_summarized1$dtrip[is.na(output_summarized1$ntrips)]
  
  output_summarized_corr<-output_summarized1 %>% 
    dplyr::filter(correlation=="corr") %>% 
    dplyr::filter(decade!=0) 
  
  output_summarized_ind<-output_summarized1 %>% 
    dplyr::filter(correlation=="independent" ) %>% 
    dplyr::filter(decade!=0) 
  
  cvtrip_diff_corr <- output_summarized_corr %>%
    rename_with(~ paste0(.x, "_corr"), c(cvtrip, cv_choice, cv, ntrips)) %>%
    dplyr::select("draw", "month", "copula","decade","cvtrip_corr", "cv_choice_corr", "cv_corr", "ntrips_corr") %>%     dplyr::filter(decade!=0 )
  
  cvtrip_diff_ind <- output_summarized_ind %>%
    rename_with(~ paste0(.x, "_ind"), c(cvtrip, cv_choice, cv, ntrips)) %>%
    dplyr::select("draw", "month", "copula","decade","cvtrip_ind", "cv_choice_ind", "cv_ind", "ntrips_ind") %>%     dplyr::filter(decade!=0 )
  
  cvtrip_diff<-cvtrip_diff_corr %>% 
    left_join(cvtrip_diff_ind, by=c("draw", "copula","decade", "month" )) %>%
    mutate(diff_ntrips=ntrips_corr- ntrips_ind, 
           diff_cvtrip=cvtrip_corr- cvtrip_ind, 
           diff_cv_choice=cv_choice_corr- cv_choice_ind, 
           diff_cv=cv_corr- cv_ind)
  
  cvtrip_diff$base_year<-yr
  
  cvtrip_diff_list[[yr]]<-cvtrip_diff
  
  #differences data catch
  diff_corr <- output_summarized_corr %>%
    rename_with(~ paste0(.x, "_corr"), c(codkeep, haddkeep, codcat, haddcat, cv,
                                         cod_hadd_keep, cod_hadd_cat, cod_tot_mort, hadd_tot_mort)) %>%
    dplyr::select("draw", "month", "copula","decade","codkeep_corr", "haddkeep_corr", "cv_corr",
                  "codcat_corr", "haddcat_corr", "cod_hadd_keep_corr", "cod_hadd_cat_corr", 
                  "cod_tot_mort_corr", "hadd_tot_mort_corr") %>%   
    dplyr::filter(decade!=0 )
  
  diff_ind <- output_summarized_ind %>%
    rename_with(~ paste0(.x, "_ind"), c(codkeep, haddkeep, codcat, haddcat, cv,
                                        cod_hadd_keep, cod_hadd_cat, cod_tot_mort, hadd_tot_mort)) %>%
    dplyr::select("draw", "month", "copula","decade","codkeep_ind", "haddkeep_ind", "cv_ind",
                  "codcat_ind", "haddcat_ind", "cod_hadd_keep_ind", "cod_hadd_cat_ind", 
                  "cod_tot_mort_ind", "hadd_tot_mort_ind") %>%   
    dplyr::filter(decade!=0 )
  
  diff<-diff_corr %>% 
    left_join(diff_ind, by=c("draw", "copula","decade","month"  )) %>%
    mutate(diff_cv=cv_corr- cv_ind,
           diff_codkeep=codkeep_corr- codkeep_ind, 
           diff_haddkeep=haddkeep_corr- haddkeep_ind, 
           diff_codcat=codcat_corr- codcat_ind, 
           diff_haddcat=haddcat_corr- haddcat_ind, 
           diff_cod_hadd_keep=cod_hadd_keep_corr- cod_hadd_keep_ind, 
           diff_cod_hadd_cat=cod_hadd_cat_corr- cod_hadd_cat_ind, 
           diff_cod_mort=cod_tot_mort_corr- cod_tot_mort_ind, 
           diff_hadd_mort=hadd_tot_mort_corr- hadd_tot_mort_ind, 
           pct_diff_codkeep=((codkeep_corr- codkeep_ind)/codkeep_ind)*100, 
           pct_diff_haddkeep=((haddkeep_corr- haddkeep_ind)/haddkeep_ind)*100, 
           pct_diff_codcat=((codcat_corr- codcat_ind)/codcat_ind)*100, 
           pct_diff_haddcat=((haddcat_corr- haddcat_ind)/haddcat_ind)*100, 
           pct_diff_cod_hadd_keep=((cod_hadd_keep_corr- cod_hadd_keep_ind)/cod_hadd_keep_ind)*100, 
           pct_diff_cod_hadd_cat=((cod_hadd_cat_corr- cod_hadd_cat_ind)/cod_hadd_cat_ind)*100, 
           pct_diff_cod_mort=((cod_tot_mort_corr- cod_tot_mort_ind)/cod_tot_mort_ind)*100, 
           pct_diff_hadd_mort=((hadd_tot_mort_corr- hadd_tot_mort_ind)/hadd_tot_mort_ind)*100, 
           base_year=yr)
  
  diff_list[[yr]]<-diff
  
}
diff_combined_mnth <- dplyr::bind_rows(diff_list)
plot_data_combined_mnth <- dplyr::bind_rows(plot_data_list)
cvtrip_diff_combined_mnth <- dplyr::bind_rows(cvtrip_diff_list)
output_summarized1_combined_mnth<-dplyr::bind_rows(output_summarized1_list)
```

### cod catch per choice occasion by month and baseline year
```{r echo = FALSE, fig.width=10}
output_summarized1_combined_mnth_dec<-output_summarized1_combined_mnth %>% 
  dplyr::filter(period %in% c("2019", "2020", "2021")) %>% 
  dplyr::mutate(period2 = paste(period, month, sep = "-"))

ggplot(output_summarized1_combined_mnth_dec,
       aes(x = factor(month), y = codcatchoice)) +
  geom_boxplot() +
  labs(x = "Month", y = "Cod catch per choice occasion") +
  theme(axis.text.x = element_text(hjust = 1)) +
  facet_wrap(~ base_year, ncol = 1) +
  scale_x_discrete(labels = month.abb)
```

### haddock catch per choice occasion by month and baseline year
```{r echo = FALSE, fig.width=10}
output_summarized1_combined_mnth_dec<-output_summarized1_combined_mnth %>% 
  dplyr::filter(period %in% c("2019", "2020", "2021")) %>% 
  dplyr::mutate(period2 = paste(period, month, sep = "-"))

ggplot(output_summarized1_combined_mnth_dec,
       aes(x = factor(month), y = haddcatchoice)) +
  geom_boxplot() +
  labs(x = "Month", y = "Haddock catch per choice occasion") +
  theme(axis.text.x = element_text(hjust = 1)) +
  facet_wrap(~ base_year, ncol = 1) +
  scale_x_discrete(labels = month.abb)
```

### cod catch per choice occasion by month - Decade 1 projections
```{r echo = FALSE, fig.width=10}
output_summarized1_combined_mnth_dec<-output_summarized1_combined_mnth %>% 
  dplyr::filter(period %in% c("Decade 1")) %>% 
  dplyr::mutate(period2 = paste(period, month, sep = "-"))
                
ggplot(output_summarized1_combined_mnth_dec, aes(x=period2, y=codcatchoice, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Month", y = "Cod catch per choice occasion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ base_year, ncol = 1)
```

### haddock catch per choice occasion by month - Decade 1 projections
```{r echo = FALSE, fig.width=10}              
ggplot(output_summarized1_combined_mnth_dec, aes(x=period2, y=haddcatchoice, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Month", y = "Haddock catch per choice occasion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ base_year, ncol = 1)
```

### cod catch per choice occasion by month - Decade 6 projections
```{r echo = FALSE, fig.width=10}
output_summarized1_combined_mnth_dec<-output_summarized1_combined_mnth %>% 
  dplyr::filter(period %in% c("Decade 6")) %>% 
  dplyr::mutate(period2 = paste(period, month, sep = "-"))
                
ggplot(output_summarized1_combined_mnth_dec, aes(x=period2, y=codcatchoice, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Month", y = "Cod catch per choice occasion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ base_year, ncol = 1)
```

### haddock catch per choice occasion by month - Decade 6 projections
```{r echo = FALSE, fig.width=10}              
ggplot(output_summarized1_combined_mnth_dec, aes(x=period2, y=haddcatchoice, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Month", y = "Haddock catch per choice occasion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ base_year, ncol = 1)
```

## Coastwide decadal projections - aggregate catch outcomes  {.tabset}

### cod harvest 
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_combined, aes(x=period, y=codkeep, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod harvest")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ base_year, ncol = 1)
```

### haddock harvest 
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_combined, aes(x=period, y=haddkeep, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock harvest")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ base_year, ncol = 1)
```

### cod total mortality 
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_combined, aes(x=period, y=cod_tot_mort, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod total mortality")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ base_year, ncol = 1)
```

### haddock total mortality  
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_combined, aes(x=period, y=hadd_tot_mort, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock total mortality")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ base_year, ncol = 1)
```

### cod plus haddock harvest 
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_combined, aes(x=period, y=cod_hadd_keep, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod plus haddock harvest")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ base_year, ncol = 1)
```

### cod catch 
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_combined, aes(x=period, y=codcat, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod catch")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ base_year, ncol = 1)
```

### haddock catch 
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_combined, aes(x=period, y=haddcat, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock catch")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ base_year, ncol = 1)
```

### cod plus haddock catch 
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_combined, aes(x=period, y=cod_hadd_cat, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod plus haddock catch")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### Diff. total cod harvest
```{r echo = FALSE, fig.width=10}
ggplot(diff_combined, aes(x = factor(decade), y = diff_codkeep, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Difference in total cod harvest (corr- ind)")+
  facet_wrap(~ base_year, ncol = 1)
```

### Diff. total cod catch
```{r echo = FALSE, fig.width=10}
ggplot(diff_combined, aes(x = factor(decade), y = diff_codcat, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Difference in total cod catch (corr- ind)")+
  facet_wrap(~ base_year, ncol = 1)
```

### Diff. total haddock harvest
```{r echo = FALSE, fig.width=10}
ggplot(diff, aes(x = factor(decade), y = diff_haddkeep, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Difference in total haddock harvest (corr- ind)")+
  facet_wrap(~ base_year, ncol = 1)
```

### Diff. total haddock catch
```{r echo = FALSE, fig.width=10}
ggplot(diff_combined, aes(x = factor(decade), y = diff_haddcat, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Difference in total haddock catch (corr- ind)")+
  facet_wrap(~ base_year, ncol = 1)
```

### Diff. total cod mortality
```{r echo = FALSE, fig.width=10}
ggplot(diff_combined, aes(x = factor(decade), y = diff_cod_mort, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Difference in total cod mortality (corr- ind)")+
  facet_wrap(~ base_year, ncol = 1)
```

### Diff. total haddock mortality
```{r echo = FALSE, fig.width=10}
ggplot(diff_combined, aes(x = factor(decade), y = diff_hadd_mort, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Difference in total haddock mortality (corr- ind)")
```

### Diff. total cod plus haddock harvest
```{r echo = FALSE, fig.width=10}
ggplot(diff_combined, aes(x = factor(decade), y = diff_cod_hadd_keep, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Difference in total cod plus haddock harvest (corr- ind)")+
  facet_wrap(~ base_year, ncol = 1)
```

### Diff. total cod plus haddock catch
```{r echo = FALSE, fig.width=10}
ggplot(diff_combined, aes(x = factor(decade), y = diff_cod_hadd_cat, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Difference in total cod plus haddock catch (corr- ind)")+
  facet_wrap(~ base_year, ncol = 1)
```

### Pct. diff. total cod harvest
```{r echo = FALSE, fig.width=10}
ggplot(diff_combined, aes(x = factor(decade), y = pct_diff_codkeep, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "% diff in total cod harvest ((corr- ind)/ind)*100")+
  facet_wrap(~ base_year, ncol = 1)
```

### Pct. diff. total cod catch
```{r echo = FALSE, fig.width=10}
ggplot(diff_combined, aes(x = factor(decade), y = pct_diff_codcat, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "% diff in total cod harvest ((corr- ind)/ind)*100")+
  facet_wrap(~ base_year, ncol = 1)
```

### Pct. diff. total haddock harvest
```{r echo = FALSE, fig.width=10}
ggplot(diff_combined, aes(x = factor(decade), y = pct_diff_haddkeep, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "% diff in total haddock harvest ((corr- ind)/ind)*100")+
  facet_wrap(~ base_year, ncol = 1)
```

### Pct. diff. total haddock catch
```{r echo = FALSE, fig.width=10}
ggplot(diff_combined, aes(x = factor(decade), y = pct_diff_haddcat, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "% diff in total haddock catch ((corr- ind)/ind)*100")+
  facet_wrap(~ base_year, ncol = 1)
```

### Pct. diff. total cod mortality
```{r echo = FALSE, fig.width=10}
ggplot(diff_combined, aes(x = factor(decade), y = pct_diff_cod_mort, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "% diff in total cod mortality ((corr- ind)/ind)*100")+
  facet_wrap(~ base_year, ncol = 1)
```

### Pct. diff. total haddock mortality
```{r echo = FALSE, fig.width=10}
ggplot(diff_combined, aes(x = factor(decade), y = pct_diff_hadd_mort, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "% diff in total haddock mortality ((corr- ind)/ind)*100")+
  facet_wrap(~ base_year, ncol = 1)
```

### Pct. diff. total cod plus haddock harvest
```{r echo = FALSE, fig.width=10}
ggplot(diff_combined, aes(x = factor(decade), y = pct_diff_cod_hadd_keep, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "% diff in total cod plus haddock harvest ((corr- ind)/ind)*100")+
  facet_wrap(~ base_year, ncol = 1)
```

### Pct. diff. total cod plus haddock catch
```{r echo = FALSE, fig.width=10}
ggplot(diff_combined, aes(x = factor(decade), y = pct_diff_cod_hadd_cat, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "% diff in total cod plus haddock catch ((corr- ind)/ind)*100")+
  facet_wrap(~ base_year, ncol = 1)
```

## Manuscript figures (base year = 2021) {.tabset}

### Absolute values 
```{r echo = FALSE, fig.width=10}
projection_temps<-historical_and_projections %>% 
  dplyr::filter(is.na(year))

output2<-output_summarized1_combined %>%
  dplyr::filter(!is.na(decade))  %>%
  dplyr::filter(decade!=0 & base_year==2021)  %>%
  dplyr::mutate(decade = dplyr::recode(decade,
                                       `1` = "2021-2030",
                                       `2` = "2031-2040",
                                       `3` = "2041-2050",
                                       `4` = "2051-2060",
                                       `5` = "2061-2070",
                                       `6` = "2071-2080",
                                       `7` = "2081-2090",
                                       `8` = "2091-3000"
  )) 

df_subset <- output2 %>%
  # keep only the independent/independent rows
  dplyr::filter(copula == "independent", correlation == "independent") %>%
  # stratified sample: 100 per decade
  dplyr::group_by(decade) %>%
  dplyr::slice_sample(n = 100) %>%
  dplyr::ungroup()

output2<-output2 %>% 
  dplyr::filter(copula!="independent") 

output2<-output2 %>% 
  plyr::rbind.fill(df_subset) %>% 
  dplyr::mutate(codkeep=codkeep/1000, haddkeep=haddkeep/1000, cv=cv/1000000)


library(ggplot2)
library(patchwork)

# Reorder factor levels so "independent" is first
output2$copula <- factor(output2$copula,
                         levels = c("independent", setdiff(unique(output2$copula), "independent")))

# Shared color scale: no title, single row legend
copula_colors <- scale_color_discrete(
  name = NULL,
  guide = guide_legend(nrow = 1)
)

# 1. Temperatures with decade strip labels
p1 <- ggplot(projection_temps, aes(month, mean_temp)) +
  geom_point() +
  geom_errorbar(aes(ymin = lower, ymax = upper)) +
  facet_wrap(~decade, nrow = 1) +
  geom_hline(aes(yintercept = mean_decadal_tmp), color = "red") +
  labs(x = NULL, y = "Sea bottom\ntemperature (C)") +
  copula_colors +
  theme(
    axis.text.x   = element_blank(),
    axis.ticks.x  = element_blank(),
    strip.text    = element_text(size = 10, margin = margin()),
    legend.position = "none"
  )

# 2. Cod harvest
p2 <- ggplot(output2, aes(y = codkeep, color = copula)) +
  geom_boxplot() +
  facet_wrap(~decade, nrow = 1) +
  labs(x = NULL, y = "Cod harvest\n('000s)") +
  copula_colors +
  theme(
    axis.text.x   = element_blank(),
    axis.ticks.x  = element_blank(),
    strip.text    = element_blank(),
    legend.position = "none"
  )

# 3. Haddock harvest
p3 <- ggplot(output2, aes(y = haddkeep, color = copula)) +
  geom_boxplot() +
  facet_wrap(~decade, nrow = 1) +
  labs(x = NULL, y = "Haddock harvest\n('000s)") +
  copula_colors +
  theme(
    axis.text.x   = element_blank(),
    axis.ticks.x  = element_blank(),
    strip.text    = element_blank(),
    legend.position = "none"
  )

# 4. Compensating variation
p4 <- ggplot(output2, aes(y = cv, color = copula)) +
  geom_boxplot() +
  facet_wrap(~decade, nrow = 1) +
  labs(x=NULL,  y = "Compensating\nvariation ($M)") +
  copula_colors +
  theme(
    axis.text.x   = element_blank(),
    axis.ticks.x  = element_blank(),
    strip.text    = element_blank(), 
    legend.title = element_text("Assumed dependance in catch-per-trip residuals"),
  )

# Combine plots with shared legend
final_plot <- (p1 / p2 / p3 / p4) +
  plot_layout(heights = c(1, 1, 1, 1), guides = "collect") &
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal",
    axis.title.y = element_text(size = 9), 
    legend.key = element_blank()
  )

final_plot
```

### Differences 
```{r echo = FALSE, fig.width=10}
projection_temps<-historical_and_projections %>% 
  dplyr::filter(is.na(year))

output2<-diff_combined %>%
  dplyr::mutate(decade = dplyr::recode(decade,
                                       `1` = "2021-2030",
                                       `2` = "2031-2040",
                                       `3` = "2041-2050",
                                       `4` = "2051-2060",
                                       `5` = "2061-2070",
                                       `6` = "2071-2080",
                                       `7` = "2081-2090",
                                       `8` = "2091-3000"
  )) %>% 
  dplyr::filter(!is.na(decade) & base_year==2021) %>% 
  dplyr::mutate(diff_cv=diff_cv/1000000)

library(ggplot2)
library(patchwork)

# Reorder factor levels so "independent" is first
output2$copula <- factor(output2$copula,
                         levels = c("independent", setdiff(unique(output2$copula), "independent")))

# Shared color scale: no title, single row legend
copula_colors <- scale_color_discrete(
  name = NULL,
  guide = guide_legend(nrow = 1)
)

# 1. Temperatures with decade strip labels
p1 <- ggplot(projection_temps, aes(month, mean_temp)) +
  geom_point() +
  geom_errorbar(aes(ymin = lower, ymax = upper)) +
  facet_wrap(~decade, nrow = 1) +
  geom_hline(aes(yintercept = mean_decadal_tmp), color = "red") +
  labs(x = NULL, y = "Sea bottom\ntemperature (C)") +
  copula_colors +
  theme(
    axis.text.x   = element_blank(),
    axis.ticks.x  = element_blank(),
    strip.text    = element_text(size = 10, margin = margin()),
    legend.position = "none"
  )

# 2. Cod harvest
p2 <- ggplot(output2, aes(y = pct_diff_codkeep, color = copula)) +
  geom_boxplot() +
  facet_wrap(~decade, nrow = 1) +
  labs(x = NULL, y = "% difference\ncod harvest") +
  copula_colors +
  theme(
    axis.text.x   = element_blank(),
    axis.ticks.x  = element_blank(),
    strip.text    = element_blank(),
    legend.position = "none"
  )

# 3. Haddock harvest
p3 <- ggplot(output2, aes(y = pct_diff_haddkeep, color = copula)) +
  geom_boxplot() +
  facet_wrap(~decade, nrow = 1) +
  labs(x = NULL, y = "% difference\nhaddock harvest") +
  copula_colors +
  theme(
    axis.text.x   = element_blank(),
    axis.ticks.x  = element_blank(),
    strip.text    = element_blank(),
    legend.position = "none"
  )

# 4. Compensating variation
p4 <- ggplot(output2, aes(y = diff_cv, color = copula)) +
  geom_boxplot() +
  facet_wrap(~decade, nrow = 1) +
  labs(x=NULL,  y = "Diff. compensating\nvariation ($M)") +
  copula_colors +
  theme(
    axis.text.x   = element_blank(),
    axis.ticks.x  = element_blank(),
    strip.text    = element_blank()
  )

# Combine plots with shared legend
final_plot <- (p1 / p2 / p3 / p4) +
  plot_layout(heights = c(1, 1, 1, 1), guides = "collect") &
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal",
    legend.title = element_blank(),
    axis.title.y = element_text(size = 9),
    legend.key = element_blank()
  )

final_plot
```

## Manuscript figures (base year = 2020) {.tabset}

### Absolute values 
```{r echo = FALSE, fig.width=10}
projection_temps<-historical_and_projections %>% 
  dplyr::filter(is.na(year))

output2<-output_summarized1_combined %>%
  dplyr::filter(!is.na(decade))  %>%
  dplyr::filter(decade!=0 & base_year==2020)  %>%
  dplyr::mutate(decade = dplyr::recode(decade,
                                       `1` = "2021-2030",
                                       `2` = "2031-2040",
                                       `3` = "2041-2050",
                                       `4` = "2051-2060",
                                       `5` = "2061-2070",
                                       `6` = "2071-2080",
                                       `7` = "2081-2090",
                                       `8` = "2091-3000"
  )) 

df_subset <- output2 %>%
  # keep only the independent/independent rows
  dplyr::filter(copula == "independent", correlation == "independent") %>%
  # stratified sample: 100 per decade
  dplyr::group_by(decade) %>%
  dplyr::slice_sample(n = 100) %>%
  dplyr::ungroup()

output2<-output2 %>% 
  dplyr::filter(copula!="independent") 

output2<-output2 %>% 
  plyr::rbind.fill(df_subset) %>% 
  dplyr::mutate(codkeep=codkeep/1000, haddkeep=haddkeep/1000, cv=cv/1000000)


library(ggplot2)
library(patchwork)

# Reorder factor levels so "independent" is first
output2$copula <- factor(output2$copula,
                         levels = c("independent", setdiff(unique(output2$copula), "independent")))

# Shared color scale: no title, single row legend
copula_colors <- scale_color_discrete(
  name = NULL,
  guide = guide_legend(nrow = 1)
)

# 1. Temperatures with decade strip labels
p1 <- ggplot(projection_temps, aes(month, mean_temp)) +
  geom_point() +
  geom_errorbar(aes(ymin = lower, ymax = upper)) +
  facet_wrap(~decade, nrow = 1) +
  geom_hline(aes(yintercept = mean_decadal_tmp), color = "red") +
  labs(x = NULL, y = "Sea bottom\ntemperature (C)") +
  copula_colors +
  theme(
    axis.text.x   = element_blank(),
    axis.ticks.x  = element_blank(),
    strip.text    = element_text(size = 10, margin = margin()),
    legend.position = "none"
  )

# 2. Cod harvest
p2 <- ggplot(output2, aes(y = codkeep, color = copula)) +
  geom_boxplot() +
  facet_wrap(~decade, nrow = 1) +
  labs(x = NULL, y = "Cod harvest\n('000s)") +
  copula_colors +
  theme(
    axis.text.x   = element_blank(),
    axis.ticks.x  = element_blank(),
    strip.text    = element_blank(),
    legend.position = "none"
  )

# 3. Haddock harvest
p3 <- ggplot(output2, aes(y = haddkeep, color = copula)) +
  geom_boxplot() +
  facet_wrap(~decade, nrow = 1) +
  labs(x = NULL, y = "Haddock harvest\n('000s)") +
  copula_colors +
  theme(
    axis.text.x   = element_blank(),
    axis.ticks.x  = element_blank(),
    strip.text    = element_blank(),
    legend.position = "none"
  )

# 4. Compensating variation
p4 <- ggplot(output2, aes(y = cv, color = copula)) +
  geom_boxplot() +
  facet_wrap(~decade, nrow = 1) +
  labs(x=NULL,  y = "Compensating\nvariation ($M)") +
  copula_colors +
  theme(
    axis.text.x   = element_blank(),
    axis.ticks.x  = element_blank(),
    strip.text    = element_blank(), 
    legend.title = element_text("Assumed dependance in catch-per-trip residuals"),
  )

# Combine plots with shared legend
final_plot <- (p1 / p2 / p3 / p4) +
  plot_layout(heights = c(1, 1, 1, 1), guides = "collect") &
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal",
    axis.title.y = element_text(size = 9), 
    legend.key = element_blank()
  )

final_plot
```

### Differences 
```{r echo = FALSE, fig.width=10}
projection_temps<-historical_and_projections %>% 
  dplyr::filter(is.na(year))

output2<-diff_combined %>%
  dplyr::mutate(decade = dplyr::recode(decade,
                                       `1` = "2021-2030",
                                       `2` = "2031-2040",
                                       `3` = "2041-2050",
                                       `4` = "2051-2060",
                                       `5` = "2061-2070",
                                       `6` = "2071-2080",
                                       `7` = "2081-2090",
                                       `8` = "2091-3000"
  )) %>% 
  dplyr::filter(!is.na(decade) & base_year==2020) %>% 
  dplyr::mutate(diff_cv=diff_cv/1000000)

library(ggplot2)
library(patchwork)

# Reorder factor levels so "independent" is first
output2$copula <- factor(output2$copula,
                         levels = c("independent", setdiff(unique(output2$copula), "independent")))

# Shared color scale: no title, single row legend
copula_colors <- scale_color_discrete(
  name = NULL,
  guide = guide_legend(nrow = 1)
)

# 1. Temperatures with decade strip labels
p1 <- ggplot(projection_temps, aes(month, mean_temp)) +
  geom_point() +
  geom_errorbar(aes(ymin = lower, ymax = upper)) +
  facet_wrap(~decade, nrow = 1) +
  geom_hline(aes(yintercept = mean_decadal_tmp), color = "red") +
  labs(x = NULL, y = "Sea bottom\ntemperature (C)") +
  copula_colors +
  theme(
    axis.text.x   = element_blank(),
    axis.ticks.x  = element_blank(),
    strip.text    = element_text(size = 10, margin = margin()),
    legend.position = "none"
  )

# 2. Cod harvest
p2 <- ggplot(output2, aes(y = pct_diff_codkeep, color = copula)) +
  geom_boxplot() +
  facet_wrap(~decade, nrow = 1) +
  labs(x = NULL, y = "% difference\ncod harvest") +
  copula_colors +
  theme(
    axis.text.x   = element_blank(),
    axis.ticks.x  = element_blank(),
    strip.text    = element_blank(),
    legend.position = "none"
  )

# 3. Haddock harvest
p3 <- ggplot(output2, aes(y = pct_diff_haddkeep, color = copula)) +
  geom_boxplot() +
  facet_wrap(~decade, nrow = 1) +
  labs(x = NULL, y = "% difference\nhaddock harvest") +
  copula_colors +
  theme(
    axis.text.x   = element_blank(),
    axis.ticks.x  = element_blank(),
    strip.text    = element_blank(),
    legend.position = "none"
  )

# 4. Compensating variation
p4 <- ggplot(output2, aes(y = diff_cv, color = copula)) +
  geom_boxplot() +
  facet_wrap(~decade, nrow = 1) +
  labs(x=NULL,  y = "Diff. compensating\nvariation ($M)") +
  copula_colors +
  theme(
    axis.text.x   = element_blank(),
    axis.ticks.x  = element_blank(),
    strip.text    = element_blank()
  )

# Combine plots with shared legend
final_plot <- (p1 / p2 / p3 / p4) +
  plot_layout(heights = c(1, 1, 1, 1), guides = "collect") &
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal",
    legend.title = element_blank(),
    axis.title.y = element_text(size = 9),
    legend.key = element_blank()
  )

final_plot
```

## Manuscript figures (base year = 2019) {.tabset}

### Absolute values 
```{r echo = FALSE, fig.width=10}
projection_temps<-historical_and_projections %>% 
  dplyr::filter(is.na(year))

output2<-output_summarized1_combined %>%
  dplyr::filter(!is.na(decade))  %>%
  dplyr::filter(decade!=0 & base_year==2019)  %>%
  dplyr::mutate(decade = dplyr::recode(decade,
                                       `1` = "2021-2030",
                                       `2` = "2031-2040",
                                       `3` = "2041-2050",
                                       `4` = "2051-2060",
                                       `5` = "2061-2070",
                                       `6` = "2071-2080",
                                       `7` = "2081-2090",
                                       `8` = "2091-3000"
  )) 

df_subset <- output2 %>%
  # keep only the independent/independent rows
  dplyr::filter(copula == "independent", correlation == "independent") %>%
  # stratified sample: 100 per decade
  dplyr::group_by(decade) %>%
  dplyr::slice_sample(n = 100) %>%
  dplyr::ungroup()

output2<-output2 %>% 
  dplyr::filter(copula!="independent") 

output2<-output2 %>% 
  plyr::rbind.fill(df_subset) %>% 
  dplyr::mutate(codkeep=codkeep/1000, haddkeep=haddkeep/1000, cv=cv/1000000)


library(ggplot2)
library(patchwork)

# Reorder factor levels so "independent" is first
output2$copula <- factor(output2$copula,
                         levels = c("independent", setdiff(unique(output2$copula), "independent")))

# Shared color scale: no title, single row legend
copula_colors <- scale_color_discrete(
  name = NULL,
  guide = guide_legend(nrow = 1)
)

# 1. Temperatures with decade strip labels
p1 <- ggplot(projection_temps, aes(month, mean_temp)) +
  geom_point() +
  geom_errorbar(aes(ymin = lower, ymax = upper)) +
  facet_wrap(~decade, nrow = 1) +
  geom_hline(aes(yintercept = mean_decadal_tmp), color = "red") +
  labs(x = NULL, y = "Sea bottom\ntemperature (C)") +
  copula_colors +
  theme(
    axis.text.x   = element_blank(),
    axis.ticks.x  = element_blank(),
    strip.text    = element_text(size = 10, margin = margin()),
    legend.position = "none"
  )

# 2. Cod harvest
p2 <- ggplot(output2, aes(y = codkeep, color = copula)) +
  geom_boxplot() +
  facet_wrap(~decade, nrow = 1) +
  labs(x = NULL, y = "Cod harvest\n('000s)") +
  copula_colors +
  theme(
    axis.text.x   = element_blank(),
    axis.ticks.x  = element_blank(),
    strip.text    = element_blank(),
    legend.position = "none"
  )

# 3. Haddock harvest
p3 <- ggplot(output2, aes(y = haddkeep, color = copula)) +
  geom_boxplot() +
  facet_wrap(~decade, nrow = 1) +
  labs(x = NULL, y = "Haddock harvest\n('000s)") +
  copula_colors +
  theme(
    axis.text.x   = element_blank(),
    axis.ticks.x  = element_blank(),
    strip.text    = element_blank(),
    legend.position = "none"
  )

# 4. Compensating variation
p4 <- ggplot(output2, aes(y = cv, color = copula)) +
  geom_boxplot() +
  facet_wrap(~decade, nrow = 1) +
  labs(x=NULL,  y = "Compensating\nvariation ($M)") +
  copula_colors +
  theme(
    axis.text.x   = element_blank(),
    axis.ticks.x  = element_blank(),
    strip.text    = element_blank(), 
    legend.title = element_text("Assumed dependance in catch-per-trip residuals"),
  )

# Combine plots with shared legend
final_plot <- (p1 / p2 / p3 / p4) +
  plot_layout(heights = c(1, 1, 1, 1), guides = "collect") &
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal",
    axis.title.y = element_text(size = 9), 
    legend.key = element_blank()
  )

final_plot
```

### Differences 
```{r echo = FALSE, fig.width=10}
projection_temps<-historical_and_projections %>% 
  dplyr::filter(is.na(year))

output2<-diff_combined %>%
  dplyr::mutate(decade = dplyr::recode(decade,
                                       `1` = "2021-2030",
                                       `2` = "2031-2040",
                                       `3` = "2041-2050",
                                       `4` = "2051-2060",
                                       `5` = "2061-2070",
                                       `6` = "2071-2080",
                                       `7` = "2081-2090",
                                       `8` = "2091-3000"
  )) %>% 
  dplyr::filter(!is.na(decade) & base_year==2019) %>% 
  dplyr::mutate(diff_cv=diff_cv/1000000)

library(ggplot2)
library(patchwork)

# Reorder factor levels so "independent" is first
output2$copula <- factor(output2$copula,
                         levels = c("independent", setdiff(unique(output2$copula), "independent")))

# Shared color scale: no title, single row legend
copula_colors <- scale_color_discrete(
  name = NULL,
  guide = guide_legend(nrow = 1)
)

# 1. Temperatures with decade strip labels
p1 <- ggplot(projection_temps, aes(month, mean_temp)) +
  geom_point() +
  geom_errorbar(aes(ymin = lower, ymax = upper)) +
  facet_wrap(~decade, nrow = 1) +
  geom_hline(aes(yintercept = mean_decadal_tmp), color = "red") +
  labs(x = NULL, y = "Sea bottom\ntemperature (C)") +
  copula_colors +
  theme(
    axis.text.x   = element_blank(),
    axis.ticks.x  = element_blank(),
    strip.text    = element_text(size = 10, margin = margin()),
    legend.position = "none"
  )

# 2. Cod harvest
p2 <- ggplot(output2, aes(y = pct_diff_codkeep, color = copula)) +
  geom_boxplot() +
  facet_wrap(~decade, nrow = 1) +
  labs(x = NULL, y = "% difference\ncod harvest") +
  copula_colors +
  theme(
    axis.text.x   = element_blank(),
    axis.ticks.x  = element_blank(),
    strip.text    = element_blank(),
    legend.position = "none"
  )

# 3. Haddock harvest
p3 <- ggplot(output2, aes(y = pct_diff_haddkeep, color = copula)) +
  geom_boxplot() +
  facet_wrap(~decade, nrow = 1) +
  labs(x = NULL, y = "% difference\nhaddock harvest") +
  copula_colors +
  theme(
    axis.text.x   = element_blank(),
    axis.ticks.x  = element_blank(),
    strip.text    = element_blank(),
    legend.position = "none"
  )

# 4. Compensating variation
p4 <- ggplot(output2, aes(y = diff_cv, color = copula)) +
  geom_boxplot() +
  facet_wrap(~decade, nrow = 1) +
  labs(x=NULL,  y = "Diff. compensating\nvariation ($M)") +
  copula_colors +
  theme(
    axis.text.x   = element_blank(),
    axis.ticks.x  = element_blank(),
    strip.text    = element_blank()
  )

# Combine plots with shared legend
final_plot <- (p1 / p2 / p3 / p4) +
  plot_layout(heights = c(1, 1, 1, 1), guides = "collect") &
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal",
    legend.title = element_blank(),
    axis.title.y = element_text(size = 9),
    legend.key = element_blank()
  )

final_plot
```

## Fishing-mode level decadal projections - welfare  {.tabset}

Each tab contains different projected fishery outcomes across copula models for the case of dependence, independence, and the difference between dependence and independence. Catch data from 2025-04-17. 
```{r echo = FALSE,  fig.width=10}

# Pull in all the data and reformat for plotting 
output_summarized1_mode_list<-list()
plot_data_mode_list<-list()
cvtrip_diff_mode_list<-list()
diff_mode_list<-list()

years<-c(2019, 2020, 2021)
for(yr in years){
  
  #plot data 
  output_summarized1<- read_rds(paste0(output_data_cd,"model_output_y",yr,"_outliers_9-21-25_reformat_mode.rds"))  %>%
    dplyr::mutate(codreltrip=codrel/ntrips,
                  haddreltrip=haddrel/ntrips, 
                  codrelchoice=codrel/n_choice_occasions,
                  haddrelchoice=haddrel/n_choice_occasions, 
                  cod_hadd_keep=codkeep+haddkeep, 
                  cod_hadd_cat=codcat+haddcat)
  
  output_summarized1$ntrips[is.na(output_summarized1$ntrips)] <- output_summarized1$dtrip[is.na(output_summarized1$ntrips)]
  output_summarized1$copula[output_summarized1$correlation=="independent"] <- "independent"
  output_summarized1$base_year<-yr
  output_summarized1_mode_list[[yr]]<-output_summarized1
  
  plot_data<-output_summarized1 %>% 
    dplyr::filter(decade!=0)
  
  plot_data$base_year<-yr
  plot_data_mode_list[[yr]]<-plot_data
  
  #differences data CV
  output_summarized1<- read_rds(paste0(output_data_cd,"model_output_y", yr,"_outliers_9-21-25_reformat_mode.rds"))  %>%
    dplyr::mutate(codreltrip=codrel/ntrips,
                  haddreltrip=haddrel/ntrips, 
                  codrelchoice=codrel/n_choice_occasions,
                  haddrelchoice=haddrel/n_choice_occasions, 
                  cod_hadd_keep=codkeep+haddkeep, 
                  cod_hadd_cat=codcat+haddcat)
  
  output_summarized1$ntrips[is.na(output_summarized1$ntrips)] <- output_summarized1$dtrip[is.na(output_summarized1$ntrips)]
  
  output_summarized_corr<-output_summarized1 %>% 
    dplyr::filter(correlation=="corr") %>% 
    dplyr::filter(decade!=0) 
  
  output_summarized_ind<-output_summarized1 %>% 
    dplyr::filter(correlation=="independent" ) %>% 
    dplyr::filter(decade!=0) 
  
  cvtrip_diff_corr <- output_summarized_corr %>%
    rename_with(~ paste0(.x, "_corr"), c(cvtrip, cv_choice, cv, ntrips)) %>%
    dplyr::select("draw", "copula","decade","cvtrip_corr", "cv_choice_corr", "cv_corr", "ntrips_corr", "mode") %>%     dplyr::filter(decade!=0 )
  
  cvtrip_diff_ind <- output_summarized_ind %>%
    rename_with(~ paste0(.x, "_ind"), c(cvtrip, cv_choice, cv, ntrips)) %>%
    dplyr::select("draw", "copula","decade","cvtrip_ind", "cv_choice_ind", "cv_ind", "ntrips_ind", "mode") %>%     dplyr::filter(decade!=0 )
  
  cvtrip_diff<-cvtrip_diff_corr %>% 
    left_join(cvtrip_diff_ind, by=c("draw", "copula","decade", "mode" )) %>%
    mutate(diff_ntrips=ntrips_corr- ntrips_ind, 
           diff_cvtrip=cvtrip_corr- cvtrip_ind, 
           diff_cv_choice=cv_choice_corr- cv_choice_ind, 
           diff_cv=cv_corr- cv_ind)
  
  cvtrip_diff$base_year<-yr
  
  cvtrip_diff_mode_list[[yr]]<-cvtrip_diff
  
  #differences data catch
  diff_corr <- output_summarized_corr %>%
    rename_with(~ paste0(.x, "_corr"), c(codkeep, haddkeep, codcat, haddcat, cv,
                                         cod_hadd_keep, cod_hadd_cat, cod_tot_mort, hadd_tot_mort)) %>%
    dplyr::select("draw", "copula","decade","codkeep_corr", "haddkeep_corr", "cv_corr",
                  "codcat_corr", "haddcat_corr", "cod_hadd_keep_corr", "cod_hadd_cat_corr", 
                  "cod_tot_mort_corr", "hadd_tot_mort_corr", "mode") %>%   
    dplyr::filter(decade!=0 )
  
  diff_ind <- output_summarized_ind %>%
    rename_with(~ paste0(.x, "_ind"), c(codkeep, haddkeep, codcat, haddcat, cv,
                                        cod_hadd_keep, cod_hadd_cat, cod_tot_mort, hadd_tot_mort)) %>%
    dplyr::select("draw", "copula","decade","codkeep_ind", "haddkeep_ind", "cv_ind",
                  "codcat_ind", "haddcat_ind", "cod_hadd_keep_ind", "cod_hadd_cat_ind", 
                  "cod_tot_mort_ind", "hadd_tot_mort_ind", "mode") %>%   
    dplyr::filter(decade!=0 )
  
  diff<-diff_corr %>% 
    left_join(diff_ind, by=c("draw", "copula","decade", "mode"  )) %>%
    mutate(diff_cv=cv_corr- cv_ind,
           diff_codkeep=codkeep_corr- codkeep_ind, 
           diff_haddkeep=haddkeep_corr- haddkeep_ind, 
           diff_codcat=codcat_corr- codcat_ind, 
           diff_haddcat=haddcat_corr- haddcat_ind, 
           diff_cod_hadd_keep=cod_hadd_keep_corr- cod_hadd_keep_ind, 
           diff_cod_hadd_cat=cod_hadd_cat_corr- cod_hadd_cat_ind, 
           diff_cod_mort=cod_tot_mort_corr- cod_tot_mort_ind, 
           diff_hadd_mort=hadd_tot_mort_corr- hadd_tot_mort_ind, 
           pct_diff_codkeep=((codkeep_corr- codkeep_ind)/codkeep_ind)*100, 
           pct_diff_haddkeep=((haddkeep_corr- haddkeep_ind)/haddkeep_ind)*100, 
           pct_diff_codcat=((codcat_corr- codcat_ind)/codcat_ind)*100, 
           pct_diff_haddcat=((haddcat_corr- haddcat_ind)/haddcat_ind)*100, 
           pct_diff_cod_hadd_keep=((cod_hadd_keep_corr- cod_hadd_keep_ind)/cod_hadd_keep_ind)*100, 
           pct_diff_cod_hadd_cat=((cod_hadd_cat_corr- cod_hadd_cat_ind)/cod_hadd_cat_ind)*100, 
           pct_diff_cod_mort=((cod_tot_mort_corr- cod_tot_mort_ind)/cod_tot_mort_ind)*100, 
           pct_diff_hadd_mort=((hadd_tot_mort_corr- hadd_tot_mort_ind)/hadd_tot_mort_ind)*100, 
           base_year=yr)
  
  diff_mode_list[[yr]]<-diff
  
}

diff_mode_combined <- dplyr::bind_rows(diff_mode_list)
plot_data_mode_combined <- dplyr::bind_rows(plot_data_mode_list)
cvtrip_diff_mode_combined <- dplyr::bind_rows(cvtrip_diff_mode_list)
output_summarized1_mode_combined<-dplyr::bind_rows(output_summarized1_mode_list)
```

### CV per trip
```{r echo = FALSE, fig.width=10}
ggplot(plot_data_mode_combined, aes(x = factor(decade), y = cvtrip, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Compensating variation per trip ($)") +
  facet_wrap(~ interaction(mode, base_year, sep = " - "), ncol = 2)

```

### Difference in CV per trip
```{r echo = FALSE, fig.width=10}
ggplot(cvtrip_diff_mode_combined, aes(x = factor(decade), y = diff_cvtrip, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Difference in CV ($) per trip (corr- ind)") +
  facet_wrap(~ interaction(mode, base_year, sep = " - "), ncol = 2)
```

### CV per choice occasion
```{r echo = FALSE, fig.width=10}
ggplot(plot_data_mode_combined, aes(x = factor(decade), y = cv_choice, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Compensating variation per choice occasion ($)")+
  facet_wrap(~ interaction(mode, base_year, sep = " - "), ncol = 2)
```

### Difference in CV per choice occasion
```{r echo = FALSE, fig.width=10}
ggplot(cvtrip_diff_mode_combined, aes(x = factor(decade), y = diff_cv_choice, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Difference in CV ($) per choice occasion (corr- ind)")+
  facet_wrap(~ interaction(mode, base_year, sep = " - "), ncol = 2)
```

### Total CV
```{r echo = FALSE, fig.width=10}
ggplot(plot_data_mode_combined, aes(x = factor(decade), y = cv, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Compensating variation ($)")+
  facet_wrap(~ interaction(mode, base_year, sep = " - "), ncol = 2)
```

### Difference in total CV
```{r echo = FALSE, fig.width=10}
ggplot(cvtrip_diff_mode_combined, aes(x = factor(decade), y = diff_cv, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Difference total CV ($) (corr- ind)")+
  facet_wrap(~ interaction(mode, base_year, sep = " - "), ncol = 2)
```

### Total directed trips
```{r echo = FALSE, fig.width=10}
ggplot(plot_data_mode_combined, aes(x = factor(period), y = ntrips, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Number of directed trips")+
  facet_wrap(~ interaction(mode, base_year, sep = " - "), ncol = 2)
```

### Difference in total directed trips
```{r echo = FALSE, fig.width=10}
ggplot(cvtrip_diff_mode_combined, aes(x = factor(decade), y = diff_ntrips, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Difference in directed trips (dtrips_corr- dtrips_ind)")+
  facet_wrap(~ interaction(mode, base_year, sep = " - "), ncol = 2)
```

## Fishing-mode level decadal projections - catch outcomes at the trip level  {.tabset}

Catch data from 2025-04-17.

### cod catch per trip
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_mode_combined, aes(x=period, y=codcattrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod catch per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ interaction(mode, base_year, sep = " - "), ncol = 2)
```

### cod keep per trip
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_mode_combined, aes(x=period, y=codkeeptrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod harvest per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ interaction(mode, base_year, sep = " - "), ncol = 2)
```

### cod release per trip
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_mode_combined, aes(x=period, y=codreltrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod release per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ interaction(mode, base_year, sep = " - "), ncol = 2)
```

### haddock catch per trip
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_mode_combined, aes(x=period, y=haddcattrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock catch per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ interaction(mode, base_year, sep = " - "), ncol = 2)
```

### haddock keep per trip
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_mode_combined, aes(x=period, y=haddkeeptrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock harvest per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ interaction(mode, base_year, sep = " - "), ncol = 2)
```

### haddock release per trip 
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_mode_combined, aes(x=period, y=haddreltrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock release per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~ interaction(mode, base_year, sep = " - "), ncol = 2)
```

### k-tau catch
```{r echo = FALSE, fig.width=10}
ggplot(k_tau_data_combined_mode, aes(x=decade, y=k_tau_catch_est, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Decade", y = "Kendall's tau")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~ interaction(mode, base_year, sep = " - "), ncol = 2)
```

### k-tau keep
```{r echo = FALSE, fig.width=10}
ggplot(k_tau_data_combined_mode, aes(x=decade, y=k_tau_keep_est, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Decade", y = "Kendall's tau")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~ interaction(mode, base_year, sep = " - "), ncol = 2)
```

## Fishing-mode decadal projections - catch outcomes at the choice occasion level  {.tabset}

Catch data from 2025-04-17.

### cod catch per choice occasion
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_mode_combined, aes(x=period, y=codcatchoice, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod catch per choice occasion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ interaction(mode, base_year, sep = " - "), ncol = 2)
```

### cod keep per choice occasion
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_mode_combined, aes(x=period, y=codkeepchoice, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod harvest per choice occasion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ interaction(mode, base_year, sep = " - "), ncol = 2)
```

### cod release per choice occasion (correlated)
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_mode_combined, aes(x=period, y=codrelchoice, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod release per choice occasion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ interaction(mode, base_year, sep = " - "), ncol = 2)
```

### haddock catch per choice occasion
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_mode_combined, aes(x=period, y=haddcatchoice, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock catch per choice occasion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ interaction(mode, base_year, sep = " - "), ncol = 2)
```

### haddock keep per choice occasion
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_mode_combined, aes(x=period, y=haddkeepchoice, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock harvest per choice occassion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ interaction(mode, base_year, sep = " - "), ncol = 2)
```

### haddock release per choice occasion
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_mode_combined, aes(x=period, y=haddrelchoice, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock release per choice occasion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ interaction(mode, base_year, sep = " - "), ncol = 2)
```

## Fishing-mode decadal projections - aggregate catch outcomes  {.tabset}

### cod harvest 
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_mode_combined, aes(x=period, y=codkeep, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod harvest")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ interaction(mode, base_year, sep = " - "), ncol = 2)
```

### haddock harvest 
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_mode_combined, aes(x=period, y=haddkeep, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock harvest")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ interaction(mode, base_year, sep = " - "), ncol = 2)
```

### cod plus haddock harvest 
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_mode_combined, aes(x=period, y=cod_hadd_keep, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod plus haddock harvest")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ interaction(mode, base_year, sep = " - "), ncol = 2)
```

### cod catch 
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_mode_combined, aes(x=period, y=codcat, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod catch")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ interaction(mode, base_year, sep = " - "), ncol = 2)
```

### haddock catch 
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_mode_combined, aes(x=period, y=haddcat, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock catch")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ interaction(mode, base_year, sep = " - "), ncol = 2)
```

### cod plus haddock catch 
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_mode_combined, aes(x=period, y=cod_hadd_cat, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod plus haddock catch")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ interaction(mode, base_year, sep = " - "), ncol = 2)
```

### Diff. total cod harvest
```{r echo = FALSE, fig.width=10}
ggplot(diff_mode_combined, aes(x = factor(decade), y = diff_codkeep, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Difference in total cod harvest (corr- ind)")+
  facet_wrap(~ interaction(mode, base_year, sep = " - "), ncol = 2)
```

### Diff. total cod catch
```{r echo = FALSE, fig.width=10}
ggplot(diff_mode_combined, aes(x = factor(decade), y = diff_codcat, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Difference in total cod catch (corr- ind)")+
  facet_wrap(~ interaction(mode, base_year, sep = " - "), ncol = 2)
```

### Diff. total haddock harvest
```{r echo = FALSE, fig.width=10}
ggplot(diff_mode_combined, aes(x = factor(decade), y = diff_haddkeep, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Difference in total haddock harvest (corr- ind)")+
  facet_wrap(~ interaction(mode, base_year, sep = " - "), ncol = 2)
```

### Diff. total haddock catch
```{r echo = FALSE, fig.width=10}
ggplot(diff_mode_combined, aes(x = factor(decade), y = diff_haddcat, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Difference in total haddock catch (corr- ind)")+
  facet_wrap(~ interaction(mode, base_year, sep = " - "), ncol = 2)
```

### Diff. total cod plus haddock harvest
```{r echo = FALSE, fig.width=10}
ggplot(diff_mode_combined, aes(x = factor(decade), y = diff_cod_hadd_keep, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Difference in total cod plus haddock harvest (corr- ind)")+
  facet_wrap(~ interaction(mode, base_year, sep = " - "), ncol = 2)
```

### Diff. total cod plus haddock catch
```{r echo = FALSE, fig.width=10}
ggplot(diff_mode_combined, aes(x = factor(decade), y = diff_cod_hadd_cat, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Difference in total cod plus haddock catch (corr- ind)")+
  facet_wrap(~ interaction(mode, base_year, sep = " - "), ncol = 2)
```

## State-level decadal projections - welfare  {.tabset}

Each tab contains different projected fishery outcomes across copula models for the case of dependence, independence, and the difference between dependence and independence. Catch data from 2025-04-17. 
```{r echo = FALSE,  fig.width=10}
# Pull in all the data and reformat for plotting 
output_summarized1_state_list<-list()
plot_data_state_list<-list()
cvtrip_diff_state_list<-list()
diff_state_list<-list()

years<-c(2019, 2020, 2021)
for(yr in years){
  
  #plot data 
  output_summarized1<- read_rds(paste0(output_data_cd,"model_output_y", yr,"_outliers_9-21-25_reformat_state.rds"))  %>%
    dplyr::mutate(codreltrip=codrel/ntrips,
                  haddreltrip=haddrel/ntrips, 
                  codrelchoice=codrel/n_choice_occasions,
                  haddrelchoice=haddrel/n_choice_occasions, 
                  cod_hadd_keep=codkeep+haddkeep, 
                  cod_hadd_cat=codcat+haddcat)
  
  output_summarized1$ntrips[is.na(output_summarized1$ntrips)] <- output_summarized1$dtrip[is.na(output_summarized1$ntrips)]
  output_summarized1$copula[output_summarized1$correlation=="independent"] <- "independent"
  output_summarized1$base_year<-yr
  output_summarized1_state_list[[yr]]<-output_summarized1
  
  plot_data<-output_summarized1 %>% 
    dplyr::filter(decade!=0)
  
  plot_data$base_year<-yr
  plot_data_state_list[[yr]]<-plot_data
  
  #differences data CV
  output_summarized1<- read_rds(paste0(output_data_cd,"model_output_y", yr,"_outliers_9-21-25_reformat_state.rds"))  %>%
    dplyr::mutate(codreltrip=codrel/ntrips,
                  haddreltrip=haddrel/ntrips, 
                  codrelchoice=codrel/n_choice_occasions,
                  haddrelchoice=haddrel/n_choice_occasions, 
                  cod_hadd_keep=codkeep+haddkeep, 
                  cod_hadd_cat=codcat+haddcat)
  
  output_summarized1$ntrips[is.na(output_summarized1$ntrips)] <- output_summarized1$dtrip[is.na(output_summarized1$ntrips)]
  
  output_summarized_corr<-output_summarized1 %>% 
    dplyr::filter(correlation=="corr") %>% 
    dplyr::filter(decade!=0) 
  
  output_summarized_ind<-output_summarized1 %>% 
    dplyr::filter(correlation=="independent" ) %>% 
    dplyr::filter(decade!=0) 
  
  cvtrip_diff_corr <- output_summarized_corr %>%
    rename_with(~ paste0(.x, "_corr"), c(cvtrip, cv_choice, cv, ntrips)) %>%
    dplyr::select("draw", "copula","decade","cvtrip_corr", "cv_choice_corr", "cv_corr", "ntrips_corr", "state") %>%     dplyr::filter(decade!=0 )
  
  cvtrip_diff_ind <- output_summarized_ind %>%
    rename_with(~ paste0(.x, "_ind"), c(cvtrip, cv_choice, cv, ntrips)) %>%
    dplyr::select("draw", "copula","decade","cvtrip_ind", "cv_choice_ind", "cv_ind", "ntrips_ind", "state") %>%     dplyr::filter(decade!=0 )
  
  cvtrip_diff<-cvtrip_diff_corr %>% 
    left_join(cvtrip_diff_ind, by=c("draw", "copula","decade", "state" )) %>%
    mutate(diff_ntrips=ntrips_corr- ntrips_ind, 
           diff_cvtrip=cvtrip_corr- cvtrip_ind, 
           diff_cv_choice=cv_choice_corr- cv_choice_ind, 
           diff_cv=cv_corr- cv_ind)
  
  cvtrip_diff$base_year<-yr
  
  cvtrip_diff_state_list[[yr]]<-cvtrip_diff
  
  #differences data catch
  diff_corr <- output_summarized_corr %>%
    rename_with(~ paste0(.x, "_corr"), c(codkeep, haddkeep, codcat, haddcat, cv,
                                         cod_hadd_keep, cod_hadd_cat, cod_tot_mort, hadd_tot_mort)) %>%
    dplyr::select("draw", "copula","decade","codkeep_corr", "haddkeep_corr", "cv_corr",
                  "codcat_corr", "haddcat_corr", "cod_hadd_keep_corr", "cod_hadd_cat_corr", 
                  "cod_tot_mort_corr", "hadd_tot_mort_corr", "state") %>%   
    dplyr::filter(decade!=0 )
  
  diff_ind <- output_summarized_ind %>%
    rename_with(~ paste0(.x, "_ind"), c(codkeep, haddkeep, codcat, haddcat, cv,
                                        cod_hadd_keep, cod_hadd_cat, cod_tot_mort, hadd_tot_mort)) %>%
    dplyr::select("draw", "copula","decade","codkeep_ind", "haddkeep_ind", "cv_ind",
                  "codcat_ind", "haddcat_ind", "cod_hadd_keep_ind", "cod_hadd_cat_ind", 
                  "cod_tot_mort_ind", "hadd_tot_mort_ind", "state") %>%   
    dplyr::filter(decade!=0 )
  
  diff<-diff_corr %>% 
    left_join(diff_ind, by=c("draw", "copula","decade", "state"  )) %>%
    mutate(diff_cv=cv_corr- cv_ind,
           diff_codkeep=codkeep_corr- codkeep_ind, 
           diff_haddkeep=haddkeep_corr- haddkeep_ind, 
           diff_codcat=codcat_corr- codcat_ind, 
           diff_haddcat=haddcat_corr- haddcat_ind, 
           diff_cod_hadd_keep=cod_hadd_keep_corr- cod_hadd_keep_ind, 
           diff_cod_hadd_cat=cod_hadd_cat_corr- cod_hadd_cat_ind, 
           diff_cod_mort=cod_tot_mort_corr- cod_tot_mort_ind, 
           diff_hadd_mort=hadd_tot_mort_corr- hadd_tot_mort_ind, 
           pct_diff_codkeep=((codkeep_corr- codkeep_ind)/codkeep_ind)*100, 
           pct_diff_haddkeep=((haddkeep_corr- haddkeep_ind)/haddkeep_ind)*100, 
           pct_diff_codcat=((codcat_corr- codcat_ind)/codcat_ind)*100, 
           pct_diff_haddcat=((haddcat_corr- haddcat_ind)/haddcat_ind)*100, 
           pct_diff_cod_hadd_keep=((cod_hadd_keep_corr- cod_hadd_keep_ind)/cod_hadd_keep_ind)*100, 
           pct_diff_cod_hadd_cat=((cod_hadd_cat_corr- cod_hadd_cat_ind)/cod_hadd_cat_ind)*100, 
           pct_diff_cod_mort=((cod_tot_mort_corr- cod_tot_mort_ind)/cod_tot_mort_ind)*100, 
           pct_diff_hadd_mort=((hadd_tot_mort_corr- hadd_tot_mort_ind)/hadd_tot_mort_ind)*100, 
           base_year=yr)
  
  diff_state_list[[yr]]<-diff
  
}

diff_state_combined <- dplyr::bind_rows(diff_state_list) %>% 
  dplyr::mutate(state = dplyr::recode(state,
                                      `23` = "ME",
                                      `25` = "MA",
                                      `33` = "NH"))
plot_data_state_combined <- dplyr::bind_rows(plot_data_state_list)%>% 
  dplyr::mutate(state = dplyr::recode(state,
                                      `23` = "ME",
                                      `25` = "MA",
                                      `33` = "NH"))

cvtrip_diff_state_combined <- dplyr::bind_rows(cvtrip_diff_state_list)%>% 
  dplyr::mutate(state = dplyr::recode(state,
                                      `23` = "ME",
                                      `25` = "MA",
                                      `33` = "NH"))
output_summarized1_state_combined<-dplyr::bind_rows(output_summarized1_state_list)%>% 
  dplyr::mutate(state = dplyr::recode(state,
                                      `23` = "ME",
                                      `25` = "MA",
                                      `33` = "NH"))


```

### CV per trip
```{r echo = FALSE, fig.width=10}
ggplot(plot_data_state_combined, aes(x = factor(decade), y = cvtrip, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Compensating variation per trip ($)") +
  facet_wrap(~ interaction(state, base_year, sep = " - "), ncol = 3)
```

### Difference in CV per trip
```{r echo = FALSE, fig.width=10}
ggplot(cvtrip_diff_state_combined, aes(x = factor(decade), y = diff_cvtrip, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Difference in CV ($) per trip (corr- ind)") +
  facet_wrap(~ interaction(state, base_year, sep = " - "), ncol = 3)
```

### CV per choice occasion
```{r echo = FALSE, fig.width=10}
ggplot(plot_data_state_combined, aes(x = factor(decade), y = cv_choice, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Compensating variation per choice occasion ($)")+
  facet_wrap(~ interaction(state, base_year, sep = " - "), ncol = 3)
```

### Difference in CV per choice occasion
```{r echo = FALSE, fig.width=10}
ggplot(cvtrip_diff_state_combined, aes(x = factor(decade), y = diff_cv_choice, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Difference in CV ($) per choice occasion (corr- ind)")+
  facet_wrap(~ interaction(state, base_year, sep = " - "), ncol = 3)
```

### Total CV
```{r echo = FALSE, fig.width=10}
ggplot(plot_data_state_combined, aes(x = factor(decade), y = cv, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Compensating variation ($)")+
  facet_wrap(~ interaction(state, base_year, sep = " - "), ncol = 3)
```

### Difference in total CV
```{r echo = FALSE, fig.width=10}
ggplot(cvtrip_diff_state_combined, aes(x = factor(decade), y = diff_cv, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Difference total CV ($) (corr- ind)")+
  facet_wrap(~ interaction(state, base_year, sep = " - "), ncol = 3)
```

### Total directed trips
```{r echo = FALSE, fig.width=10}
ggplot(plot_data_state_combined, aes(x = factor(period), y = ntrips, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Number of directed trips")+
  facet_wrap(~ interaction(state, base_year, sep = " - "), ncol = 3)
```

### Difference in total directed trips
```{r echo = FALSE, fig.width=10}
ggplot(cvtrip_diff_state_combined, aes(x = factor(decade), y = diff_ntrips, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Difference in directed trips (dtrips_corr- dtrips_ind)")+
  facet_wrap(~ interaction(state, base_year, sep = " - "), ncol = 3)
```

## State-level  level decadal projections - catch outcomes at the trip level  {.tabset}

Catch data from 2025-04-17.

### cod catch per trip
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_state_combined, aes(x=period, y=codcattrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod catch per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ interaction(state, base_year, sep = " - "), ncol = 3)
```

### cod keep per trip
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_state_combined, aes(x=period, y=codkeeptrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod harvest per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ interaction(state, base_year, sep = " - "), ncol = 3)
```

### cod release per trip
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_state_combined, aes(x=period, y=codreltrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod release per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ interaction(state, base_year, sep = " - "), ncol = 3)
```

### haddock catch per trip
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_state_combined, aes(x=period, y=haddcattrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock catch per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ interaction(state, base_year, sep = " - "), ncol = 3)
```

### haddock keep per trip
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_state_combined, aes(x=period, y=haddkeeptrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock harvest per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ interaction(state, base_year, sep = " - "), ncol = 3)
```

### haddock release per trip 
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_state_combined, aes(x=period, y=haddreltrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock release per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ interaction(state, base_year, sep = " - "), ncol = 3)
```

### k-tau catch
```{r echo = FALSE, fig.width=10}
ggplot(k_tau_data_combined_state, aes(x=decade, y=k_tau_catch_est, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Decade", y = "Kendall's tau")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~ interaction(state, base_year, sep = " - "), ncol = 3)
```

### k-tau keep
```{r echo = FALSE, fig.width=10}
ggplot(k_tau_data_combined_state, aes(x=decade, y=k_tau_keep_est, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Decade", y = "Kendall's tau")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~ interaction(state, base_year, sep = " - "), ncol = 3)
```

## State-level decadal projections - catch outcomes at the choice occasion level  {.tabset}

Catch data from 2025-04-17.

### cod catch per choice occasion
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_state_combined, aes(x=period, y=codcatchoice, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod catch per choice occasion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ interaction(state, base_year, sep = " - "), ncol = 3)
```

### cod keep per choice occasion
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_state_combined, aes(x=period, y=codkeepchoice, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod harvest per choice occasion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ interaction(state, base_year, sep = " - "), ncol = 3)
```

### cod release per choice occasion
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_state_combined, aes(x=period, y=codrelchoice, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod release per choice occasion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ interaction(state, base_year, sep = " - "), ncol = 3)
```

### haddock catch per choice occasion
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_state_combined, aes(x=period, y=haddcatchoice, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock catch per choice occasion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ interaction(state, base_year, sep = " - "), ncol = 3)
```

### haddock keep per choice occasion
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_state_combined, aes(x=period, y=haddkeepchoice, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock harvest per choice occassion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ interaction(state, base_year, sep = " - "), ncol = 3)
```

### haddock release per choice occasion
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_state_combined, aes(x=period, y=haddrelchoice, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock release per choice occasion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ interaction(state, base_year, sep = " - "), ncol = 3)
```

## State-level decadal projections - aggregate catch outcomes  {.tabset}

### cod harvest 
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_state_combined, aes(x=period, y=codkeep, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod harvest")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ interaction(state, base_year, sep = " - "), ncol = 3)
```

### haddock harvest 
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_state_combined, aes(x=period, y=haddkeep, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock harvest")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ interaction(state, base_year, sep = " - "), ncol = 3)
```

### cod plus haddock harvest 
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_state_combined, aes(x=period, y=cod_hadd_keep, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod plus haddock harvest")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ interaction(state, base_year, sep = " - "), ncol = 3)
```

### cod catch 
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_state_combined, aes(x=period, y=codcat, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod catch")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ interaction(state, base_year, sep = " - "), ncol = 3)
```

### haddock catch 
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_state_combined, aes(x=period, y=haddcat, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock catch")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ interaction(state, base_year, sep = " - "), ncol = 3)
```

### cod plus haddock catch 
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1_state_combined, aes(x=period, y=cod_hadd_cat, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod plus haddock catch")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ interaction(state, base_year, sep = " - "), ncol = 3)
```

### Diff. total cod harvest
```{r echo = FALSE, fig.width=10}
ggplot(diff_state_combined, aes(x = factor(decade), y = diff_codkeep, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Difference in total cod harvest (corr- ind)")+
  facet_wrap(~ interaction(state, base_year, sep = " - "), ncol = 3)
```

### Diff. total cod catch
```{r echo = FALSE, fig.width=10}
ggplot(diff_state_combined, aes(x = factor(decade), y = diff_codcat, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Difference in total cod catch (corr- ind)")+
  facet_wrap(~ interaction(state, base_year, sep = " - "), ncol = 3)
```

### Diff. total haddock harvest
```{r echo = FALSE, fig.width=10}
ggplot(diff_state_combined, aes(x = factor(decade), y = diff_haddkeep, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Difference in total haddock harvest (corr- ind)")+
  facet_wrap(~ interaction(state, base_year, sep = " - "), ncol = 3)
```

### Diff. total haddock catch
```{r echo = FALSE, fig.width=10}
ggplot(diff_state_combined, aes(x = factor(decade), y = diff_haddcat, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Difference in total haddock catch (corr- ind)")+
  facet_wrap(~ interaction(state, base_year, sep = " - "), ncol = 3)
```

### Diff. total cod plus haddock harvest
```{r echo = FALSE, fig.width=10}
ggplot(diff_state_combined, aes(x = factor(decade), y = diff_cod_hadd_keep, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Difference in total cod plus haddock harvest (corr- ind)")+
  facet_wrap(~ interaction(state, base_year, sep = " - "), ncol = 3)
```

### Diff. total cod plus haddock catch
```{r echo = FALSE, fig.width=10}
ggplot(diff_state_combined, aes(x = factor(decade), y = diff_cod_hadd_cat, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Difference in total cod plus haddock catch (corr- ind)")+
  facet_wrap(~ interaction(state, base_year, sep = " - "), ncol = 3)
```
