---
title: "GoM cod and haddock RDM"
author: "Lou Carr-Harris"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: cerulean
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, comment = NA)

# Package setup
pkgs_to_use <- c("tidyverse", "data.table", "readxl", "haven", "stringr", "knitr",
                 "furrr", "profvis", "future", "copula", "VineCopula", "fitdistrplus",
                 "psych", "logspline", "univariateML", "ggpubr", "gridExtra", "hrbrthemes",
                 "writexl", "sjPlot", "tictoc", "Hmisc", "plyr", "dplyr", "conflicted")

install_if_missing <- setdiff(pkgs_to_use, rownames(installed.packages()))
if (length(install_if_missing) > 0) install.packages(install_if_missing)
lapply(pkgs_to_use, library, character.only = TRUE)
# Set preferred functions from conflicted packages
if ("conflicted" %in% rownames(installed.packages())) {
  library(conflicted)
  conflicts_prefer(dplyr::filter)
  conflicts_prefer(dplyr::select)
  conflicts_prefer(dplyr::mutate)
  conflicts_prefer(dplyr::rename)
  conflicts_prefer(dplyr::summarize)
  conflicts_prefer(dplyr::summarise)
  conflicts_prefer(dplyr::count)
}

output_data_cd <- "C:/Users/andrew.carr-harris/Desktop/Git/welfare-model-GoM/newest_version/output_data/"
input_data_cd <- "C:/Users/andrew.carr-harris/Desktop/Git/welfare-model-GoM/newest_version/input_data/"

options(scipen=999)
```

## Bottom temperatures {.tabset}
```{r bottom-temp-data, echo = FALSE, fig.width=8, fig.height=6}
historical_and_projections<- read_excel(paste0(output_data_cd,"bottom_temp_reformat1.xlsx"))  #save the data
historical_and_projections_annual<- read_excel(paste0(output_data_cd,"bottom_temp_reformat2.xlsx"))  #save the data
```

### By decade
```{r bottom-temp-plot, echo = FALSE, fig.height=6, fig.width=10}
ggplot(historical_and_projections, aes(month, mean_temp)) +
  geom_point() +
  geom_errorbar(aes(ymin = lower, ymax = upper)) +
  facet_wrap(~decade, nrow = 1) +
  theme(
    axis.text.x = element_blank(),
    strip.text = element_text(size = 7, margin = margin()),
    axis.ticks.x = element_blank()
  ) +
  geom_hline(aes(yintercept = mean_decadal_tmp), color = "red") +
  labs(x = NULL, y = "Sea bottom temperature (C)") +
  ggtitle("Historical and projected average monthly sea bottom temperatures in the Gulf of Maine by decade")
```

*Mean monthly bottom temps by decade/year, red line indicates the decadal average. Bars represent mean monthly temp +/- 1.96 x standard dev.*

### By year
```{r bottom-temp-plot2, echo = FALSE, fig.height=6, fig.width=10}
ggplot(historical_and_projections_annual, aes(month, mean_temp)) +
  geom_point() +
  geom_errorbar(aes(ymin = lower, ymax = upper)) +
  facet_wrap(~decade, nrow = 1) +
  theme(
    axis.text.x = element_blank(),
    strip.text = element_text(size = 7, margin = margin()),
    axis.ticks.x = element_blank()
  ) +
  geom_hline(aes(yintercept = mean_decadal_tmp), color = "red") +
  labs(x = NULL, y = "Sea bottom temperature (C)") +
  ggtitle("Historical and projected average monthly sea bottom temperatures in the Gulf of Maine by year/decade")
```

*Mean monthly bottom temps by decade/year, red line indicates the decadal average. Bars represent mean monthly temp +/- 1.96 x standard dev.*

<!--
## Model input projected catch-trip-data
```{r echo = FALSE}
final_result<- read_excel(paste0(output_data_cd,"model_input_proj_data.xlsx"))  #save the data

head(final_result)
```
-->

## Coastwide decadal projections - welfare {.tabset}

Each tab contains different projected fishery outcomes across copula models for the case of dependence, independence, and the difference between dependence and independence. Catch data from 2025-04-17. 
```{r echo = FALSE,  fig.width=10}
#By decade and copula - coast
output_summarized1<- read_rds(paste0(output_data_cd,"model_output_5-14-25_reformat_coast.rds"))  %>%
  mutate(copula = replace_na(copula, "baseline")) %>% 
  dplyr::mutate(codreltrip=codrel/ntrips,
                haddreltrip=haddrel/ntrips, 
                codrelchoice=codrel/n_choice_occasions,
                haddrelchoice=haddrel/n_choice_occasions)

output_summarized1$ntrips[is.na(output_summarized1$ntrips)] <- output_summarized1$dtrip[is.na(output_summarized1$ntrips)]

output_summarized_corr<-output_summarized1 %>% 
  dplyr::filter(correlation=="corr" | correlation=="baseline" | (is.na(correlation) & year==2021)) %>% 
  dplyr::select(-correlation)

output_summarized_ind<-output_summarized1 %>% 
  dplyr::filter(correlation=="ind" | correlation=="baseline" | (is.na(correlation) & year==2021)) %>% 
  dplyr::select(-correlation)

cvtrip_diff_corr <- output_summarized_corr %>%
  rename_with(~ paste0(.x, "_corr"), c(cvtrip)) %>%
    dplyr::select("draw", "copula","decade","cvtrip_corr") %>% 
    dplyr::filter(decade!=0 & !is.na(decade))

cvtrip_diff_ind <- output_summarized_ind %>%
  rename_with(~ paste0(.x, "_ind"), c(cvtrip)) %>%
    dplyr::select("draw", "copula","decade","cvtrip_ind") %>% 
    dplyr::filter(decade!=0 & !is.na(decade))

cvtrip_diff <- cvtrip_diff_corr %>% 
    left_join(cvtrip_diff_ind, by=c("draw", "copula","decade" )) %>%
     mutate(diff_cvtrip=cvtrip_corr- cvtrip_ind)

cvchoice_diff_corr <- output_summarized_corr %>%
  rename_with(~ paste0(.x, "_corr"), c(cv_choice)) %>%
    dplyr::select("draw", "copula","decade","cv_choice_corr") %>% 
    dplyr::filter(decade!=0 & !is.na(decade))

cvchoice_diff_ind <- output_summarized_ind %>%
  rename_with(~ paste0(.x, "_ind"), c(cv_choice)) %>%
    dplyr::select("draw", "copula","decade","cv_choice_ind") %>% 
    dplyr::filter(decade!=0 & !is.na(decade))

cvchoice_diff <- cvchoice_diff_corr %>% 
    left_join(cvchoice_diff_ind, by=c("draw", "copula","decade" )) %>%
     mutate(diff_cvchoice=cv_choice_corr- cv_choice_ind)

cvtotal_diff_corr <- output_summarized_corr %>%
  rename_with(~ paste0(.x, "_corr"), c(cv)) %>%
    dplyr::select("draw", "copula","decade","cv_corr") %>% 
    dplyr::filter(decade!=0 & !is.na(decade))

cvtotal_diff_ind <- output_summarized_ind %>%
  rename_with(~ paste0(.x, "_ind"), c(cv)) %>%
    dplyr::select("draw", "copula","decade","cv_ind") %>% 
    dplyr::filter(decade!=0 & !is.na(decade))

cvtotal_diff <- cvtotal_diff_corr %>% 
    left_join(cvtotal_diff_ind, by=c("draw", "copula","decade" )) %>%
     mutate(diff_total_cv=cv_corr- cv_ind)

ntrips_diff_corr <- output_summarized_corr %>%
  rename_with(~ paste0(.x, "_corr"), c(ntrips)) %>%
    dplyr::select("draw", "copula","decade","ntrips_corr") %>% 
    dplyr::filter(decade!=0 & !is.na(decade))

ntrips_diff_ind <- output_summarized_ind %>%
  rename_with(~ paste0(.x, "_ind"), c(ntrips)) %>%
    dplyr::select("draw", "copula","decade","ntrips_ind") %>% 
    dplyr::filter(decade!=0 & !is.na(decade))

ntrips_diff <- ntrips_diff_corr %>% 
    left_join(ntrips_diff_ind, by=c("draw", "copula","decade" )) %>%
     mutate(diff_ntrips=ntrips_corr- ntrips_ind)

output_summarized_corr_filtered <- output_summarized_corr %>% filter(decade != 0)
output_summarized_ind_filtered <- output_summarized_ind %>% filter(decade != 0)

# Find global y-axis limits for both datasets - CV per trip
y_min_cv <- min(c(output_summarized_corr_filtered$cvtrip, 
                  output_summarized_ind_filtered$cvtrip), na.rm = TRUE)
y_max_cv <- max(c(output_summarized_corr_filtered$cvtrip, 
                  output_summarized_ind_filtered$cvtrip), na.rm = TRUE)

# Find global y-axis limits for both datasets - CV per choice occasion
y_min_cv_choice <- min(c(output_summarized_corr_filtered$cv_choice,
                         output_summarized_ind_filtered$cv_choice), na.rm = TRUE)
y_max_cv_choice <- max(c(output_summarized_corr_filtered$cv_choice,
                         output_summarized_ind_filtered$cv_choice), na.rm = TRUE)

# Find global y-axis limits for both datasets - total CV
y_min_cv_total <- min(c(output_summarized_corr_filtered$cv,
                         output_summarized_ind_filtered$cv), na.rm = TRUE)
y_max_cv_total <- max(c(output_summarized_corr_filtered$cv,
                         output_summarized_ind_filtered$cv), na.rm = TRUE)

# Find global y-axis limits for both datasets - ntrips
y_min_ntrips <- min(c(output_summarized_corr$ntrips,
                         output_summarized_ind$ntrips), na.rm = TRUE)
y_max_ntrips <- max(c(output_summarized_corr$ntrips,
                         output_summarized_ind$ntrips), na.rm = TRUE)

# Find global y-axis limits for both datasets - hadd keep
y_min_hadd_keep <- min(c(output_summarized_corr$haddkeeptrip,
                         output_summarized_ind$haddkeeptrip), na.rm = TRUE)
y_max_hadd_keep <- max(c(output_summarized_corr$haddkeeptrip,
                         output_summarized_ind$haddkeeptrip), na.rm = TRUE)

y_min_hadd_keep_choice <- min(c(output_summarized_corr$haddkeepchoice,
                         output_summarized_ind$haddkeepchoice), na.rm = TRUE)
y_max_hadd_keep_choice <- max(c(output_summarized_corr$haddkeepchoice,
                         output_summarized_ind$haddkeepchoice), na.rm = TRUE)

# Find global y-axis limits for both datasets - hadd_release
y_min_hadd_release <- min(c(output_summarized_corr$haddreltrip,
                         output_summarized_ind$haddreltrip), na.rm = TRUE)
y_max_hadd_release <- max(c(output_summarized_corr$haddreltrip,
                         output_summarized_ind$haddreltrip), na.rm = TRUE)

y_min_hadd_release_choice <- min(c(output_summarized_corr$haddrelchoice,
                         output_summarized_ind$haddrelchoice), na.rm = TRUE)
y_max_hadd_release_choice <- max(c(output_summarized_corr$haddrelchoice,
                         output_summarized_ind$haddrelchoice), na.rm = TRUE)

# Find global y-axis limits for both datasets - cod keep
y_min_cod_keep <- min(c(output_summarized_corr$codkeeptrip,
                         output_summarized_ind$codkeeptrip), na.rm = TRUE)
y_max_cod_keep <- max(c(output_summarized_corr$codkeeptrip,
                         output_summarized_ind$codkeeptrip), na.rm = TRUE)

y_min_cod_keep_choice <- min(c(output_summarized_corr$codkeepchoice,
                         output_summarized_ind$codkeepchoice), na.rm = TRUE)
y_max_cod_keep_choice <- max(c(output_summarized_corr$codkeepchoice,
                         output_summarized_ind$codkeepchoice), na.rm = TRUE)


# Find global y-axis limits for both datasets - cod_release
y_min_cod_release <- min(c(output_summarized_corr$codreltrip,
                         output_summarized_ind$codreltrip), na.rm = TRUE)
y_max_cod_release <- max(c(output_summarized_corr$codreltrip,
                         output_summarized_ind$codreltrip), na.rm = TRUE)

y_min_cod_release_choice <- min(c(output_summarized_corr$codrelchoice,
                         output_summarized_ind_filtered$codrelchoice), na.rm = TRUE)
y_max_cod_release_choice <- max(c(output_summarized_corr_filtered$codrelchoice,
                         output_summarized_ind_filtered$codrelchoice), na.rm = TRUE)


y_min_cod_cat_choice <- min(c(output_summarized_corr_filtered$codcatchoice,
                         output_summarized_ind_filtered$codcatchoice), na.rm = TRUE)
y_max_cod_cat_choice <- max(c(output_summarized_corr_filtered$codcatchoice,
                         output_summarized_ind_filtered$codcatchoice), na.rm = TRUE)

y_min_hadd_cat_choice <- min(c(output_summarized_corr_filtered$haddcatchoice,
                         output_summarized_ind_filtered$haddcatchoice), na.rm = TRUE)
y_max_hadd_cat_choice <- max(c(output_summarized_corr_filtered$haddcatchoice,
                         output_summarized_ind_filtered$haddcatchoice), na.rm = TRUE)


#ktau data 
ktau_data<-read_excel(paste0(output_data_cd,"ktau_output_5-14-25.xlsx"))

ktau_annual<-ktau_data %>% filter(month==0) %>% 
  dplyr::select(-k_tau_catch_p, -k_tau_keep_p)

ktau_annual_long <- ktau_annual %>%
  mutate(parts = str_split(domain, "_", simplify = TRUE),
    correlation = parts[, 1],
    copula = str_extract(parts[, 2], "^[a-zA-Z]+"),
    decade = str_extract(parts[, 2], "[0-9]+")
  ) %>%
  select(draw, correlation, copula, decade, k_tau_keep_est, k_tau_catch_est)

ktau_data_base<-read_excel(paste0(output_data_cd,"ktau_baseline_year_output_6-2-25.xlsx"))



ktau_corr<-ktau_annual_long %>% dplyr::filter(correlation=="corr")
ktau_ind<-ktau_annual_long %>% dplyr::filter(correlation=="ind")

y_min_catch_corr <- min(c(ktau_corr$k_tau_catch_est, ktau_ind$k_tau_catch_est), na.rm = TRUE)
y_max_catch_corr <- max(c(ktau_corr$k_tau_catch_est, ktau_ind$k_tau_catch_est), na.rm = TRUE)

y_min_keep_corr <- min(c(ktau_corr$k_tau_keep_est, ktau_ind$k_tau_keep_est), na.rm = TRUE)
y_max_keep_corr <- max(c(ktau_corr$k_tau_keep_est, ktau_ind$k_tau_keep_est), na.rm = TRUE)
```

### CV per trip (correlated)
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized_corr_filtered, aes(x = factor(decade), y = cvtrip, color = factor(copula))) +
  geom_boxplot() +
  coord_cartesian(ylim = c(y_min_cv, y_max_cv)) +
  labs(x = "Decade", y = "Compensating variation per trip ($)")
```

### CV per trip (independent)
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized_ind_filtered, aes(x = factor(decade), y = cvtrip, color = factor(copula))) +
  geom_boxplot() +
  coord_cartesian(ylim = c(y_min_cv, y_max_cv))+
  labs(x = "Decade", y = "Compensating variation per trip ($)")
```

### Difference in CV per trip (corr. - ind.)
```{r echo = FALSE, fig.width=10}
ggplot(cvtrip_diff, aes(x = factor(decade), y = diff_cvtrip, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Difference in CV ($) per trip (CV_corr- CV_ind)")
```

### CV per choice occasion (correlated)
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized_corr_filtered, aes(x = factor(decade), y = cv_choice, color = factor(copula))) +
  geom_boxplot() +
  coord_cartesian(ylim = c(y_min_cv_choice, y_max_cv_choice)) +
  labs(x = "Decade", y = "Compensating variation per trip ($)")
```

### CV per choice occasion (independent)
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized_ind_filtered, aes(x = factor(decade), y = cv_choice, color = factor(copula))) +
  geom_boxplot() +
  coord_cartesian(ylim = c(y_min_cv_choice, y_max_cv_choice))+
  labs(x = "Decade", y = "Compensating variation per trip ($)")
```

### Difference in CV per choice occasion (corr. - ind.)
```{r echo = FALSE, fig.width=10}
ggplot(cvchoice_diff, aes(x = factor(decade), y = diff_cvchoice, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Difference in CV ($) per trip (CV_corr- CV_ind)")
```

### Total CV (independent)
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized_ind_filtered, aes(x = factor(decade), y = cv, color = factor(copula))) +
  geom_boxplot() +
  coord_cartesian(ylim = c(y_min_cv_total, y_max_cv_total))+
  labs(x = "Decade", y = "Compensating variation($)")
```

### Total CV (correlated)
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized_corr_filtered, aes(x = factor(decade), y = cv, color = factor(copula))) +
  geom_boxplot() +
  coord_cartesian(ylim = c(y_min_cv_total, y_max_cv_total))+
  labs(x = "Decade", y = "Compensating variation($)")
```

### Difference in total CV (corr. - ind.)
```{r echo = FALSE, fig.width=10}
ggplot(cvtotal_diff, aes(x = factor(decade), y = diff_total_cv, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Difference in total CV ($) (CV_corr- CV_ind)")
```

### Total directed trips (independent)
```{r echo = FALSE, fig.width=10}
plot_data <- output_summarized_ind %>%
  dplyr::select(-year, -tot_cat_cod, -tot_cat_hadd, -dtrip) %>% 
  filter(!(grepl("^\\d{4}$", period) & as.numeric(period) >= 2011 & as.numeric(period) <= 2020))

ggplot(plot_data, aes(x = factor(period), y = ntrips, color = factor(copula))) +
  geom_boxplot() +
  coord_cartesian(ylim = c(y_min_ntrips, y_max_ntrips))+
  labs(x = "Decade", y = "Number of directed trips")
```

### Total directed trips (correlated)
```{r echo = FALSE, fig.width=10}
plot_data <- output_summarized_corr %>%
  dplyr::select(-year, -tot_cat_cod, -tot_cat_hadd, -dtrip) %>% 
  filter(!(grepl("^\\d{4}$", period) & as.numeric(period) >= 2011 & as.numeric(period) <= 2020))

ggplot(plot_data, aes(x = factor(period), y = ntrips, color = factor(copula))) +
  geom_boxplot() +
  coord_cartesian(ylim = c(y_min_ntrips, y_max_ntrips))+
  labs(x = "Decade", y = "Number of directed trips")
```

### Difference in total directed trips (corr. - ind.)
```{r echo = FALSE, fig.width=10}
ggplot(ntrips_diff, aes(x = factor(decade), y = diff_ntrips, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Difference in directed trips (dtrips_corr- dtrips_ind)")
```

## Coastwide decadal projections - catch outcomes at the trip level {.tabset}

Catch data from 2025-04-17.

### cod catch per trip (correlated)
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized_corr, aes(x=period, y=codcattrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod catch per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### cod catch per trip (independent)
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized_ind, aes(x=period, y=codcattrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod catch per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### cod keep per trip (correlated)
```{r echo = FALSE, fig.width=10}
# Filter out periods that are numeric years between 2011 and 2020
plot_data <- output_summarized_corr %>%
  dplyr::select(-year, -tot_cat_cod, -tot_cat_hadd, -dtrip) %>% 
  filter(!(grepl("^\\d{4}$", period) & as.numeric(period) >= 2011 & as.numeric(period) <= 2020))


ggplot(plot_data, aes(x=period, y=codkeeptrip, color = factor(copula)))+
  geom_boxplot() +
  coord_cartesian(ylim = c(y_min_cod_keep, y_max_cod_keep))+
  labs(x = "Period", y = "Cod harvest per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### cod keep per trip (independent)
```{r echo = FALSE, fig.width=10}
plot_data <- output_summarized_ind %>%
   dplyr::select(-year, -tot_cat_cod, -tot_cat_hadd, -dtrip) %>% 
   dplyr::filter(!(grepl("^\\d{4}$", period) & as.numeric(period) >= 2011 & as.numeric(period) <= 2020))

ggplot(plot_data, aes(x=period, y=codkeeptrip, color = factor(copula)))+
  geom_boxplot() +
  coord_cartesian(ylim = c(y_min_cod_keep, y_max_cod_keep))+
  labs(x = "Period", y = "Cod harvest per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### cod release per trip (correlated)
```{r echo = FALSE, fig.width=10}
# Filter out periods that are numeric years between 2011 and 2020
plot_data <- output_summarized_corr %>%
  dplyr::select(-year, -tot_cat_cod, -tot_cat_hadd, -dtrip) %>% 
  filter(!(grepl("^\\d{4}$", period) & as.numeric(period) >= 2011 & as.numeric(period) <= 2020))


ggplot(plot_data, aes(x=period, y=codreltrip, color = factor(copula)))+
  geom_boxplot() +
  coord_cartesian(ylim = c(y_min_cod_release, y_max_cod_release))+
  labs(x = "Period", y = "Cod release per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### cod release per trip (independent)
```{r echo = FALSE, fig.width=10}
plot_data <- output_summarized_ind %>%
   dplyr::select(-year, -tot_cat_cod, -tot_cat_hadd, -dtrip) %>% 
   dplyr::filter(!(grepl("^\\d{4}$", period) & as.numeric(period) >= 2011 & as.numeric(period) <= 2020))

ggplot(plot_data, aes(x=period, y=codreltrip, color = factor(copula)))+
  geom_boxplot() +
  coord_cartesian(ylim = c(y_min_cod_release, y_max_cod_release))+
  labs(x = "Period", y = "Cod release per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### haddock catch per trip (correlated)
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized_corr, aes(x=period, y=haddcattrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock catch per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### haddock catch per trip (independent)
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized_ind, aes(x=period, y=haddcattrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock catch per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### haddock keep per trip (correlated)
```{r echo = FALSE, fig.width=10}
plot_data <- output_summarized_corr %>%
  dplyr::select(-year, -tot_cat_cod, -tot_cat_hadd, -dtrip) %>% 
  dplyr::filter(!(grepl("^\\d{4}$", period) & as.numeric(period) >= 2011 & as.numeric(period) <= 2020))

ggplot(plot_data, aes(x=period, y=haddkeeptrip, color = factor(copula)))+
  geom_boxplot() +
  coord_cartesian(ylim = c(y_min_hadd_keep, y_max_hadd_keep))+
  labs(x = "Period", y = "Haddock harvest per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### haddock keep per trip (independent)
```{r echo = FALSE, fig.width=10}
plot_data <- output_summarized_ind %>%
  dplyr::select(-year, -tot_cat_cod, -tot_cat_hadd, -dtrip) %>% 
  filter(!(grepl("^\\d{4}$", period) & as.numeric(period) >= 2011 & as.numeric(period) <= 2020))

ggplot(plot_data, aes(x=period, y=haddkeeptrip, color = factor(copula)))+
  geom_boxplot() +
  coord_cartesian(ylim = c(y_min_hadd_keep, y_max_hadd_keep))+
  labs(x = "Period", y = "Haddock harvest per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### haddock release per trip (correlated)
```{r echo = FALSE, fig.width=10}
plot_data <- output_summarized_corr %>%
  dplyr::select(-year, -tot_cat_cod, -tot_cat_hadd, -dtrip) %>% 
  dplyr::filter(!(grepl("^\\d{4}$", period) & as.numeric(period) >= 2011 & as.numeric(period) <= 2020))

ggplot(plot_data, aes(x=period, y=haddreltrip, color = factor(copula)))+
  geom_boxplot() +
  coord_cartesian(ylim = c(y_min_hadd_release, y_max_hadd_release))+
  labs(x = "Period", y = "Haddock release per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### haddock release per trip (independent)
```{r echo = FALSE, fig.width=10}
plot_data <- output_summarized_ind %>%
  dplyr::select(-year, -tot_cat_cod, -tot_cat_hadd, -dtrip) %>% 
  filter(!(grepl("^\\d{4}$", period) & as.numeric(period) >= 2011 & as.numeric(period) <= 2020))

ggplot(plot_data, aes(x=period, y=haddreltrip, color = factor(copula)))+
  geom_boxplot() +
  coord_cartesian(ylim = c(y_min_hadd_release, y_max_hadd_release))+
  labs(x = "Period", y = "Haddock release per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### k-tau catch (correlated)
```{r echo = FALSE, fig.width=10}
ggplot(ktau_corr, aes(x=decade, y=k_tau_catch_est, color = factor(copula)))+
  geom_boxplot() +
  coord_cartesian(ylim = c(y_min_catch_corr, y_max_catch_corr))+
  labs(x = "Decade", y = "Kendall's tau")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### k-tau catch (independent)
```{r echo = FALSE, fig.width=10}
ggplot(ktau_ind, aes(x=decade, y=k_tau_catch_est, color = factor(copula)))+
  geom_boxplot() +
  coord_cartesian(ylim = c(y_min_catch_corr, y_max_catch_corr))+
  labs(x = "Decade", y = "Kendall's tau")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### k-tau keep (correlated)
```{r echo = FALSE, fig.width=10}
ggplot(ktau_corr, aes(x=decade, y=k_tau_keep_est, color = factor(copula)))+
  geom_boxplot() +
  coord_cartesian(ylim = c(y_min_keep_corr, y_max_keep_corr))+
  labs(x = "Decade", y = "Kendall's tau")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### k-tau keep (independent)
```{r echo = FALSE, fig.width=10}
ggplot(ktau_ind, aes(x=decade, y=k_tau_keep_est, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Decade", y = "Kendall's tau")+
  coord_cartesian(ylim = c(y_min_keep_corr, y_max_keep_corr))+
  theme(axis.text.x = element_text(angle = 45))
```

## Coastwide decadal projections - catch outcomes at the choice occasion level {.tabset}

Catch data from 2025-04-17.

### cod catch per choice occasion (correlated)
```{r echo = FALSE, fig.width=10}
plot_data <- output_summarized_corr %>%
  dplyr::select(-year, -tot_cat_cod, -tot_cat_hadd, -dtrip) %>% 
  dplyr::filter(!(grepl("^\\d{4}$", period) & as.numeric(period) >= 2011 & as.numeric(period) <= 2020))

ggplot(plot_data, aes(x=period, y=codcatchoice, color = factor(copula)))+
  geom_boxplot() +
  coord_cartesian(ylim = c(y_min_cod_cat_choice, y_max_cod_cat_choice))+
  labs(x = "Period", y = "Cod catch per choice occasion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### cod catch per choice occasion (independent)
```{r echo = FALSE, fig.width=10}
plot_data <- output_summarized_ind %>%
  dplyr::select(-year, -tot_cat_cod, -tot_cat_hadd, -dtrip) %>% 
  dplyr::filter(!(grepl("^\\d{4}$", period) & as.numeric(period) >= 2011 & as.numeric(period) <= 2020))

ggplot(plot_data, aes(x=period, y=codcatchoice, color = factor(copula)))+
  geom_boxplot() +
  coord_cartesian(ylim = c(y_min_cod_cat_choice, y_max_cod_cat_choice))+
  labs(x = "Period", y = "Cod catch per choice occasion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### cod keep per choice occasion (correlated)
```{r echo = FALSE, fig.width=10}
# Filter out periods that are numeric years between 2011 and 2020
plot_data <- output_summarized_corr %>%
  dplyr::select(-year, -tot_cat_cod, -tot_cat_hadd, -dtrip) %>% 
  filter(!(grepl("^\\d{4}$", period) & as.numeric(period) >= 2011 & as.numeric(period) <= 2020))


ggplot(plot_data, aes(x=period, y=codkeepchoice, color = factor(copula)))+
  geom_boxplot() +
  coord_cartesian(ylim = c(y_min_cod_keep_choice, y_max_cod_keep_choice))+
  labs(x = "Period", y = "Cod harvest per choice occasion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### cod keep per choice occasion (independent)
```{r echo = FALSE, fig.width=10}
plot_data <- output_summarized_ind %>%
   dplyr::select(-year, -tot_cat_cod, -tot_cat_hadd, -dtrip) %>% 
   dplyr::filter(!(grepl("^\\d{4}$", period) & as.numeric(period) >= 2011 & as.numeric(period) <= 2020))

ggplot(plot_data, aes(x=period, y=codkeepchoice, color = factor(copula)))+
  geom_boxplot() +
  coord_cartesian(ylim = c(y_min_cod_keep_choice, y_max_cod_keep_choice))+
  labs(x = "Period", y = "Cod harvest per choice occasion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### cod release per choice occasion (correlated)
```{r echo = FALSE, fig.width=10}
# Filter out periods that are numeric years between 2011 and 2020
plot_data <- output_summarized_corr %>%
  dplyr::select(-year, -tot_cat_cod, -tot_cat_hadd, -dtrip) %>% 
  filter(!(grepl("^\\d{4}$", period) & as.numeric(period) >= 2011 & as.numeric(period) <= 2020))


ggplot(plot_data, aes(x=period, y=codrelchoice, color = factor(copula)))+
  geom_boxplot() +
  coord_cartesian(ylim = c(y_min_cod_release_choice, y_max_cod_release_choice))+
  labs(x = "Period", y = "Cod release per choice occasion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### cod release per choice occasion (independent)
```{r echo = FALSE, fig.width=10}
plot_data <- output_summarized_ind %>%
   dplyr::select(-year, -tot_cat_cod, -tot_cat_hadd, -dtrip) %>% 
   dplyr::filter(!(grepl("^\\d{4}$", period) & as.numeric(period) >= 2011 & as.numeric(period) <= 2020))

ggplot(plot_data, aes(x=period, y=codrelchoice, color = factor(copula)))+
  geom_boxplot() +
  coord_cartesian(ylim = c(y_min_cod_release_choice, y_max_cod_release_choice))+
  labs(x = "Period", y = "Cod release per choice occasion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### haddock catch per choice occasion (correlated)
```{r echo = FALSE, fig.width=10}
plot_data <- output_summarized_corr %>%
   dplyr::select(-year, -tot_cat_cod, -tot_cat_hadd, -dtrip) %>% 
   dplyr::filter(!(grepl("^\\d{4}$", period) & as.numeric(period) >= 2011 & as.numeric(period) <= 2020))

ggplot(plot_data, aes(x=period, y=haddcatchoice, color = factor(copula)))+
  geom_boxplot() +
  coord_cartesian(ylim = c(y_min_hadd_cat_choice, y_max_hadd_cat_choice))+
  labs(x = "Period", y = "Haddock catch per choice occasion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### haddock catch per choice occasion (independent)
```{r echo = FALSE, fig.width=10}
plot_data <- output_summarized_ind %>%
   dplyr::select(-year, -tot_cat_cod, -tot_cat_hadd, -dtrip) %>% 
   dplyr::filter(!(grepl("^\\d{4}$", period) & as.numeric(period) >= 2011 & as.numeric(period) <= 2020))

ggplot(plot_data, aes(x=period, y=haddcatchoice, color = factor(copula)))+
  geom_boxplot() +
  coord_cartesian(ylim = c(y_min_hadd_cat_choice, y_max_hadd_cat_choice))+
  labs(x = "Period", y = "Haddock catch per choice occasion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### haddock keep per choice occasion (correlated)
```{r echo = FALSE, fig.width=10}
plot_data <- output_summarized_corr %>%
  dplyr::select(-year, -tot_cat_cod, -tot_cat_hadd, -dtrip) %>% 
  dplyr::filter(!(grepl("^\\d{4}$", period) & as.numeric(period) >= 2011 & as.numeric(period) <= 2020))

ggplot(plot_data, aes(x=period, y=haddkeepchoice, color = factor(copula)))+
  geom_boxplot() +
  coord_cartesian(ylim = c(y_min_hadd_keep_choice, y_max_hadd_keep_choice))+
  labs(x = "Period", y = "Haddock harvest per choice occassion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### haddock keep per choice occasion (independent)
```{r echo = FALSE, fig.width=10}
plot_data <- output_summarized_ind %>%
  dplyr::select(-year, -tot_cat_cod, -tot_cat_hadd, -dtrip) %>% 
  filter(!(grepl("^\\d{4}$", period) & as.numeric(period) >= 2011 & as.numeric(period) <= 2020))

ggplot(plot_data, aes(x=period, y=haddkeepchoice, color = factor(copula)))+
  geom_boxplot() +
  coord_cartesian(ylim = c(y_min_hadd_keep_choice, y_max_hadd_keep_choice))+
  labs(x = "Period", y = "Haddock harvest per choice occasion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### haddock release per choice occasion (correlated)
```{r echo = FALSE, fig.width=10}
plot_data <- output_summarized_corr %>%
  dplyr::select(-year, -tot_cat_cod, -tot_cat_hadd, -dtrip) %>% 
  dplyr::filter(!(grepl("^\\d{4}$", period) & as.numeric(period) >= 2011 & as.numeric(period) <= 2020))

ggplot(plot_data, aes(x=period, y=haddrelchoice, color = factor(copula)))+
  geom_boxplot() +
  coord_cartesian(ylim = c(y_min_hadd_release_choice, y_max_hadd_release_choice))+
  labs(x = "Period", y = "Haddock release per choice occasion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### haddock release per choice occasion (independent)
```{r echo = FALSE, fig.width=10}
plot_data <- output_summarized_ind %>%
  dplyr::select(-year, -tot_cat_cod, -tot_cat_hadd, -dtrip) %>% 
  filter(!(grepl("^\\d{4}$", period) & as.numeric(period) >= 2011 & as.numeric(period) <= 2020))

ggplot(plot_data, aes(x=period, y=haddrelchoice, color = factor(copula)))+
  geom_boxplot() +
  coord_cartesian(ylim = c(y_min_hadd_release_choice, y_max_hadd_release_choice))+
  labs(x = "Period", y = "Haddock release per choice occasion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## Fishing mode-level decadal projections - welfare {.tabset}

Each tab contains different projected fishery outcomes across copula models for the case of dependence, independence, and the difference between dependence and independence. Catch data from 2025-04-17. 

```{r echo = FALSE,  fig.width=10}
output_summarized1<- read_rds(paste0(output_data_cd,"model_output_5-14-25_reformat_mode.rds"))  %>%
  mutate(copula = replace_na(copula, "baseline")) 

output_summarized_corr<-output_summarized1 %>% 
  dplyr::filter(correlation=="corr" | correlation=="baseline" | (is.na(correlation) & year==2021)) %>% 
  dplyr::select(-correlation)

output_summarized_ind<-output_summarized1 %>% 
  dplyr::filter(correlation=="ind" | correlation=="baseline" | (is.na(correlation) & year==2021)) %>% 
  dplyr::select(-correlation)

cvtrip_diff_corr <- output_summarized_corr %>%
  rename_with(~ paste0(.x, "_corr"), c(cvtrip)) %>%
    dplyr::select("draw", "copula","decade","cvtrip_corr", "mode") %>% 
    dplyr::filter(decade!=0 & !is.na(decade))

cvtrip_diff_ind <- output_summarized_ind %>%
  rename_with(~ paste0(.x, "_ind"), c(cvtrip)) %>%
    dplyr::select("draw", "copula","decade","cvtrip_ind", "mode") %>% 
    dplyr::filter(decade!=0 & !is.na(decade))

cvtrip_diff <- cvtrip_diff_corr %>% 
    left_join(cvtrip_diff_ind, by=c("draw", "copula","decade", "mode" )) %>%
     mutate(diff_cvtrip=cvtrip_corr- cvtrip_ind)

cvchoice_diff_corr <- output_summarized_corr %>%
  rename_with(~ paste0(.x, "_corr"), c(cv_choice)) %>%
    dplyr::select("draw", "copula","decade","cv_choice_corr", "mode") %>% 
    dplyr::filter(decade!=0 & !is.na(decade))

cvchoice_diff_ind <- output_summarized_ind %>%
  rename_with(~ paste0(.x, "_ind"), c(cv_choice)) %>%
    dplyr::select("draw", "copula","decade","cv_choice_ind", "mode") %>% 
    dplyr::filter(decade!=0 & !is.na(decade))

cvchoice_diff <- cvchoice_diff_corr %>% 
    left_join(cvchoice_diff_ind, by=c("draw", "copula","decade" , "mode")) %>%
     mutate(diff_cvchoice=cv_choice_corr- cv_choice_ind)

output_summarized_corr_filtered <- output_summarized_corr %>% filter(decade != 0)
output_summarized_ind_filtered <- output_summarized_ind %>% filter(decade != 0)

# Find global y-axis limits for both datasets
y_min_cv <- min(c(output_summarized_corr_filtered$cvtrip, output_summarized_ind_filtered$cvtrip), na.rm = TRUE)
y_max_cv <- max(c(output_summarized_corr_filtered$cvtrip, output_summarized_ind_filtered$cvtrip), na.rm = TRUE)

# Find global y-axis limits for both datasets
y_min_cv_choice <- min(c(output_summarized_corr_filtered$cv_choice, output_summarized_ind_filtered$cv_choice), na.rm = TRUE)
y_max_cv_choice <- max(c(output_summarized_corr_filtered$cv_choice, output_summarized_ind_filtered$cv_choice), na.rm = TRUE)
```

### CV per trip (correlated)
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized_corr_filtered, aes(x = factor(decade), y = cvtrip, color = factor(copula))) +
  geom_boxplot() +
  coord_cartesian(ylim = c(y_min_cv, y_max_cv)) +
  labs(x = "Decade", y = "Compensating variation per trip ($)") +
  facet_wrap(~ mode)
```

### CV per trip (independent)
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized_ind_filtered, aes(x = factor(decade), y = cvtrip, color = factor(copula))) +
  geom_boxplot() +
  coord_cartesian(ylim = c(y_min_cv, y_max_cv))+
  labs(x = "Decade", y = "Compensating variation per trip ($)") +
  facet_wrap(~ mode)
```

### Difference in CV per trip (corr. - ind.)
```{r echo = FALSE, fig.width=10}
ggplot(cvtrip_diff, aes(x = factor(decade), y = diff_cvtrip, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Difference in CV ($) per trip (CV_corr- CV_ind)") +
  facet_wrap(~ mode)
```

### CV per choice occasion (correlated)
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized_corr_filtered, aes(x = factor(decade), y = cv_choice, color = factor(copula))) +
  geom_boxplot() +
  coord_cartesian(ylim = c(y_min_cv_choice, y_max_cv_choice)) +
  labs(x = "Decade", y = "Compensating variation per trip ($)") +
  facet_wrap(~ mode)
```

### CV per choice occasion (independent)
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized_ind_filtered, aes(x = factor(decade), y = cv_choice, color = factor(copula))) +
  geom_boxplot() +
  coord_cartesian(ylim = c(y_min_cv_choice, y_max_cv_choice))+
  labs(x = "Decade", y = "Compensating variation per trip ($)") +
  facet_wrap(~ mode)
```

### Difference in CV per choice occasion (corr. - ind.)
```{r echo = FALSE, fig.width=10}
ggplot(cvchoice_diff, aes(x = factor(decade), y = diff_cvchoice, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Difference in CV ($) per trip (CV_corr- CV_ind)") +
  facet_wrap(~ mode)
```

## Fishing mode-level decadal projections - catch {.tabset}

Catch data from 2025-04-17. 

### cod catch per trip (correlated)
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized_corr, aes(x=period, y=codcattrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod catch per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~ mode)
```

### cod catch per trip (independent)
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized_ind, aes(x=period, y=codcattrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod catch per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~ mode)
```

### cod keep per trip (correlated)
```{r echo = FALSE, fig.width=10}
# Filter out periods that are numeric years between 2011 and 2020
plot_data <- output_summarized_corr %>%
  dplyr::select(-year, -tot_cat_cod, -tot_cat_hadd, -dtrip) %>% 
  filter(!(grepl("^\\d{4}$", period) & as.numeric(period) >= 2011 & as.numeric(period) <= 2020))


ggplot(plot_data, aes(x=period, y=codkeeptrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod harvest per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~ mode)
```

### cod keep per trip (independent)
```{r echo = FALSE, fig.width=10}
plot_data <- output_summarized_ind %>%
   dplyr::select(-year, -tot_cat_cod, -tot_cat_hadd, -dtrip) %>% 
   dplyr::filter(!(grepl("^\\d{4}$", period) & as.numeric(period) >= 2011 & as.numeric(period) <= 2020))

ggplot(plot_data, aes(x=period, y=codkeeptrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod harvest per trip")+ 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~ mode)
```

### haddock catch per trip (correlated)
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized_corr, aes(x=period, y=haddcattrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock catch per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~ mode)
```

### haddock catch per trip (independent)
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized_ind, aes(x=period, y=haddcattrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock catch per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~ mode)
```

### haddock keep per trip (correlated)
```{r echo = FALSE, fig.width=10}
plot_data <- output_summarized_corr %>%
  dplyr::select(-year, -tot_cat_cod, -tot_cat_hadd, -dtrip) %>% 
  dplyr::filter(!(grepl("^\\d{4}$", period) & as.numeric(period) >= 2011 & as.numeric(period) <= 2020))

ggplot(plot_data, aes(x=period, y=haddkeeptrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock harvest per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~ mode)
```

### haddock keep per trip (independent)
```{r echo = FALSE, fig.width=10}
plot_data <- output_summarized_ind %>%
  dplyr::select(-year, -tot_cat_cod, -tot_cat_hadd, -dtrip) %>% 
  filter(!(grepl("^\\d{4}$", period) & as.numeric(period) >= 2011 & as.numeric(period) <= 2020))

ggplot(plot_data, aes(x=period, y=haddkeeptrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock harvest per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~ mode)
```

## State-level decadal projections - welfare {.tabset}

Each tab contains different projected fishery outcomes across copula models for the case of dependence, independence, and the difference between dependence and independence. Catch data from 2025-04-17. 

```{r echo = FALSE,  fig.width=10}
output_summarized1<- read_rds(paste0(output_data_cd,"model_output_5-14-25_reformat_state.rds")) %>%
  mutate(copula = replace_na(copula, "baseline")) 

output_summarized_corr<-output_summarized1 %>% 
  dplyr::filter(correlation=="corr" | correlation=="baseline" | (is.na(correlation) & year==2021)) %>% 
  dplyr::select(-correlation) 

output_summarized_ind<-output_summarized1 %>% 
  dplyr::filter(correlation=="ind" | correlation=="baseline" | (is.na(correlation) & year==2021)) %>% 
  dplyr::select(-correlation)

cvtrip_diff_corr <- output_summarized_corr %>%
  rename_with(~ paste0(.x, "_corr"), c(cvtrip)) %>%
    dplyr::select("draw", "copula","decade","cvtrip_corr", "state") %>% 
    dplyr::filter(decade!=0 & !is.na(decade))

cvtrip_diff_ind <- output_summarized_ind %>%
  rename_with(~ paste0(.x, "_ind"), c(cvtrip)) %>%
    dplyr::select("draw", "copula","decade","cvtrip_ind", "state") %>% 
    dplyr::filter(decade!=0 & !is.na(decade))

cvtrip_diff <- cvtrip_diff_corr %>% 
    left_join(cvtrip_diff_ind, by=c("draw", "copula","decade", "state" )) %>%
     mutate(diff_cvtrip=cvtrip_corr- cvtrip_ind)

cvchoice_diff_corr <- output_summarized_corr %>%
  rename_with(~ paste0(.x, "_corr"), c(cv_choice)) %>%
    dplyr::select("draw", "copula","decade","cv_choice_corr", "state") %>% 
    dplyr::filter(decade!=0 & !is.na(decade))

cvchoice_diff_ind <- output_summarized_ind %>%
  rename_with(~ paste0(.x, "_ind"), c(cv_choice)) %>%
    dplyr::select("draw", "copula","decade","cv_choice_ind", "state") %>% 
    dplyr::filter(decade!=0 & !is.na(decade))

cvchoice_diff <- cvchoice_diff_corr %>% 
    left_join(cvchoice_diff_ind, by=c("draw", "copula","decade" , "state")) %>%
     mutate(diff_cvchoice=cv_choice_corr- cv_choice_ind)

output_summarized_corr_filtered <- output_summarized_corr %>% filter(decade != 0)
output_summarized_ind_filtered <- output_summarized_ind %>% filter(decade != 0)

# Find global y-axis limits for both datasets
y_min_cv <- min(c(output_summarized_corr_filtered$cvtrip, output_summarized_ind_filtered$cvtrip), na.rm = TRUE)
y_max_cv <- max(c(output_summarized_corr_filtered$cvtrip, output_summarized_ind_filtered$cvtrip), na.rm = TRUE)

# Find global y-axis limits for both datasets
y_min_cv_choice <- min(c(output_summarized_corr_filtered$cv_choice, output_summarized_ind_filtered$cv_choice), na.rm = TRUE)
y_max_cv_choice <- max(c(output_summarized_corr_filtered$cv_choice, output_summarized_ind_filtered$cv_choice), na.rm = TRUE)
```

### CV per trip (correlated)
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized_corr_filtered, aes(x = factor(decade), y = cvtrip, color = factor(copula))) +
  geom_boxplot() +
  coord_cartesian(ylim = c(y_min_cv, y_max_cv)) +
  labs(x = "Decade", y = "Compensating variation per trip ($)") +
  facet_wrap(~ state)
```

### CV per trip (independent)
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized_ind_filtered, aes(x = factor(decade), y = cvtrip, color = factor(copula))) +
  geom_boxplot() +
  coord_cartesian(ylim = c(y_min_cv, y_max_cv))+
  labs(x = "Decade", y = "Compensating variation per trip ($)") +
  facet_wrap(~ state)
```

### Difference in CV per trip (corr. - ind.)
```{r echo = FALSE, fig.width=10}
ggplot(cvtrip_diff, aes(x = factor(decade), y = diff_cvtrip, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Difference in CV ($) per trip (CV_corr- CV_ind)") +
  facet_wrap(~ state)
```

### CV per choice occasion (correlated)
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized_corr_filtered, aes(x = factor(decade), y = cv_choice, color = factor(copula))) +
  geom_boxplot() +
  coord_cartesian(ylim = c(y_min_cv_choice, y_max_cv_choice)) +
  labs(x = "Decade", y = "Compensating variation per trip ($)") +
  facet_wrap(~ state)
```

### CV per choice occasion (independent)
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized_ind_filtered, aes(x = factor(decade), y = cv_choice, color = factor(copula))) +
  geom_boxplot() +
  coord_cartesian(ylim = c(y_min_cv_choice, y_max_cv_choice))+
  labs(x = "Decade", y = "Compensating variation per trip ($)") +
  facet_wrap(~ state)
```

### Difference in CV per choice occasion (corr. - ind.)
```{r echo = FALSE, fig.width=10}
ggplot(cvchoice_diff, aes(x = factor(decade), y = diff_cvchoice, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Difference in CV ($) per trip (CV_corr- CV_ind)") +
  facet_wrap(~ state)
```

## State-level decadal projections - catch {.tabset}

Catch data from 2025-04-17. 

### cod catch per trip (correlated)
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized_corr, aes(x=period, y=codcattrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod catch per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~ state)
```

### cod catch per trip (independent)
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized_ind, aes(x=period, y=codcattrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod catch per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~ state)
```

### cod keep per trip (correlated)
```{r echo = FALSE, fig.width=10}
# Filter out periods that are numeric years between 2011 and 2020
plot_data <- output_summarized_corr %>%
  dplyr::select(-year, -tot_cat_cod, -tot_cat_hadd, -dtrip) %>% 
  filter(!(grepl("^\\d{4}$", period) & as.numeric(period) >= 2011 & as.numeric(period) <= 2020))


ggplot(plot_data, aes(x=period, y=codkeeptrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod harvest per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~ state)
```

### cod keep per trip (independent)
```{r echo = FALSE, fig.width=10}
plot_data <- output_summarized_ind %>%
   dplyr::select(-year, -tot_cat_cod, -tot_cat_hadd, -dtrip) %>% 
   dplyr::filter(!(grepl("^\\d{4}$", period) & as.numeric(period) >= 2011 & as.numeric(period) <= 2020))

ggplot(plot_data, aes(x=period, y=codkeeptrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod harvest per trip")+ 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~ state)
```

### haddock catch per trip (correlated)
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized_corr, aes(x=period, y=haddcattrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock catch per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~ state)
```

### haddock catch per trip (independent)
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized_ind, aes(x=period, y=haddcattrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock catch per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~ state)
```

### haddock keep per trip (correlated)
```{r echo = FALSE, fig.width=10}
plot_data <- output_summarized_corr %>%
  dplyr::select(-year, -tot_cat_cod, -tot_cat_hadd, -dtrip) %>% 
  dplyr::filter(!(grepl("^\\d{4}$", period) & as.numeric(period) >= 2011 & as.numeric(period) <= 2020))

ggplot(plot_data, aes(x=period, y=haddkeeptrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock harvest per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~ state)
```

### haddock keep per trip (independent)
```{r echo = FALSE, fig.width=10}
plot_data <- output_summarized_ind %>%
  dplyr::select(-year, -tot_cat_cod, -tot_cat_hadd, -dtrip) %>% 
  filter(!(grepl("^\\d{4}$", period) & as.numeric(period) >= 2011 & as.numeric(period) <= 2020))

ggplot(plot_data, aes(x=period, y=haddkeeptrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock harvest per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~ state)
```


