---
title: "GoM cod and haddock RDM"
author: "Lou Carr-Harris"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: cerulean
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, comment = NA)

# Package setup
pkgs_to_use <- c("tidyverse", "data.table", "readxl", "haven", "stringr", "knitr",
                 "furrr", "profvis", "future", "copula", "VineCopula", "fitdistrplus",
                 "psych", "logspline", "univariateML", "ggpubr", "gridExtra", "hrbrthemes",
                 "writexl", "sjPlot", "tictoc", "Hmisc", "plyr", "dplyr", "conflicted")

install_if_missing <- setdiff(pkgs_to_use, rownames(installed.packages()))
if (length(install_if_missing) > 0) install.packages(install_if_missing)
lapply(pkgs_to_use, library, character.only = TRUE)
# Set preferred functions from conflicted packages
if ("conflicted" %in% rownames(installed.packages())) {
  library(conflicted)
  conflicts_prefer(dplyr::filter)
  conflicts_prefer(dplyr::select)
  conflicts_prefer(dplyr::mutate)
  conflicts_prefer(dplyr::rename)
  conflicts_prefer(dplyr::summarize)
  conflicts_prefer(dplyr::summarise)
  conflicts_prefer(dplyr::count)
}

output_data_cd <- "C:/Users/andrew.carr-harris/Desktop/Git/welfare-model-GoM/newest_version/output_data/"
input_data_cd <- "C:/Users/andrew.carr-harris/Desktop/Git/welfare-model-GoM/newest_version/input_data/"

options(scipen=999)
```

## Bottom temperatures {.tabset}
```{r bottom-temp-data, echo = FALSE, fig.width=8, fig.height=6}
historical_and_projections<- read_excel(paste0(output_data_cd,"bottom_temp_reformat1.xlsx"))  #save the data
historical_and_projections_annual<- read_excel(paste0(output_data_cd,"bottom_temp_reformat2.xlsx"))  #save the data
```

### Historical by decade and projected 
```{r bottom-temp-plot1, echo = FALSE, fig.height=6, fig.width=10}
ggplot(historical_and_projections, aes(month, mean_temp)) +
  geom_point() +
  geom_errorbar(aes(ymin = lower, ymax = upper)) +
  facet_wrap(~decade, nrow = 1) +
  theme(
    axis.text.x = element_blank(),
    strip.text = element_text(size = 7, margin = margin()),
    axis.ticks.x = element_blank()
  ) +
  geom_hline(aes(yintercept = mean_decadal_tmp), color = "red") +
  labs(x = NULL, y = "Sea bottom temperature (C)") +
  ggtitle("Historical and projected average monthly sea bottom temperatures in the Gulf of Maine by decade")
```

*Mean monthly bottom temps by decade/year, red line indicates the decadal average. Bars represent mean monthly temp +/- 1.96 x standard dev.*

### Projected
```{r bottom-temp-plot2, echo = FALSE, fig.height=6, fig.width=10}
projection_temps<-historical_and_projections %>% 
  dplyr::filter(is.na(year))

ggplot(projection_temps, aes(month, mean_temp)) +
  geom_point() +
  geom_errorbar(aes(ymin = lower, ymax = upper)) +
  facet_wrap(~decade, nrow = 1) +
  theme(
    axis.text.x = element_blank(),
    strip.text = element_text(size = 10, margin = margin()),
    axis.ticks.x = element_blank()
  ) +
  geom_hline(aes(yintercept = mean_decadal_tmp), color = "red") +
  labs(x = NULL, y = "Sea bottom temperature (C)") 
ggsave("Z:/cod and haddock/species shift/projection_temps.pdf", width = 8, height = 4)
```

*Mean monthly bottom temps by decade/year, red line indicates the decadal average. Bars represent mean monthly temp +/- 1.96 x standard dev.*

### Historical by year and projected

```{r bottom-temp-plot3, echo = FALSE, fig.height=6, fig.width=10}
ggplot(historical_and_projections_annual, aes(month, mean_temp)) +
  geom_point() +
  geom_errorbar(aes(ymin = lower, ymax = upper)) +
  facet_wrap(~decade, nrow = 1) +
  theme(
    axis.text.x = element_blank(),
    strip.text = element_text(size = 7, margin = margin()),
    axis.ticks.x = element_blank()
  ) +
  geom_hline(aes(yintercept = mean_decadal_tmp), color = "red") +
  labs(x = NULL, y = "Sea bottom temperature (C)") +
  ggtitle("Historical and projected average monthly sea bottom temperatures in the Gulf of Maine by year/decade")
```

*Mean monthly bottom temps by decade/year, red line indicates the decadal average. Bars represent mean monthly temp +/- 1.96 x standard dev.*

<!--
## Model input projected catch-trip-data
```{r echo = FALSE}
final_result<- read_excel(paste0(output_data_cd,"model_input_proj_data.xlsx"))  #save the data

head(final_result)
```
-->

## Coastwide decadal projections - welfare {.tabset}

Each tab contains different projected fishery outcomes across copula models for the case of dependence, independence, and the difference between dependence and independence. Catch data from 2025-04-17. 
```{r echo = FALSE,  fig.width=10}
# coastwide ktau data 
ktau_data<-read_excel(paste0(output_data_cd,"ktau_output_6-2-25.xlsx"))
ktau_annual<-ktau_data %>% filter(month==0 & domain1=="all") %>% 
  dplyr::select(-k_tau_catch_p, -k_tau_keep_p, -domain1)

ktau_annual_long <- ktau_annual %>%
  mutate(parts = str_split(domain, "_", simplify = TRUE),
    correlation = parts[, 1],
    copula = str_extract(parts[, 2], "^[a-zA-Z]+"),
    decade = str_extract(parts[, 2], "[0-9]+")
  ) %>%
  select(draw, correlation, copula, decade, k_tau_keep_est, k_tau_catch_est)


ktau_data_ind<-read_excel(paste0(output_data_cd,"ktau_output_6-2-25_ind.xlsx"))
ktau_annual_ind<-ktau_data_ind %>% filter(month==0 & domain1=="all") %>% 
  dplyr::select(-k_tau_catch_p, -k_tau_keep_p, -domain1)

ktau_annual_ind_long <- ktau_annual_ind %>%
  mutate(parts = str_split(domain, "_", simplify = TRUE),
    correlation = parts[, 1],
    copula = str_extract(parts[, 2], "^[a-zA-Z]+"),
    decade = str_extract(parts[, 2], "[0-9]+")
  ) %>%
  select(draw, correlation, copula, decade, k_tau_keep_est, k_tau_catch_est) %>% 
  dplyr::mutate(copula="independent")

k_tau_baseline <- readRDS(paste0(output_data_cd, "k_tau_baseline.rds")) %>% 
    select(draw,  copula, decade, k_tau_keep_est, k_tau_catch_est)

k_tau_data_combined_coast<-ktau_annual_ind_long %>%
  plyr::rbind.fill(ktau_annual_long, k_tau_baseline) 

# coastwide by state ktau data 
ktau_data<-read_excel(paste0(output_data_cd,"ktau_output_6-2-25.xlsx"))
ktau_annual<-ktau_data %>% filter(month==0 & domain1 %in% c("ME", "NH", "MA")) %>% 
  dplyr::select(-k_tau_catch_p, -k_tau_keep_p) %>% 
  dplyr::rename(state=domain1)

ktau_annual_long <- ktau_annual %>%
  mutate(parts = str_split(domain, "_", simplify = TRUE),
    correlation = parts[, 1],
    copula = str_extract(parts[, 2], "^[a-zA-Z]+"),
    decade = str_extract(parts[, 2], "[0-9]+")
  ) %>%
  select(draw, correlation, copula, decade, k_tau_keep_est, k_tau_catch_est, state)


ktau_data_ind<-read_excel(paste0(output_data_cd,"ktau_output_6-2-25_ind.xlsx"))
ktau_annual_ind<-ktau_data_ind %>% filter(month==0 & domain1 %in% c("ME", "NH", "MA")) %>% 
  dplyr::select(-k_tau_catch_p, -k_tau_keep_p) %>% 
  dplyr::rename(state=domain1)

ktau_annual_ind_long <- ktau_annual_ind %>%
  mutate(parts = str_split(domain, "_", simplify = TRUE),
    correlation = parts[, 1],
    copula = str_extract(parts[, 2], "^[a-zA-Z]+"),
    decade = str_extract(parts[, 2], "[0-9]+")
  ) %>%
  select(draw, correlation, copula, decade, k_tau_keep_est, k_tau_catch_est, state) %>% 
  dplyr::mutate(copula="independent")

# k_tau_baseline <- readRDS(paste0(output_data_cd, "k_tau_baseline.rds")) %>% 
#     select(draw,  copula, decade, k_tau_keep_est, k_tau_catch_est)
# 
# k_tau_data_combined_coast<-ktau_annual_ind_long %>%
#   plyr::rbind.fill(ktau_annual_long, k_tau_baseline) 

k_tau_data_combined_state<-ktau_annual_ind_long %>% 
    plyr::rbind.fill(ktau_annual_long) 

# coastwide by mode ktau data 
ktau_data<-read_excel(paste0(output_data_cd,"ktau_output_6-2-25.xlsx"))
ktau_annual<-ktau_data %>% filter(month==0 & domain1 %in% c("pr", "fh")) %>% 
  dplyr::select(-k_tau_catch_p, -k_tau_keep_p) %>% 
  dplyr::rename(mode=domain1)

ktau_annual_long <- ktau_annual %>%
  mutate(parts = str_split(domain, "_", simplify = TRUE),
    correlation = parts[, 1],
    copula = str_extract(parts[, 2], "^[a-zA-Z]+"),
    decade = str_extract(parts[, 2], "[0-9]+")
  ) %>%
  select(draw, correlation, copula, decade, k_tau_keep_est, k_tau_catch_est, mode)


ktau_data_ind<-read_excel(paste0(output_data_cd,"ktau_output_6-2-25_ind.xlsx"))
ktau_annual_ind<-ktau_data_ind %>% filter(month==0 & domain1 %in% c("pr", "fh")) %>% 
  dplyr::select(-k_tau_catch_p, -k_tau_keep_p) %>% 
  dplyr::rename(mode=domain1)

ktau_annual_ind_long <- ktau_annual_ind %>%
  mutate(parts = str_split(domain, "_", simplify = TRUE),
    correlation = parts[, 1],
    copula = str_extract(parts[, 2], "^[a-zA-Z]+"),
    decade = str_extract(parts[, 2], "[0-9]+")
  ) %>%
  select(draw, correlation, copula, decade, k_tau_keep_est, k_tau_catch_est, mode) %>% 
  dplyr::mutate(copula="independent")

# k_tau_baseline <- readRDS(paste0(output_data_cd, "k_tau_baseline.rds")) %>% 
#     select(draw,  copula, decade, k_tau_keep_est, k_tau_catch_est)
# 
# k_tau_data_combined_coast<-ktau_annual_ind_long %>%
#   plyr::rbind.fill(ktau_annual_long, k_tau_baseline) 

k_tau_data_combined_mode<-ktau_annual_ind_long %>% 
    plyr::rbind.fill(ktau_annual_long) 

```

### CV per trip
```{r echo = FALSE, fig.width=10}
output_summarized1<- read_rds(paste0(output_data_cd,"model_output_6-2-25_reformat_coast.rds"))  %>%
  dplyr::mutate(codreltrip=codrel/ntrips,
                haddreltrip=haddrel/ntrips, 
                codrelchoice=codrel/n_choice_occasions,
                haddrelchoice=haddrel/n_choice_occasions, 
                cod_hadd_keep=codkeep+haddkeep, 
                cod_hadd_cat=codcat+haddcat)

output_summarized1$ntrips[is.na(output_summarized1$ntrips)] <- output_summarized1$dtrip[is.na(output_summarized1$ntrips)]
output_summarized1$copula[output_summarized1$correlation=="independent"] <- "independent"

plot_data<-output_summarized1 %>% 
  dplyr::filter(decade!=0)

ggplot(plot_data, aes(x = factor(decade), y = cvtrip, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Compensating variation per trip ($)")
```

### Difference in CV per trip (corr. - ind.)
```{r echo = FALSE, fig.width=10}
output_summarized1<- read_rds(paste0(output_data_cd,"model_output_6-2-25_reformat_coast.rds"))  %>%
  dplyr::mutate(codreltrip=codrel/ntrips,
                haddreltrip=haddrel/ntrips, 
                codrelchoice=codrel/n_choice_occasions,
                haddrelchoice=haddrel/n_choice_occasions, 
                cod_hadd_keep=codkeep+haddkeep, 
                cod_hadd_cat=codcat+haddcat)

output_summarized1$ntrips[is.na(output_summarized1$ntrips)] <- output_summarized1$dtrip[is.na(output_summarized1$ntrips)]

output_summarized_corr<-output_summarized1 %>% 
  dplyr::filter(correlation=="corr") %>% 
  dplyr::filter(decade!=0) 

output_summarized_ind<-output_summarized1 %>% 
  dplyr::filter(correlation=="independent" ) %>% 
  dplyr::filter(decade!=0) 

cvtrip_diff_corr <- output_summarized_corr %>%
  rename_with(~ paste0(.x, "_corr"), c(cvtrip, cv_choice, cv, ntrips)) %>%
    dplyr::select("draw", "copula","decade","cvtrip_corr", "cv_choice_corr", "cv_corr", "ntrips_corr") %>%     dplyr::filter(decade!=0 )

cvtrip_diff_ind <- output_summarized_ind %>%
  rename_with(~ paste0(.x, "_ind"), c(cvtrip, cv_choice, cv, ntrips)) %>%
    dplyr::select("draw", "copula","decade","cvtrip_ind", "cv_choice_ind", "cv_ind", "ntrips_ind") %>%     dplyr::filter(decade!=0 )

cvtrip_diff<-cvtrip_diff_corr %>% 
    left_join(cvtrip_diff_ind, by=c("draw", "copula","decade" )) %>%
     mutate(diff_ntrips=ntrips_corr- ntrips_ind, 
            diff_cvtrip=cvtrip_corr- cvtrip_ind, 
            diff_cv_choice=cv_choice_corr- cv_choice_ind, 
            diff_cv=cv_corr- cv_ind)

ggplot(cvtrip_diff, aes(x = factor(decade), y = diff_cvtrip, color = factor(copula))) +
   geom_boxplot() +
   labs(x = "Decade", y = "Difference in CV ($) per trip (CV_corr- CV_ind)")
```

### CV per choice occasion
```{r echo = FALSE, fig.width=10}
ggplot(plot_data, aes(x = factor(decade), y = cv_choice, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Compensating variation per choice occasion ($)")
```

### Difference in CV per choice occasion (corr. - ind.)
```{r echo = FALSE, fig.width=10}
ggplot(cvtrip_diff, aes(x = factor(decade), y = diff_cv_choice, color = factor(copula))) +
   geom_boxplot() +
   labs(x = "Decade", y = "Difference in CV ($) per choice occasion (CV_corr- CV_ind)")
```

### Total CV
```{r echo = FALSE, fig.width=10}
ggplot(plot_data, aes(x = factor(decade), y = cv, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Compensating variation ($)")
```

### Difference in total CV (corr. - ind.)
```{r echo = FALSE, fig.width=10}
ggplot(cvtrip_diff, aes(x = factor(decade), y = diff_cv, color = factor(copula))) +
   geom_boxplot() +
   labs(x = "Decade", y = "Difference total CV ($) (CV_corr- CV_ind)")
```

### Total directed trips
```{r echo = FALSE, fig.width=10}
ggplot(plot_data, aes(x = factor(period), y = ntrips, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Number of directed trips")
```

### Difference in total directed trips (corr. - ind.)
```{r echo = FALSE, fig.width=10}
ggplot(cvtrip_diff, aes(x = factor(decade), y = diff_ntrips, color = factor(copula))) +
   geom_boxplot() +
   labs(x = "Decade", y = "Difference in directed trips (dtrips_corr- dtrips_ind)")
```

## Coastwide decadal projections - catch outcomes at the trip level {.tabset}

Catch data from 2025-04-17.

### cod catch per trip
```{r echo = FALSE, fig.width=10}
output_summarized1<- read_rds(paste0(output_data_cd,"model_output_6-2-25_reformat_coast.rds"))  %>%
  dplyr::mutate(codreltrip=codrel/ntrips,
                haddreltrip=haddrel/ntrips, 
                codrelchoice=codrel/n_choice_occasions,
                haddrelchoice=haddrel/n_choice_occasions, 
                cod_hadd_keep=codkeep+haddkeep, 
                cod_hadd_cat=codcat+haddcat)

output_summarized1$ntrips[is.na(output_summarized1$ntrips)] <- output_summarized1$dtrip[is.na(output_summarized1$ntrips)]
output_summarized1$copula[output_summarized1$correlation=="independent"] <- "independent"

ggplot(output_summarized1, aes(x=period, y=codcattrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod catch per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### cod keep per trip
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=codkeeptrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod harvest per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### cod release per trip
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=codreltrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod release per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### haddock catch per trip
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=haddcattrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock catch per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### haddock keep per trip
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=haddkeeptrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock harvest per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### haddock release per trip 
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=haddreltrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock release per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### k-tau catch
```{r echo = FALSE, fig.width=10}
ggplot(k_tau_data_combined_coast, aes(x=decade, y=k_tau_catch_est, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Decade", y = "Kendall's tau")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### k-tau keep
```{r echo = FALSE, fig.width=10}
ggplot(k_tau_data_combined_coast, aes(x=decade, y=k_tau_keep_est, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Decade", y = "Kendall's tau")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## Coastwide decadal projections - catch outcomes at the choice occasion level {.tabset}

Catch data from 2025-04-17.

### cod catch per choice occasion
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=codcatchoice, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod catch per choice occasion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### cod keep per choice occasion
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=codkeepchoice, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod harvest per choice occasion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### cod release per choice occasion
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=codrelchoice, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod release per choice occasion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### haddock catch per choice occasion
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=haddcatchoice, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock catch per choice occasion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### haddock keep per choice occasion
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=haddkeepchoice, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock harvest per choice occassion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### haddock release per choice occasion
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=haddrelchoice, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock release per choice occasion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## Coastwide decadal projections - aggregate catch outcomes  {.tabset}

### cod harvest 
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=codkeep, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod harvest")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### haddock harvest 
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=haddkeep, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock harvest")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### cod plus haddock harvest 
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=cod_hadd_keep, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod plus haddock harvest")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### cod catch 
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=codcat, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod catch")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### haddock catch 
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=haddcat, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock catch")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### cod plus haddock catch 
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=cod_hadd_cat, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod plus haddock catch")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### Diff. total cod harvest (corr. - ind.)
```{r echo = FALSE, fig.width=10}
output_summarized1<- read_rds(paste0(output_data_cd,"model_output_6-2-25_reformat_coast.rds"))  %>%
  dplyr::mutate(codreltrip=codrel/ntrips,
                haddreltrip=haddrel/ntrips, 
                codrelchoice=codrel/n_choice_occasions,
                haddrelchoice=haddrel/n_choice_occasions, 
                cod_hadd_keep=codkeep+haddkeep, 
                cod_hadd_cat=codcat+haddcat)

output_summarized1$ntrips[is.na(output_summarized1$ntrips)] <- output_summarized1$dtrip[is.na(output_summarized1$ntrips)]

output_summarized_corr<-output_summarized1 %>% 
  dplyr::filter(correlation=="corr") %>% 
  dplyr::filter(decade!=0) 

output_summarized_ind<-output_summarized1 %>% 
  dplyr::filter(correlation=="independent" ) %>% 
  dplyr::filter(decade!=0) 

diff_corr <- output_summarized_corr %>%
  rename_with(~ paste0(.x, "_corr"), c(codkeep, haddkeep, codcat, haddcat, 
                                       cod_hadd_keep, cod_hadd_cat)) %>%
    dplyr::select("draw", "copula","decade","codkeep_corr", "haddkeep_corr", 
                  "codcat_corr", "haddcat_corr", "cod_hadd_keep_corr", "cod_hadd_cat_corr") %>%   
                                       dplyr::filter(decade!=0 )

diff_ind <- output_summarized_ind %>%
  rename_with(~ paste0(.x, "_ind"), c(codkeep, haddkeep, codcat, haddcat, 
                                       cod_hadd_keep, cod_hadd_cat)) %>%
    dplyr::select("draw", "copula","decade","codkeep_ind", "haddkeep_ind", 
                  "codcat_ind", "haddcat_ind", "cod_hadd_keep_ind", "cod_hadd_cat_ind") %>%   
                                       dplyr::filter(decade!=0 )

diff<-diff_corr %>% 
    left_join(diff_ind, by=c("draw", "copula","decade" )) %>%
     mutate(diff_codkeep=codkeep_corr- codkeep_ind, 
            diff_haddkeep=haddkeep_corr- haddkeep_ind, 
            diff_codcat=codcat_corr- codcat_ind, 
            diff_haddcat=haddcat_corr- haddcat_ind, 
            diff_cod_hadd_keep=cod_hadd_keep_corr- cod_hadd_keep_ind, 
            diff_cod_hadd_cat=cod_hadd_cat_corr- cod_hadd_cat_ind )

ggplot(diff, aes(x = factor(decade), y = diff_codkeep, color = factor(copula))) +
   geom_boxplot() +
   labs(x = "Decade", y = "Difference in total cod harvest (CV_corr- CV_ind)")
```

### Diff. total cod catch
```{r echo = FALSE, fig.width=10}
ggplot(diff, aes(x = factor(decade), y = diff_codcat, color = factor(copula))) +
   geom_boxplot() +
   labs(x = "Decade", y = "Difference in total cod catch (CV_corr- CV_ind)")
```

### Diff. total haddock harvest
```{r echo = FALSE, fig.width=10}
ggplot(diff, aes(x = factor(decade), y = diff_haddkeep, color = factor(copula))) +
   geom_boxplot() +
   labs(x = "Decade", y = "Difference in total haddock harvest (CV_corr- CV_ind)")
```

### Diff. total haddock catch
```{r echo = FALSE, fig.width=10}
ggplot(diff, aes(x = factor(decade), y = diff_haddcat, color = factor(copula))) +
   geom_boxplot() +
   labs(x = "Decade", y = "Difference in total haddock catch (CV_corr- CV_ind)")
```

### Diff. total cod plus haddock harvest
```{r echo = FALSE, fig.width=10}
ggplot(diff, aes(x = factor(decade), y = diff_cod_hadd_keep, color = factor(copula))) +
   geom_boxplot() +
   labs(x = "Decade", y = "Difference in total cod plus haddock harvest (CV_corr- CV_ind)")
```

### Diff. total cod plus haddock catch
```{r echo = FALSE, fig.width=10}
ggplot(diff, aes(x = factor(decade), y = diff_cod_hadd_cat, color = factor(copula))) +
   geom_boxplot() +
   labs(x = "Decade", y = "Difference in total cod plus haddock catch (CV_corr- CV_ind)")
```

## Fishing-mode level decadal projections - welfare {.tabset}

Each tab contains different projected fishery outcomes across copula models for the case of dependence, independence, and the difference between dependence and independence. Catch data from 2025-04-17. 
```{r echo = FALSE,  fig.width=10}
#ktau data 
# ktau_data<-read_excel(paste0(output_data_cd,"ktau_output_6-2-25.xlsx"))
# ktau_annual<-ktau_data %>% filter(month==0) %>% 
#   dplyr::select(-k_tau_catch_p, -k_tau_keep_p)
# 
# ktau_annual_long <- ktau_annual %>%
#   mutate(parts = str_split(domain, "_", simplify = TRUE),
#     correlation = parts[, 1],
#     copula = str_extract(parts[, 2], "^[a-zA-Z]+"),
#     decade = str_extract(parts[, 2], "[0-9]+")
#   ) %>%
#   select(draw, correlation, copula, decade, k_tau_keep_est, k_tau_catch_est)
# 
# 
# ktau_data_ind<-read_excel(paste0(output_data_cd,"ktau_output_6-2-25_ind.xlsx"))
# ktau_annual_ind<-ktau_data_ind %>% filter(month==0) %>% 
#   dplyr::select(-k_tau_catch_p, -k_tau_keep_p)
# 
# ktau_annual_ind_long <- ktau_annual_ind %>%
#   mutate(parts = str_split(domain, "_", simplify = TRUE),
#     correlation = parts[, 1],
#     copula = str_extract(parts[, 2], "^[a-zA-Z]+"),
#     decade = str_extract(parts[, 2], "[0-9]+")
#   ) %>%
#   select(draw, correlation, copula, decade, k_tau_keep_est, k_tau_catch_est) %>% 
#   dplyr::mutate(copula="independent")
# 
# k_tau_data_comnined<-ktau_annual_ind_long %>%
#   plyr::rbind.fill(ktau_annual_long) 
```

### CV per trip
```{r echo = FALSE, fig.width=10}
output_summarized1<- read_rds(paste0(output_data_cd,"model_output_6-2-25_reformat_mode.rds"))  %>%
  dplyr::mutate(codreltrip=codrel/ntrips,
                haddreltrip=haddrel/ntrips, 
                codrelchoice=codrel/n_choice_occasions,
                haddrelchoice=haddrel/n_choice_occasions, 
                cod_hadd_keep=codkeep+haddkeep, 
                cod_hadd_cat=codcat+haddcat)

output_summarized1$ntrips[is.na(output_summarized1$ntrips)] <- output_summarized1$dtrip[is.na(output_summarized1$ntrips)]
output_summarized1$copula[output_summarized1$correlation=="independent"] <- "independent"

plot_data<-output_summarized1 %>% 
  dplyr::filter(decade!=0)

ggplot(plot_data, aes(x = factor(decade), y = cvtrip, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Compensating variation per trip ($)") +
  facet_wrap(~ mode)
```

### Difference in CV per trip (corr. - ind.)
```{r echo = FALSE, fig.width=10}
output_summarized1<- read_rds(paste0(output_data_cd,"model_output_6-2-25_reformat_mode.rds"))  %>%
  dplyr::mutate(codreltrip=codrel/ntrips,
                haddreltrip=haddrel/ntrips, 
                codrelchoice=codrel/n_choice_occasions,
                haddrelchoice=haddrel/n_choice_occasions, 
                cod_hadd_keep=codkeep+haddkeep, 
                cod_hadd_cat=codcat+haddcat)

output_summarized1$ntrips[is.na(output_summarized1$ntrips)] <- output_summarized1$dtrip[is.na(output_summarized1$ntrips)]

output_summarized_corr<-output_summarized1 %>% 
  dplyr::filter(correlation=="corr") %>% 
  dplyr::filter(decade!=0) 

output_summarized_ind<-output_summarized1 %>% 
  dplyr::filter(correlation=="independent" ) %>% 
  dplyr::filter(decade!=0) 

cvtrip_diff_corr <- output_summarized_corr %>%
  rename_with(~ paste0(.x, "_corr"), c(cvtrip, cv_choice, cv, ntrips)) %>%
    dplyr::select("draw", "mode", "copula","decade","cvtrip_corr", "cv_choice_corr", "cv_corr", "ntrips_corr") %>%     dplyr::filter(decade!=0 )

cvtrip_diff_ind <- output_summarized_ind %>%
  rename_with(~ paste0(.x, "_ind"), c(cvtrip, cv_choice, cv, ntrips)) %>%
    dplyr::select("draw", "mode", "copula","decade","cvtrip_ind", "cv_choice_ind", "cv_ind", "ntrips_ind") %>%     dplyr::filter(decade!=0 )

cvtrip_diff<-cvtrip_diff_corr %>% 
    left_join(cvtrip_diff_ind, by=c("draw","mode", "copula","decade" )) %>%
     mutate(diff_ntrips=ntrips_corr- ntrips_ind, 
            diff_cvtrip=cvtrip_corr- cvtrip_ind, 
            diff_cv_choice=cv_choice_corr- cv_choice_ind, 
            diff_cv=cv_corr- cv_ind)

ggplot(cvtrip_diff, aes(x = factor(decade), y = diff_cvtrip, color = factor(copula))) +
   geom_boxplot() +
   labs(x = "Decade", y = "Difference in CV ($) per trip (CV_corr- CV_ind)") +
  facet_wrap(~ mode)
```

### CV per choice occasion
```{r echo = FALSE, fig.width=10}
ggplot(plot_data, aes(x = factor(decade), y = cv_choice, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Compensating variation per choice occasion ($)")+
  facet_wrap(~ mode)
```

### Difference in CV per choice occasion (corr. - ind.)
```{r echo = FALSE, fig.width=10}
ggplot(cvtrip_diff, aes(x = factor(decade), y = diff_cv_choice, color = factor(copula))) +
   geom_boxplot() +
   labs(x = "Decade", y = "Difference in CV ($) per choice occasion (CV_corr- CV_ind)")+
  facet_wrap(~ mode)
```

### Total CV
```{r echo = FALSE, fig.width=10}
ggplot(plot_data, aes(x = factor(decade), y = cv, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Compensating variation ($)")+
  facet_wrap(~ mode)
```

### Difference in total CV (corr. - ind.)
```{r echo = FALSE, fig.width=10}
ggplot(cvtrip_diff, aes(x = factor(decade), y = diff_cv, color = factor(copula))) +
   geom_boxplot() +
   labs(x = "Decade", y = "Difference total CV ($) (CV_corr- CV_ind)")+
  facet_wrap(~ mode)
```

### Total directed trips
```{r echo = FALSE, fig.width=10}
ggplot(plot_data, aes(x = factor(period), y = ntrips, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Number of directed trips")+
  facet_wrap(~ mode)
```

### Difference in total directed trips (corr. - ind.)
```{r echo = FALSE, fig.width=10}
ggplot(cvtrip_diff, aes(x = factor(decade), y = diff_ntrips, color = factor(copula))) +
   geom_boxplot() +
   labs(x = "Decade", y = "Difference in directed trips (dtrips_corr- dtrips_ind)")+
  facet_wrap(~ mode)
```

## Fishing-mode level decadal projections - catch outcomes at the trip level {.tabset}

Catch data from 2025-04-17.

### cod catch per trip
```{r echo = FALSE, fig.width=10}
output_summarized1<- read_rds(paste0(output_data_cd,"model_output_6-2-25_reformat_mode.rds"))  %>%
  dplyr::mutate(codreltrip=codrel/ntrips,
                haddreltrip=haddrel/ntrips, 
                codrelchoice=codrel/n_choice_occasions,
                haddrelchoice=haddrel/n_choice_occasions, 
                cod_hadd_keep=codkeep+haddkeep, 
                cod_hadd_cat=codcat+haddcat)

output_summarized1$ntrips[is.na(output_summarized1$ntrips)] <- output_summarized1$dtrip[is.na(output_summarized1$ntrips)]
output_summarized1$copula[output_summarized1$correlation=="independent"] <- "independent"

ggplot(output_summarized1, aes(x=period, y=codcattrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod catch per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ mode)
```

### cod keep per trip
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=codkeeptrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod harvest per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ mode)
```

### cod release per trip
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=codreltrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod release per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ mode)
```

### haddock catch per trip
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=haddcattrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock catch per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ mode)
```

### haddock keep per trip
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=haddkeeptrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock harvest per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ mode)
```

### haddock release per trip 
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=haddreltrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock release per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~ mode)
```

### k-tau catch
```{r echo = FALSE, fig.width=10}
ggplot(k_tau_data_combined_mode, aes(x=decade, y=k_tau_catch_est, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Decade", y = "Kendall's tau")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~ mode)
```

### k-tau keep
```{r echo = FALSE, fig.width=10}
ggplot(k_tau_data_combined_mode, aes(x=decade, y=k_tau_keep_est, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Decade", y = "Kendall's tau")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~ mode)
```

## Fishing-mode decadal projections - catch outcomes at the choice occasion level {.tabset}

Catch data from 2025-04-17.

### cod catch per choice occasion
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=codcatchoice, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod catch per choice occasion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ mode)
```

### cod keep per choice occasion
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=codkeepchoice, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod harvest per choice occasion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ mode)
```

### cod release per choice occasion (correlated)
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=codrelchoice, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod release per choice occasion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ mode)
```

### haddock catch per choice occasion
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=haddcatchoice, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock catch per choice occasion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ mode)
```

### haddock keep per choice occasion
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=haddkeepchoice, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock harvest per choice occassion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ mode)
```

### haddock release per choice occasion
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=haddrelchoice, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock release per choice occasion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ mode)
```

## Fishing-mode decadal projections - aggregate catch outcomes  {.tabset}

### cod harvest 
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=codkeep, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod harvest")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ mode)
```

### haddock harvest 
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=haddkeep, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock harvest")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ mode)
```

### cod plus haddock harvest 
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=cod_hadd_keep, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod plus haddock harvest")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ mode)
```

### cod catch 
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=codcat, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod catch")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ mode)
```

### haddock catch 
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=haddcat, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock catch")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ mode)
```

### cod plus haddock catch 
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=cod_hadd_cat, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod plus haddock catch")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ mode)
```

### Diff. total cod harvest (corr. - ind.)
```{r echo = FALSE, fig.width=10}
output_summarized1<- read_rds(paste0(output_data_cd,"model_output_6-2-25_reformat_mode.rds"))  %>%
  dplyr::mutate(codreltrip=codrel/ntrips,
                haddreltrip=haddrel/ntrips, 
                codrelchoice=codrel/n_choice_occasions,
                haddrelchoice=haddrel/n_choice_occasions, 
                cod_hadd_keep=codkeep+haddkeep, 
                cod_hadd_cat=codcat+haddcat)

output_summarized1$ntrips[is.na(output_summarized1$ntrips)] <- output_summarized1$dtrip[is.na(output_summarized1$ntrips)]

output_summarized_corr<-output_summarized1 %>% 
  dplyr::filter(correlation=="corr") %>% 
  dplyr::filter(decade!=0) 

output_summarized_ind<-output_summarized1 %>% 
  dplyr::filter(correlation=="independent" ) %>% 
  dplyr::filter(decade!=0) 

diff_corr <- output_summarized_corr %>%
  rename_with(~ paste0(.x, "_corr"), c(codkeep, haddkeep, codcat, haddcat, 
                                       cod_hadd_keep, cod_hadd_cat)) %>%
    dplyr::select("draw", "copula","decade","mode", "codkeep_corr", "haddkeep_corr", 
                  "codcat_corr", "haddcat_corr", "cod_hadd_keep_corr", "cod_hadd_cat_corr") %>%   
                                       dplyr::filter(decade!=0 )

diff_ind <- output_summarized_ind %>%
  rename_with(~ paste0(.x, "_ind"), c(codkeep, haddkeep, codcat, haddcat, 
                                       cod_hadd_keep, cod_hadd_cat)) %>%
    dplyr::select("draw", "copula","decade","mode","codkeep_ind", "haddkeep_ind", 
                  "codcat_ind", "haddcat_ind", "cod_hadd_keep_ind", "cod_hadd_cat_ind") %>%   
                                       dplyr::filter(decade!=0 )

diff<-diff_corr %>% 
    left_join(diff_ind, by=c("draw", "copula","decade","mode" )) %>%
     mutate(diff_codkeep=codkeep_corr- codkeep_ind, 
            diff_haddkeep=haddkeep_corr- haddkeep_ind, 
            diff_codcat=codcat_corr- codcat_ind, 
            diff_haddcat=haddcat_corr- haddcat_ind, 
            diff_cod_hadd_keep=cod_hadd_keep_corr- cod_hadd_keep_ind, 
            diff_cod_hadd_cat=cod_hadd_cat_corr- cod_hadd_cat_ind )

ggplot(diff, aes(x = factor(decade), y = diff_codkeep, color = factor(copula))) +
   geom_boxplot() +
   labs(x = "Decade", y = "Difference in total cod harvest (CV_corr- CV_ind)")+
  facet_wrap(~ mode)
```

### Diff. total cod catch
```{r echo = FALSE, fig.width=10}
ggplot(diff, aes(x = factor(decade), y = diff_codcat, color = factor(copula))) +
   geom_boxplot() +
   labs(x = "Decade", y = "Difference in total cod catch (CV_corr- CV_ind)")+
  facet_wrap(~ mode)
```

### Diff. total haddock harvest
```{r echo = FALSE, fig.width=10}
ggplot(diff, aes(x = factor(decade), y = diff_haddkeep, color = factor(copula))) +
   geom_boxplot() +
   labs(x = "Decade", y = "Difference in total haddock harvest (CV_corr- CV_ind)")+
  facet_wrap(~ mode)
```

### Diff. total haddock catch
```{r echo = FALSE, fig.width=10}
ggplot(diff, aes(x = factor(decade), y = diff_haddcat, color = factor(copula))) +
   geom_boxplot() +
   labs(x = "Decade", y = "Difference in total haddock catch (CV_corr- CV_ind)")+
  facet_wrap(~ mode)
```

### Diff. total cod plus haddock harvest
```{r echo = FALSE, fig.width=10}
ggplot(diff, aes(x = factor(decade), y = diff_cod_hadd_keep, color = factor(copula))) +
   geom_boxplot() +
   labs(x = "Decade", y = "Difference in total cod plus haddock harvest (CV_corr- CV_ind)")+
  facet_wrap(~ mode)
```

### Diff. total cod plus haddock catch
```{r echo = FALSE, fig.width=10}
ggplot(diff, aes(x = factor(decade), y = diff_cod_hadd_cat, color = factor(copula))) +
   geom_boxplot() +
   labs(x = "Decade", y = "Difference in total cod plus haddock catch (CV_corr- CV_ind)")+
  facet_wrap(~ mode)
```

## State-level decadal projections - welfare {.tabset}

Each tab contains different projected fishery outcomes across copula models for the case of dependence, independence, and the difference between dependence and independence. Catch data from 2025-04-17. 
```{r echo = FALSE,  fig.width=10}
#ktau data 
# ktau_data<-read_excel(paste0(output_data_cd,"ktau_output_6-2-25.xlsx"))
# ktau_annual<-ktau_data %>% filter(month==0) %>% 
#   dplyr::select(-k_tau_catch_p, -k_tau_keep_p)
# 
# ktau_annual_long <- ktau_annual %>%
#   mutate(parts = str_split(domain, "_", simplify = TRUE),
#     correlation = parts[, 1],
#     copula = str_extract(parts[, 2], "^[a-zA-Z]+"),
#     decade = str_extract(parts[, 2], "[0-9]+")
#   ) %>%
#   select(draw, correlation, copula, decade, k_tau_keep_est, k_tau_catch_est)
# 
# 
# ktau_data_ind<-read_excel(paste0(output_data_cd,"ktau_output_6-2-25_ind.xlsx"))
# ktau_annual_ind<-ktau_data_ind %>% filter(month==0) %>% 
#   dplyr::select(-k_tau_catch_p, -k_tau_keep_p)
# 
# ktau_annual_ind_long <- ktau_annual_ind %>%
#   mutate(parts = str_split(domain, "_", simplify = TRUE),
#     correlation = parts[, 1],
#     copula = str_extract(parts[, 2], "^[a-zA-Z]+"),
#     decade = str_extract(parts[, 2], "[0-9]+")
#   ) %>%
#   select(draw, correlation, copula, decade, k_tau_keep_est, k_tau_catch_est) %>% 
#   dplyr::mutate(copula="independent")
# 
# k_tau_data_comnined<-ktau_annual_ind_long %>%
#   plyr::rbind.fill(ktau_annual_long) 
```

### CV per trip
```{r echo = FALSE, fig.width=10}
output_summarized1<- read_rds(paste0(output_data_cd,"model_output_6-2-25_reformat_state.rds"))  %>%
  dplyr::mutate(codreltrip=codrel/ntrips,
                haddreltrip=haddrel/ntrips, 
                codrelchoice=codrel/n_choice_occasions,
                haddrelchoice=haddrel/n_choice_occasions, 
                cod_hadd_keep=codkeep+haddkeep, 
                cod_hadd_cat=codcat+haddcat)

output_summarized1$ntrips[is.na(output_summarized1$ntrips)] <- output_summarized1$dtrip[is.na(output_summarized1$ntrips)]
output_summarized1$copula[output_summarized1$correlation=="independent"] <- "independent"

plot_data<-output_summarized1 %>% 
  dplyr::filter(decade!=0)

ggplot(plot_data, aes(x = factor(decade), y = cvtrip, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Compensating variation per trip ($)") +
  facet_wrap(~ state)
```

### Difference in CV per trip (corr. - ind.)
```{r echo = FALSE, fig.width=10}
output_summarized1<- read_rds(paste0(output_data_cd,"model_output_6-2-25_reformat_state.rds"))  %>%
  dplyr::mutate(codreltrip=codrel/ntrips,
                haddreltrip=haddrel/ntrips, 
                codrelchoice=codrel/n_choice_occasions,
                haddrelchoice=haddrel/n_choice_occasions, 
                cod_hadd_keep=codkeep+haddkeep, 
                cod_hadd_cat=codcat+haddcat)

output_summarized1$ntrips[is.na(output_summarized1$ntrips)] <- output_summarized1$dtrip[is.na(output_summarized1$ntrips)]

output_summarized_corr<-output_summarized1 %>% 
  dplyr::filter(correlation=="corr") %>% 
  dplyr::filter(decade!=0) 

output_summarized_ind<-output_summarized1 %>% 
  dplyr::filter(correlation=="independent" ) %>% 
  dplyr::filter(decade!=0) 

cvtrip_diff_corr <- output_summarized_corr %>%
  rename_with(~ paste0(.x, "_corr"), c(cvtrip, cv_choice, cv, ntrips)) %>%
    dplyr::select("draw", "state", "copula","decade","cvtrip_corr", "cv_choice_corr", "cv_corr", "ntrips_corr") %>%     dplyr::filter(decade!=0 )

cvtrip_diff_ind <- output_summarized_ind %>%
  rename_with(~ paste0(.x, "_ind"), c(cvtrip, cv_choice, cv, ntrips)) %>%
    dplyr::select("draw", "state", "copula","decade","cvtrip_ind", "cv_choice_ind", "cv_ind", "ntrips_ind") %>%     dplyr::filter(decade!=0 )

cvtrip_diff<-cvtrip_diff_corr %>% 
    left_join(cvtrip_diff_ind, by=c("draw","state", "copula","decade" )) %>%
     mutate(diff_ntrips=ntrips_corr- ntrips_ind, 
            diff_cvtrip=cvtrip_corr- cvtrip_ind, 
            diff_cv_choice=cv_choice_corr- cv_choice_ind, 
            diff_cv=cv_corr- cv_ind)

ggplot(cvtrip_diff, aes(x = factor(decade), y = diff_cvtrip, color = factor(copula))) +
   geom_boxplot() +
   labs(x = "Decade", y = "Difference in CV ($) per trip (CV_corr- CV_ind)") +
  facet_wrap(~ state)
```

### CV per choice occasion
```{r echo = FALSE, fig.width=10}
ggplot(plot_data, aes(x = factor(decade), y = cv_choice, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Compensating variation per choice occasion ($)")+
  facet_wrap(~ state)
```

### Difference in CV per choice occasion (corr. - ind.)
```{r echo = FALSE, fig.width=10}
ggplot(cvtrip_diff, aes(x = factor(decade), y = diff_cv_choice, color = factor(copula))) +
   geom_boxplot() +
   labs(x = "Decade", y = "Difference in CV ($) per choice occasion (CV_corr- CV_ind)")+
  facet_wrap(~ state)
```

### Total CV
```{r echo = FALSE, fig.width=10}
ggplot(plot_data, aes(x = factor(decade), y = cv, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Compensating variation ($)")+
  facet_wrap(~ state)
```

### Difference in total CV (corr. - ind.)
```{r echo = FALSE, fig.width=10}
ggplot(cvtrip_diff, aes(x = factor(decade), y = diff_cv, color = factor(copula))) +
   geom_boxplot() +
   labs(x = "Decade", y = "Difference total CV ($) (CV_corr- CV_ind)")+
  facet_wrap(~ state)
```

### Total directed trips
```{r echo = FALSE, fig.width=10}
ggplot(plot_data, aes(x = factor(period), y = ntrips, color = factor(copula))) +
  geom_boxplot() +
  labs(x = "Decade", y = "Number of directed trips")+
  facet_wrap(~ state)
```

### Difference in total directed trips (corr. - ind.)
```{r echo = FALSE, fig.width=10}
ggplot(cvtrip_diff, aes(x = factor(decade), y = diff_ntrips, color = factor(copula))) +
   geom_boxplot() +
   labs(x = "Decade", y = "Difference in directed trips (dtrips_corr- dtrips_ind)")+
  facet_wrap(~ state)
```

## State-level  level decadal projections - catch outcomes at the trip level {.tabset}

Catch data from 2025-04-17.

### cod catch per trip
```{r echo = FALSE, fig.width=10}
output_summarized1<- read_rds(paste0(output_data_cd,"model_output_6-2-25_reformat_state.rds"))  %>%
  dplyr::mutate(codreltrip=codrel/ntrips,
                haddreltrip=haddrel/ntrips, 
                codrelchoice=codrel/n_choice_occasions,
                haddrelchoice=haddrel/n_choice_occasions, 
                cod_hadd_keep=codkeep+haddkeep, 
                cod_hadd_cat=codcat+haddcat)

output_summarized1$ntrips[is.na(output_summarized1$ntrips)] <- output_summarized1$dtrip[is.na(output_summarized1$ntrips)]
output_summarized1$copula[output_summarized1$correlation=="independent"] <- "independent"

ggplot(output_summarized1, aes(x=period, y=codcattrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod catch per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ state)
```

### cod keep per trip
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=codkeeptrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod harvest per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ state)
```

### cod release per trip
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=codreltrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod release per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ state)
```

### haddock catch per trip
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=haddcattrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock catch per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ state)
```

### haddock keep per trip
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=haddkeeptrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock harvest per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ state)
```

### haddock release per trip 
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=haddreltrip, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock release per trip")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ state)
```

### k-tau catch
```{r echo = FALSE, fig.width=10}
ggplot(k_tau_data_combined_state, aes(x=decade, y=k_tau_catch_est, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Decade", y = "Kendall's tau")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~ state)
```

### k-tau keep
```{r echo = FALSE, fig.width=10}
ggplot(k_tau_data_combined_state, aes(x=decade, y=k_tau_keep_est, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Decade", y = "Kendall's tau")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~ state)
```

## State-level decadal projections - catch outcomes at the choice occasion level {.tabset}

Catch data from 2025-04-17.

### cod catch per choice occasion
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=codcatchoice, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod catch per choice occasion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ state)
```

### cod keep per choice occasion
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=codkeepchoice, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod harvest per choice occasion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ state)
```

### cod release per choice occasion (correlated)
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=codrelchoice, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod release per choice occasion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ state)
```

### haddock catch per choice occasion
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=haddcatchoice, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock catch per choice occasion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ state)
```

### haddock keep per choice occasion
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=haddkeepchoice, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock harvest per choice occassion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ state)
```

### haddock release per choice occasion
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=haddrelchoice, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock release per choice occasion")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ state)
```

## State-level decadal projections - aggregate catch outcomes  {.tabset}

### cod harvest 
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=codkeep, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod harvest")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ state)
```

### haddock harvest 
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=haddkeep, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock harvest")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ state)
```

### cod plus haddock harvest 
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=cod_hadd_keep, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod plus haddock harvest")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ state)
```

### cod catch 
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=codcat, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod catch")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ state)
```

### haddock catch 
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=haddcat, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Haddock catch")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ state)
```

### cod plus haddock catch 
```{r echo = FALSE, fig.width=10}
ggplot(output_summarized1, aes(x=period, y=cod_hadd_cat, color = factor(copula)))+
  geom_boxplot() +
  labs(x = "Period", y = "Cod plus haddock catch")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~ state)
```

### Diff. total cod harvest (corr. - ind.)
```{r echo = FALSE, fig.width=10}
output_summarized1<- read_rds(paste0(output_data_cd,"model_output_6-2-25_reformat_state.rds"))  %>%
  dplyr::mutate(codreltrip=codrel/ntrips,
                haddreltrip=haddrel/ntrips, 
                codrelchoice=codrel/n_choice_occasions,
                haddrelchoice=haddrel/n_choice_occasions, 
                cod_hadd_keep=codkeep+haddkeep, 
                cod_hadd_cat=codcat+haddcat)

output_summarized1$ntrips[is.na(output_summarized1$ntrips)] <- output_summarized1$dtrip[is.na(output_summarized1$ntrips)]

output_summarized_corr<-output_summarized1 %>% 
  dplyr::filter(correlation=="corr") %>% 
  dplyr::filter(decade!=0) 

output_summarized_ind<-output_summarized1 %>% 
  dplyr::filter(correlation=="independent" ) %>% 
  dplyr::filter(decade!=0) 

diff_corr <- output_summarized_corr %>%
  rename_with(~ paste0(.x, "_corr"), c(codkeep, haddkeep, codcat, haddcat, 
                                       cod_hadd_keep, cod_hadd_cat)) %>%
    dplyr::select("draw", "copula","decade","state", "codkeep_corr", "haddkeep_corr", 
                  "codcat_corr", "haddcat_corr", "cod_hadd_keep_corr", "cod_hadd_cat_corr") %>%   
                                       dplyr::filter(decade!=0 )

diff_ind <- output_summarized_ind %>%
  rename_with(~ paste0(.x, "_ind"), c(codkeep, haddkeep, codcat, haddcat, 
                                       cod_hadd_keep, cod_hadd_cat)) %>%
    dplyr::select("draw", "copula","decade","state","codkeep_ind", "haddkeep_ind", 
                  "codcat_ind", "haddcat_ind", "cod_hadd_keep_ind", "cod_hadd_cat_ind") %>%   
                                       dplyr::filter(decade!=0 )

diff<-diff_corr %>% 
    left_join(diff_ind, by=c("draw", "copula","decade","state" )) %>%
     mutate(diff_codkeep=codkeep_corr- codkeep_ind, 
            diff_haddkeep=haddkeep_corr- haddkeep_ind, 
            diff_codcat=codcat_corr- codcat_ind, 
            diff_haddcat=haddcat_corr- haddcat_ind, 
            diff_cod_hadd_keep=cod_hadd_keep_corr- cod_hadd_keep_ind, 
            diff_cod_hadd_cat=cod_hadd_cat_corr- cod_hadd_cat_ind )

ggplot(diff, aes(x = factor(decade), y = diff_codkeep, color = factor(copula))) +
   geom_boxplot() +
   labs(x = "Decade", y = "Difference in total cod harvest (CV_corr- CV_ind)")+
  facet_wrap(~ state)
```

### Diff. total cod catch
```{r echo = FALSE, fig.width=10}
ggplot(diff, aes(x = factor(decade), y = diff_codcat, color = factor(copula))) +
   geom_boxplot() +
   labs(x = "Decade", y = "Difference in total cod catch (CV_corr- CV_ind)")+
  facet_wrap(~ state)
```

### Diff. total haddock harvest
```{r echo = FALSE, fig.width=10}
ggplot(diff, aes(x = factor(decade), y = diff_haddkeep, color = factor(copula))) +
   geom_boxplot() +
   labs(x = "Decade", y = "Difference in total haddock harvest (CV_corr- CV_ind)")+
  facet_wrap(~ state)
```

### Diff. total haddock catch
```{r echo = FALSE, fig.width=10}
ggplot(diff, aes(x = factor(decade), y = diff_haddcat, color = factor(copula))) +
   geom_boxplot() +
   labs(x = "Decade", y = "Difference in total haddock catch (CV_corr- CV_ind)")+
  facet_wrap(~ state)
```

### Diff. total cod plus haddock harvest
```{r echo = FALSE, fig.width=10}
ggplot(diff, aes(x = factor(decade), y = diff_cod_hadd_keep, color = factor(copula))) +
   geom_boxplot() +
   labs(x = "Decade", y = "Difference in total cod plus haddock harvest (CV_corr- CV_ind)")+
  facet_wrap(~ state)
```

### Diff. total cod plus haddock catch
```{r echo = FALSE, fig.width=10}
ggplot(diff, aes(x = factor(decade), y = diff_cod_hadd_cat, color = factor(copula))) +
   geom_boxplot() +
   labs(x = "Decade", y = "Difference in total cod plus haddock catch (CV_corr- CV_ind)")+
  facet_wrap(~ state)
```
