

---
title: "GoM cod and haddock RDM"
author: "Lou Carr-Harris"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: cerulean
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(comment = NA)
cat('<pre>')
pkgs_to_use <- c("tidyr",  "magrittr", "tidyverse", "reshape2","splitstackshape",
                 "doBy","WriteXLS","Rcpp", "ggplot2","dplyr", "rlist","fitdistrplus",
                 "MASS",  "psych", "rgl","copula", "VineCopula","scales","univariateML",
                 "logspline","readr","data.table","conflicted", "readxl", "writexl", "stringr",
                 "plyr" , "furrr", "profvis", "future", "Hmisc", "tictoc", "sjPlot", "gridExtra", 
                 "rmdformats", "prettydoc", "hrbrthemes", "tint", "tufte", "knitr", "hrbrthemes", "ggpubr")
install.packages(setdiff(pkgs_to_use, rownames(installed.packages())))  
lapply(pkgs_to_use, library, character.only = TRUE, quietly = TRUE)
conflicts_prefer(dplyr::filter)
conflicts_prefer(dplyr::select)
conflicts_prefer(dplyr::mutate)
conflicts_prefer(dplyr::rename)
conflicts_prefer(dplyr::summarize)
conflicts_prefer(dplyr::summarise)
conflicts_prefer(dplyr::count)

output_data_cd<- "C:/Users/andrew.carr-harris/Desktop/Git/welfare-model-GoM/newest_version/output_data/"
```

### Decadal projections (2025-02-10) {.tabset}
Each tab contains different projected fishery outcomes across copula models for the case of dependence, independence, and the difference between dependence and independence. 
```{r echo = FALSE,  fig.width=10}
output<-read_excel(paste0(output_data_cd,"model_output_orig.xlsx"))  

#Output by year
output <- output %>% dplyr::select(-matches("base"))
output <- output %>%
  rename_with(~ gsub("_(cat)", "\\1", .x), matches("_cat")) %>%
  rename_with(~ gsub("_(keep)", "\\1", .x), matches("_keep")) %>%
  rename_with(~ gsub("_(rel)", "\\1", .x), matches("_rel")) %>%
  rename_with(~ gsub("_(alt)", "\\1", .x), matches("_alt")) %>% 
  rename_with(~ gsub("Gaussian", "gaussian", .x), contains("Gaussian"))

# Reshaping to long format
output_long <- output %>%
  pivot_longer(
    cols = starts_with("cv") | starts_with("codkeep") | starts_with("codrel") | starts_with("haddkeep") |
           starts_with("haddrel") | starts_with("haddcat") | starts_with("codcat") | starts_with("ntripsalt"),  # Select columns to reshape
    names_to = c(".value", "correlation", "copula", "decade"), 
    names_pattern = "([a-z]+)_([a-z]+)_([a-z]+)([12345678])"  
  )


# Summing selected variables by grouping variables
output_summarized <- output_long %>%
  group_by(draw, copula, correlation, decade) %>%
  summarise(across(c(codcat, codkeep, codrel, cv, haddcat, haddkeep, haddrel, ntripsalt), \(x) sum(x, na.rm = TRUE)), .groups="drop")

output_summarized <- output_summarized %>%
  dplyr::mutate(codcattrip=codcat/ntripsalt, 
                codkeeptrip=codkeep/ntripsalt, 
                haddcattrip=haddcat/ntripsalt, 
                haddkeeptrip=haddkeep/ntripsalt, 
                cvtrip=cv/ntripsalt)


## What to plot:
  #cod keep trip/total
  #hadd keep trip/total 
  #cod catch trip/total
  #hadd catch trip/total 
  #cv trip/total

#By decade and copula
output_summarized_corr<-output_summarized %>% 
  dplyr::filter(correlation=="corr") %>% 
  dplyr::select(-correlation)

output_summarized_corr <- output_summarized_corr %>%
  rename_with(~ paste0(.x, "_corr"), c(codcat, codkeep, codrel, cv, haddcat, haddkeep, haddrel, ntripsalt, 
                                      codcattrip, codkeeptrip, haddcattrip, haddkeeptrip, cvtrip))

output_summarized_ind<-output_summarized %>% 
  dplyr::filter(correlation=="ind") %>% 
  dplyr::select(-correlation)

output_summarized_ind <- output_summarized_ind %>%
  rename_with(~ paste0(.x, "_ind"), c(codcat, codkeep, codrel, cv, haddcat, haddkeep, haddrel, ntripsalt, 
                                      codcattrip, codkeeptrip, haddcattrip, haddkeeptrip, cvtrip))

output_summarized <- output_summarized_corr %>% 
  dplyr::left_join(output_summarized_ind, by=c("draw", "copula","decade" )) %>% 
  dplyr::mutate(diff_codcat= codcat_corr-codcat_ind,
                diff_codkeep=  codkeep_corr- codkeep_ind,
                diff_codrel=  codrel_corr- codrel_ind,
                diff_cv=  cv_corr- cv_ind,
                diff_haddcat=  haddcat_corr- haddcat_ind,
                diff_haddkeep= haddkeep_corr- haddkeep_ind,
                diff_haddrel= haddrel_corr- haddrel_ind,
                diff_ntripsalt= ntripsalt_corr- ntripsalt_ind,
                diff_codcattrip=  codcattrip_corr- codcattrip_ind,
                diff_codkeeptrip= codkeeptrip_corr- codkeeptrip_ind,
                diff_haddcattrip= haddcattrip_corr- haddcattrip_ind,
                diff_haddkeeptrip= haddkeeptrip_corr- haddkeeptrip_ind,
                diff_cvtrip=cvtrip_corr- cvtrip_ind)

```
<div style="margin-bottom:50px;">
</div>

#### CV per trip (correlated)
```{r echo = FALSE, fig.width=10}
  
ggplot(output_summarized, aes(x=factor(decade), y=cvtrip_corr, color = factor(copula)))+
  geom_boxplot() 

```
<div style="margin-bottom:50px;">
</div>

#### cod catch per trip (correlated)
```{r echo = FALSE, fig.width=10}
  
ggplot(output_summarized, aes(x=factor(decade), y=codcattrip_corr, color = factor(copula)))+
  geom_boxplot() 

```
<div style="margin-bottom:50px;">
</div>

#### cod keep per trip (correlated)
```{r echo = FALSE, fig.width=10}
  
ggplot(output_summarized, aes(x=factor(decade), y=codkeeptrip_corr, color = factor(copula)))+
  geom_boxplot() 

```
<div style="margin-bottom:50px;">
</div>

#### haddock catch per trip (correlated)
```{r echo = FALSE, fig.width=10}
  
ggplot(output_summarized, aes(x=factor(decade), y=haddcattrip_corr, color = factor(copula)))+
  geom_boxplot() 

```
<div style="margin-bottom:50px;">
</div>

#### haddock keep per trip (correlated)
```{r echo = FALSE, fig.width=10}
  
ggplot(output_summarized, aes(x=factor(decade), y=haddkeeptrip_corr, color = factor(copula)))+
  geom_boxplot() 

```
<div style="margin-bottom:50px;">
</div>

#### CV per trip (independent)
```{r echo = FALSE, fig.width=10}
  
ggplot(output_summarized, aes(x=factor(decade), y=cvtrip_ind, color = factor(copula)))+
  geom_boxplot() 
```
<div style="margin-bottom:50px;">
</div>

#### cod catch per trip (independent)
```{r echo = FALSE, fig.width=10}
  
ggplot(output_summarized, aes(x=factor(decade), y=codcattrip_ind, color = factor(copula)))+
  geom_boxplot() 

```
<div style="margin-bottom:50px;">
</div>

#### cod keep per trip (independent)
```{r echo = FALSE, fig.width=10}
  
ggplot(output_summarized, aes(x=factor(decade), y=codkeeptrip_ind, color = factor(copula)))+
  geom_boxplot() 

```
<div style="margin-bottom:50px;">
</div>

#### haddock catch per trip (independent)
```{r echo = FALSE, fig.width=10}
  
ggplot(output_summarized, aes(x=factor(decade), y=haddcattrip_ind, color = factor(copula)))+
  geom_boxplot() 

```
<div style="margin-bottom:50px;">
</div>

#### haddock keep per trip (independent)
```{r echo = FALSE, fig.width=10}
  
ggplot(output_summarized, aes(x=factor(decade), y=haddkeeptrip_ind, color = factor(copula)))+
  geom_boxplot() 

```
#### Diff. CV per trip (corr.-ind.)
```{r echo = FALSE, fig.width=10}
  
ggplot(output_summarized, aes(x=factor(decade), y=diff_cvtrip, color = factor(copula)))+
  geom_boxplot() 
```
<div style="margin-bottom:50px;">
</div>

#### Diff. cod catch per trip (corr.-ind.)
```{r echo = FALSE, fig.width=10}
  
ggplot(output_summarized, aes(x=factor(decade), y=diff_codcattrip, color = factor(copula)))+
  geom_boxplot() 

```
<div style="margin-bottom:50px;">
</div>

#### Diff. cod keep per trip (corr.-ind.)
```{r echo = FALSE, fig.width=10}
  
ggplot(output_summarized, aes(x=factor(decade), y=diff_codkeeptrip, color = factor(copula)))+
  geom_boxplot() 

```
<div style="margin-bottom:50px;">
</div>

#### Diff. haddock catch per trip (corr.-ind.)
```{r echo = FALSE, fig.width=10}
  
ggplot(output_summarized, aes(x=factor(decade), y=diff_haddcattrip, color = factor(copula)))+
  geom_boxplot() 

```
<div style="margin-bottom:50px;">
</div>

#### Diff. haddock keep per trip (corr.-ind.)
```{r echo = FALSE, fig.width=10}
  
ggplot(output_summarized, aes(x=factor(decade), y=diff_haddkeeptrip, color = factor(copula)))+
  geom_boxplot() 

```
### {-}

### Decadal projections (2025-02-14) {.tabset}
